---
title: "NPH static analysis"
author: "Adam"
date: "September 23, 2015"
output: word_document
---
This is my first effort at analysis of the activity of the purported NPH cells. 

In Matlab, I did spike sorting and created a spike density function by convolving the spiketimes with a Gaussian with a standard deviation of 20ms. I then saved that as a table containing the right and left eye position and velocity (calculated using a 7 point parabolic differentiation function) and the spike density function, scaled to approximate firing rate.

```{r,message=FALSE}
t1 <- read.csv("~/GitHub/NPHanalysis/917BTcell.csv")
t2 <- read.csv("~/GitHub/NPHanalysis/datatest1914.csv")

library(ggplot2)
library(dplyr)
library(knitr)
```

First I will plot the average firing rate of the neuron while the eyes are in various positions. I've restricted my analysis to periods when the eyes are not in motion using a simple eye velocity threshold. I require both the vertical and horizontal eye position to be less than one. This allows for pre-movement burst activity to potentially interfere with the static analysis. 

```{r}
meanfr <- function(t){
  t %>%
    filter(rev<1, revV<1) %>%
    mutate(Hep=round(rep),Vep=round(repV)) %>%
    group_by(Hep,Vep) %>%
    summarize(fr=mean(sdf)) ->
    s
  return(s)
}
s1<-meanfr(t1)
s2<-meanfr(t2)
m<-ggplot(s1,aes(Hep,Vep,fill=fr,z=fr))
m+geom_tile()+scale_fill_gradient(low='black',high='orange')+
  xlab('Horizontal Eye Position')+
  ylab('Vertical Eye Position')
  m<-ggplot(s2,aes(Hep,Vep,fill=fr,z=fr))
m+geom_tile()+scale_fill_gradient(low='black',high='orange')+
  xlab('Horizontal Eye Position')+
  ylab('Vertical Eye Position')



```

Next, I calculate the sensitivity of the neuron to horizontal and vertical eye position:

```{r}
compareslope <- function(s) {
  horizontalSlope<-summary(lm(fr~Hep,data=s))$coefficients[2]
  verticalSlope<-summary(lm(fr~Vep,data=s))$coefficients[2]
  preferredDirection<-atan2(verticalSlope,horizontalSlope)*180/pi
  return(data.frame(horizontalSlope=horizontalSlope,verticalSlope=verticalSlope,preferredDirection=preferredDirection))
}
x1<-compareslope(s1)
x2<-compareslope(s2)

x<-rbind(x1,x2)
kable(x,digits=2)
```

For the first cell: The slope is `r round(x1$horizontalSlope,3)` (spikes/s per degree) for horizontal eye positions and `r round(x1$verticalSlope,3)` for vertical eye positions. This corresponds with a preferred angle of `r round(x1$preferredDirection,3)` degrees.

For the second cell: The slope is `r round(x2$horizontalSlope,3)` (spikes/s per degree) for horizontal eye positions and `r round(x2$verticalSlope,3)` for vertical eye positions. This corresponds with a preferred angle of `r round(x2$preferredDirection,3)` degrees.

