---
title: "R Notebook"
output: html_notebook
---



```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE,cache=FALSE)
```

```{r,message=FALSE,echo=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
library(broom)
# library(grid)
library(relaimpo)
library(leaps)
library(stringr)
library(cladoRcpp)
library(boot)
library(ggpubr)
source('Adamhelperfunctions.R')
source('fixationanalysisfunctions.R')
select<- dplyr::select
```


```{r plotFunctions,echo=FALSE}

compare2cells<- function(zp,zmc,c1,c2,maxEP=25,color1='black',color2='black',
                         c1name=NA,c2name=NA){
  
  if(is.na(c1name)){c1name=c1}
  if(is.na(c2name)){c2name=c2}
  
zp<- filter(zp,
            neuron %in% c(c1,c2),
            dur>200,
            abs(mean.R.H)<maxEP,
            abs(mean.L.H)<maxEP,
            abs(mean.R.V)<maxEP,
            abs(mean.L.V)<maxEP,
            meanFR<500)
  
tab<-zmc %>%
  filter(neuron %in% c(c1,c2)) %>%
  select(neuron,R2,H.R2,V.R2,dir.pref.slope,dir.pref.imp)

nV<-ggplot(zp %>% filter(neuron==c1))+
  geom_point(aes(mean.V,meanFR),color=color1)+
  stat_smooth(aes(mean.V,meanFR),color='black',se=FALSE,method=lm)+
  xlab('')+
  theme_minimal()+
  ylab(paste(c1name,'\nMean Firing Rate (spk/s)'))

nH<-ggplot(zp %>% filter(neuron==c1))+
  geom_point(aes(mean.H,meanFR),color=color1)+
  stat_smooth(aes(mean.H,meanFR),color='black',se=FALSE,method=lm)+
  xlab('')+
  ylab('')+
  theme_minimal()

  sV<-ggplot(zp %>% filter(neuron==c2))+
    geom_point(aes(mean.V,meanFR),color=color2)+
    stat_smooth(aes(mean.V,meanFR),color='black',se=FALSE,method=lm)+
    xlab('Mean Vertical Eye Position (deg)')+
    ylab(paste(c2name,'\nMean Firing Rate (spk/s)'))+
    theme_minimal()
  
  sH<-ggplot(zp %>% filter(neuron==c2))+
    geom_point(aes(mean.H,meanFR),color=color2)+
    stat_smooth(aes(mean.H,meanFR),color='black',se=FALSE,method=lm)+
    xlab('Mean Horizontal Eye Position (deg)')+
    ylab('')+
    theme_minimal()


#make a named list to manually color the direction plots
color.values<-NULL
color.values[[c1]]<-color1
color.values[[c2]]<-color2

dir.imp<-ggplot(tab)+
  # geom_segment(aes(y=0,yend=1,x=dir.pref.imp,xend=dir.pref.imp),color='black')+
  geom_segment(aes(y=0,yend=1,x=dir.pref.imp,xend=dir.pref.imp,color=neuron))+
  scale_color_manual(values=color.values)+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  xlab('Direction preference\nusing relative importance')

dir.slope<-ggplot(tab)+
  geom_segment(aes(y=0,yend=1,x=dir.pref.slope,xend=dir.pref.slope,color=neuron))+
  scale_color_manual(values=color.values)+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  xlab('Direction Preference\nusing slopes')

# print(multiplot(nV,sV,dir.slope,nH,sH,dir.imp,cols=2))


return(list(nV,sV,dir.slope,nH,sH,dir.imp))


}

show1cell<- function(zp,zmc,c1,maxEP=25,color1='black',c1name=NA){
  
  if(is.na(c1name)){c1name=c1}

zp<- filter(zp,
            neuron == c1,
            dur>200,
            abs(mean.R.H)<maxEP,
            abs(mean.L.H)<maxEP,
            abs(mean.R.V)<maxEP,
            abs(mean.L.V)<maxEP,
            meanFR<500)
  
tab<-zmc %>%
  filter(neuron == c1) %>%
  select(neuron,R2,H.R2,V.R2,dir.pref.slope,dir.pref.imp)

nV<-ggplot(zp %>% filter(neuron==c1))+
  geom_point(aes(mean.V,meanFR),color=color1)+
  stat_smooth(aes(mean.V,meanFR),color='black',se=FALSE,method=lm)+
  xlab('Mean Horizontal Eye Position (deg)')+
  theme_minimal()+
  ylab(paste(c1name,'\nMean Firing Rate (spk/s)'))

nH<-ggplot(zp %>% filter(neuron==c1))+
  geom_point(aes(mean.H,meanFR),color=color1)+
  stat_smooth(aes(mean.H,meanFR),color='black',se=FALSE,method=lm)+
  xlab('Mean Vertical Eye Position (deg)')+
  ylab('')+
  theme_minimal()


#make a named list to manually color the direction plots
color.values<-NULL
color.values[[c1]]<-color1

dir.imp<-ggplot(tab)+
  # geom_segment(aes(y=0,yend=1,x=dir.pref.imp,xend=dir.pref.imp),color='black')+
  geom_segment(aes(y=0,yend=1,x=dir.pref.imp,xend=dir.pref.imp,color=neuron))+
  scale_color_manual(values=color.values)+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  xlab('Direction preference\nusing relative importance')

dir.slope<-ggplot(tab)+
  geom_segment(aes(y=0,yend=1,x=dir.pref.slope,xend=dir.pref.slope,color=neuron))+
  scale_color_manual(values=color.values)+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  xlab('Direction Preference\nusing slopes')

# print(multiplot(nV,sV,dir.slope,nH,sH,dir.imp,cols=2))


return(list(nV,dir.slope,nH,dir.imp))

}

```


```{r load,cache=FALSE}
#skip the next two chunks (quickload and mark saccades) if you load this.
 # t<- readRDS('INCsaccadesmarked.RDS')
 # t<- readRDS('OMNstrabMeasured4-19-2018.RDS') 
 t<-readRDS('INCmeasuredall.RDS')
```

```{r quickload,echo=FALSE,cache=TRUE}
LoadFromFile<- FALSE

if (LoadFromFile){
  o<- readRDS('OMNstrab.RDS')
}else{
  o<-NULL
}

# t<- loadnewcsv2(path="C:/Users/setup/Desktop/NRTP Vergence/OMNfinal/",referencefile=o)
t<- loadnewcsv2(path="C:/Users/setup/Desktop/NRTP Vergence/INCstrab/",referencefile=o)

t<- rbind(o,t)

o<-NULL

```


```{r mark saccades,cache=FALSE,eval=FALSE}

t %>%
  group_by(neuron) %>%
  # mutate(time=row_number()) %>%
  do(cleanFixations(.)) ->
  # do(measureFixations(.))-># %>%
  # do(expandSaccades(.,buffer=80))->
  t

# saveRDS(t,'OMNstrabMeasured4-19-2018.RDS')

```

```{r Measure_Fixations,warning=FALSE}


zp<-measureFixations(t)

maxEP<- 35
zp<- filter(zp,
            dur>200,
            abs(mean.R.H)<maxEP,
            abs(mean.L.H)<maxEP,
            abs(mean.R.V)<maxEP,
            abs(mean.L.V)<maxEP,
            meanFR<500)



```

```{r bootstrap sensitivities}


getObservedcoef<-function(z){
  modR <- lm(meanFR ~ mean.R.H+mean.R.V,data=z)
  modL <- lm(meanFR ~ mean.L.H+mean.L.V,data=z)
  modRL<- lm(meanFR ~ mean.H+mean.V,data=z)
  rn<- c('right','left','cyclopean')
  dt<-as_tibble(rbind(as.numeric(coef(modR)),
                      as.numeric(coef(modL)),
                      as.numeric(coef(modRL))))
  names(dt)<-c('intercept_o','horizontal_o','vertical_o')
  dt$type=rn
  dt 
}

bootstrapDirPref<-function(zboot,nreps){
  
  getcoef<-function(n,z){
    z <- sample_frac(z,size= 1,replace=TRUE)
    modR <- lm(meanFR ~ mean.R.H+mean.R.V,data=z)
    modL <- lm(meanFR ~ mean.L.H+mean.L.V,data=z)
    modRL<- lm(meanFR ~ mean.H+mean.V,data=z)
    rn<- c('right','left','cyclopean')
    dt<-as_tibble(rbind(as.numeric(coef(modR)),
                        as.numeric(coef(modL)),
                        as.numeric(coef(modRL))))
    names(dt)<-c('intercept','horizontal','vertical')
    dt$type=rn
    dt$repN=n
    dt 
  }
  
  n<- matrix(1:nreps)
  neuronName<- zboot$neuron[1]
  x<- as.data.frame(rbindlist(lapply(n,getcoef,zboot))) #calls the function n times
  x<- mutate(x,neuron=neuronName)
}


##########################################################
#THIS BLOCK TAKES A LONG TIME SINCE IT FITS >600k linear models
###########################################################
# zb<-readRDS('INCbootstrap-4-24-2018.RDS')
zp %>%
  group_by(neuron) %>%
  do(bootstrapDirPref(.,nreps=1999)) %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  zb
# saveRDS(zb,'INCbootstrap-4-24-2018.RDS')

zp %>%
  group_by(neuron) %>%
  do(getObservedcoef(.)) %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  zo



zb %>%
  group_by(neuron,type) %>%
  summarize(lowH=quantile(horizontal,probs=0.025),
            lowV=quantile(vertical,probs=0.025),
            highH=quantile(horizontal,probs=0.975),
            highV=quantile(vertical,probs=0.975)) %>%
  mutate(zerocrossH=lowH*highH < 0,
         zerocrossV=lowV*highV < 0)->
  zci

zo<- left_join(zo,zci)
```


First we will plot all of the cells and their bootstrapped confidence intervals:

```{r Bootstrapplots}
ggplot(zo,aes(abs(horizontal_o),abs(vertical_o)))+
  geom_errorbar(aes(ymin=lowV*sign(vertical_o),ymax=highV*sign(vertical_o)),
                 width=0,size=0.5,alpha=0.3)+
  geom_errorbarh(aes(xmin=lowH*sign(horizontal_o),xmax=highH*sign(horizontal_o)),
                 height=0,size=0.5,alpha=0.3)+
  geom_point(aes(color=monkey),size=2)+
  geom_abline(size=2,linetype=2,alpha=0.2)+
  coord_fixed()+
  facet_wrap(~type,ncol=3)+
  # ylim(c(NA,3.9))+
  theme_minimal()+
  geom_vline(xintercept = 0,color='hotpink')+
  geom_hline(yintercept = 0,color='hotpink')+
  xlab('Sensitivity to Horizontal Eye Position ((spk/s)/(deg/s))')+
  ylab('Sensitivfity to Vertical Eye Position ((spk/s)/(deg/s))')+
  theme(legend.position='bottom')
```

```{r,fig.height=6,fig.width=8}
ggplot(zo %>% filter(type=='right'),aes(abs(horizontal_o),abs(vertical_o)))+
  geom_errorbar(aes(ymin=lowV*sign(vertical_o),ymax=highV*sign(vertical_o)),
                 width=0,size=0.5,alpha=0.3)+
  geom_errorbarh(aes(xmin=lowH*sign(horizontal_o),xmax=highH*sign(horizontal_o)),
                 height=0,size=0.5,alpha=0.3)+
  geom_point(aes(color=monkey),size=2)+
  geom_abline(size=2,linetype=2,alpha=0.2)+
  coord_fixed()+
  facet_wrap(~monkey,ncol=3)+
  # ylim(c(NA,3.9))+
  theme_minimal()+
  geom_vline(xintercept = 0,color='hotpink')+
  geom_hline(yintercept = 0,color='hotpink')+
  xlab('Sensitivity to Horizontal Eye Position ((spk/s)/(deg/s))')+
  ylab('Sensitivfity to Vertical Eye Position ((spk/s)/(deg/s))')+
  theme(legend.position='bottom')
```

Next we can look at just those that have a significant sensitivity to horizontal position:

```{r,fig.height=8,fig.width=4}
ggplot(zo %>% filter(type=='right',!zerocrossH),aes(abs(horizontal_o),abs(vertical_o)))+
  geom_errorbar(aes(ymin=lowV*sign(vertical_o),ymax=highV*sign(vertical_o)),
                 width=0,size=0.5,alpha=0.3)+
  geom_errorbarh(aes(xmin=lowH*sign(horizontal_o),xmax=highH*sign(horizontal_o)),
                 height=0,size=0.5,alpha=0.3)+
  geom_point(aes(color=monkey),size=2)+
  geom_abline(size=2,linetype=2,alpha=0.2)+
  coord_fixed()+
  facet_wrap(~type,ncol=3)+
  ylim(c(NA,3.9))+
  theme_minimal()+
  geom_vline(xintercept = 0,color='hotpink')+
  geom_hline(yintercept = 0,color='hotpink')+
  xlab('Sensitivity to Horizontal Eye Position ((spk/s)/(deg/s))')+
  ylab('Sensitivfity to Vertical Eye Position ((spk/s)/(deg/s))')+
  theme(legend.position='bottom')

zo %>% 
  filter(type=='right') %>%
  group_by(monkey) %>%
  summarize(n=n(),
            signifH=sum(!zerocrossH),
            signifV=sum(!zerocrossV),
            signifboth=sum(!zerocrossH & !zerocrossV),
            signifHfrac=sum(!zerocrossH)/n,
            signifVfrac=sum(!zerocrossV)/n,
            signifbothfrac=sum(!zerocrossH & !zerocrossV)/n) %>%
  kable(digits = 2)
```

```{r,fig.height=8,fig.width=4}
ggplot(zo %>% filter(type=='right'),aes(abs(horizontal_o),abs(vertical_o)))+
  geom_point(aes(color=monkey),size=2)+
  geom_abline(size=2,linetype=2,alpha=0.2)+
  geom_segment(x=0,y=0,aes(xend=abs(horizontal_o),yend=abs(vertical_o),color=monkey),alpha=0.5)+
  coord_fixed()+
  facet_wrap(~monkey,ncol=3)+
  ylim(c(NA,3.9))+
  theme_minimal()+
  geom_vline(xintercept = 0,color='hotpink')+
  geom_hline(yintercept = 0,color='hotpink')+
  xlab('Sensitivity to Horizontal Eye Position ((spk/s)/(deg/s))')+
  ylab('Sensitivfity to Vertical Eye Position ((spk/s)/(deg/s))')+
  theme(legend.position='bottom')
```
```{r,fig.height=8,fig.width=4}
ggplot(zo %>% filter(type=='left',!zerocrossV),aes(horizontal_o,vertical_o))+
  geom_point(aes(color=monkey),size=2)+
  geom_abline(size=2,linetype=2,alpha=0.2)+
  geom_segment(x=0,y=0,aes(xend=horizontal_o,yend=vertical_o,color=monkey),alpha=0.5)+
  coord_fixed()+
  facet_wrap(~monkey,ncol=3)+
  ylim(c(NA,3.9))+
  theme_minimal()+
  geom_vline(xintercept = 0,color='hotpink')+
  geom_hline(yintercept = 0,color='hotpink')+
  xlab('Sensitivity to Horizontal Eye Position ((spk/s)/(deg/s))')+
  ylab('Sensitivfity to Vertical Eye Position ((spk/s)/(deg/s))')+
  theme(legend.position='bottom')
```


```{r}
zo<- mutate(zo,magnitude=sqrt(horizontal_o^2+vertical_o^2))

zo %>%
  filter(type=='right') %>%
  group_by(monkey) %>%
  summarize(meanHsens=mean(abs(horizontal_o)),
            sdHsens=sd(abs(horizontal_o))) %>%
  kable(digits=2)

zo %>%
  filter(type=='right') %>%
  ggplot()+
  geom_boxplot(aes(monkey,abs(horizontal_o),fill=monkey))
  
summary(aov(abs(horizontal_o)~monkey,data=zo))

```

```{r}
zo<- mutate(zo,magnitude=sqrt(horizontal_o^2+vertical_o^2))

zo %>%
  filter(type=='right') %>%
  group_by(monkey) %>%
  summarize(meanVsens=mean(abs(vertical_o)),
            sdVsens=sd(abs(horizontal_o))) %>%
  kable(digits=2)

zo %>%
  filter(type=='right') %>%
  ggplot()+
  geom_boxplot(aes(monkey,abs(vertical_o),fill=monkey))
  
summary(aov(abs(vertical_o)~monkey,data=zo))

```



```{r statfigsV}

zo %>%
  filter(type=='right') %>%
ggboxplot(x = "monkey", y='abs(vertical_o)',
         color = "monkey", palette = "npg",
         # facet.by = c("subject","amp.bins.15"), short.panel.labs = TRUE)
         short.panel.labs = TRUE) + 
  stat_compare_means(label.y=5)+
  stat_compare_means(comparisons = list(c('Bee','DC'),c('Bee','Kopachuck'),c('DC','Kopachuck')))+
  # stat_compare_means(label = "p.signif")+
  xlab('Monkey')+
  ylab('Sensitivity to Vertical Eye Position ((spk/s)/(deg/s))')+
  theme(legend.position = 'bottom')

```


Horizontal sensitivity is not significantly different, but there are a lot of cells included here where the slopes are not significant.

```{r statfigsH}

zo %>%
  filter(type=='right') %>%
ggboxplot(x = "monkey", y='abs(horizontal_o)',
         color = "monkey", palette = "npg",
         # facet.by = c("subject","amp.bins.15"), short.panel.labs = TRUE)
         short.panel.labs = TRUE) + 
  stat_compare_means(label.y=1.6)+
  stat_compare_means(comparisons = list(c('Bee','DC'),c('Bee','Kopachuck'),c('DC','Kopachuck')))+
  # stat_compare_means(label = "p.signif")+
  xlab('Monkey')+
  ylab('Sensitivity to Horizontal Eye Position ((spk/s)/(deg/s))')+
  theme(legend.position = 'bottom')

```


However, if we just look at cells where there is a significant sensitivity to horizontal eye position, then the differences are significant, but not remarkably so.

```{r statfigsHsignif}

zo %>%
  filter(type=='right',!zerocrossH) %>%
ggboxplot(x = "monkey", y='abs(horizontal_o)',
         color = "monkey", palette = "npg",
         # facet.by = c("subject","amp.bins.15"), short.panel.labs = TRUE)
         short.panel.labs = TRUE) + 
  stat_compare_means(label.y=1.6)+
  stat_compare_means(comparisons = list(c('Bee','DC'),c('Bee','Kopachuck'),c('DC','Kopachuck')))+
  # stat_compare_means(label = "p.signif")+
  xlab('Monkey')+
  ylab('Sensitivity to Horizontal Eye Position ((spk/s)/(deg/s))')+
  theme(legend.position = 'bottom')

```


#Curve fitting direction preferences

```{r}
getPreferredDirectionFixSin<-function(ndata,eye='cyclopean',min_amp=5){
  
  if (eye=='cyclopean'){
    ndata %>%
      mutate(fix.angle=atan2(mean.V,mean.H),
             fix.radius=sqrt(mean.H^2+mean.V^2)) ->
      # filter(meanFR>1,meanFR<300,fix.radius>min_amp,dur>200)->
      ndata
  } else if(eye=='right'){
    
    ndata %>%
      mutate(fix.angle=atan2(mean.R.V,mean.R.H),
             fix.radius=sqrt(mean.R.H^2+mean.R.V^2)) ->
      # filter(meanFR>0,meanFR<250,fix.radius>min_amp,dur>200)->
      ndata
  }else if (eye=='left'){
    
    ndata %>%
      mutate(fix.angle=atan2(mean.L.V,mean.L.H),
             fix.radius=sqrt(mean.L.H^2+mean.L.V^2)) ->
       # filter(meanFR>0,meanFR<250,fix.radius>min_amp,dur>200)->
      ndata
  }else if (eye=='viewing'){
        ndata %>%
      mutate(fix.angle=atan2(mean.V.viewing,mean.H.viewing),
             fix.radius=sqrt(mean.H.viewing^2+mean.V.viewing^2)) ->
       # filter(meanFR>0,meanFR<250,fix.radius>min_amp,dur>200,fix.radius<40)->
      ndata
  }else{
    message('Invalid Eye Choice')
    return(NULL)
  }
  
  ndata %>%
    mutate(fix.angle=fix.angle+pi) %>%
    filter(meanFR>0,meanFR<250,fix.radius>min_amp,dur>200,fix.radius<40)->
    ndata
  
  mod<- lm(meanFR~sin(fix.angle)+cos(fix.angle)+fix.angle,
           data=ndata)
  
  # template<-data.frame(fix.angle=seq(-pi,pi,by = 0.01))
  template<-data.frame(fix.angle=seq(0,2*pi,by = 0.01))
  
  template$xx<-predict(mod,newdata=template)
  
  # print(qplot(fix.angle,xx,data=template))
  # print(qplot(fix.angle*180/pi,meanFR,data=ndata)+
  #         stat_smooth(method='lm',formula=y~exp(-1*x+1))+
  #       geom_point(aes(fix.angle*180/pi,xx),data=template,color='magenta'))
  
  preferred.direction=filter(template,xx==max(xx))$fix.angle
  pFR=max(template$xx)
  return(data.frame(dirpref=preferred.direction*180/pi,pFR=pFR,R2=summary(mod)$r.squared))
}
```


```{r}
zp%>%
  ungroup() %>%
  group_by(neuron) %>%
  # filter(neuron=='Bee-110') %>%
  do(getPreferredDirectionFixSin(.,eye='right',min_amp = 10)) %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  dpfix

multiplot(
  ggplot(dpfix)+
    geom_segment(aes(y=0,yend=pFR,x=dirpref,xend=dirpref,color=monkey))+
    scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
    coord_polar(start=pi/2,direction=-1)+
    theme_minimal()+
    theme(legend.position='none')+
    facet_wrap(~monkey,ncol=3)+
    xlab('Direction preference')+
    ylab('Average Maximum FR')
,
  ggplot(dpfix)+
    geom_segment(aes(y=0,yend=R2,x=dirpref,xend=dirpref,color=monkey))+
    scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
    coord_polar(start=pi/2,direction=-1)+
    theme_minimal()+
    theme(legend.position='none')+
    facet_wrap(~monkey,ncol=3)+
    xlab('Direction preference')+
    ylab('Goodness of Fit')
)
```

Let's look at how well this function fits the cells

```{r}

ggplot(dpfix)+
  geom_boxplot(aes(monkey,R2,fill=monkey))

```



```{r botplotstats}
ggboxplot(dpfix,x = "monkey", y='R2',
         color = "monkey", palette = "npg",
         # facet.by = c("subject","amp.bins.15"), short.panel.labs = TRUE)
         short.panel.labs = TRUE) + 
  stat_compare_means(label.y=1.2)+
  stat_compare_means(comparisons = list(c('Bee','DC'),c('Bee','Kopachuck'),c('DC','Kopachuck')))+
  # stat_compare_means(label = "p.signif")+
  xlab('Monkey')+
  ylab('Goodness of Fit')+
  theme(legend.position = 'bottom')
```



##Viewing Eye
```{r viewing}
zp%>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE) %>%
  filter(monkey !='Bee', #Bee looks with both eyes
         !(is.na(right.eye.viewing)&is.na(left.eye.viewing))) %>% #get rid of ones with no viewing eye
  mutate(mean.H.viewing=ifelse(right.eye.viewing,mean.R.H,mean.L.H),
         mean.V.viewing=ifelse(right.eye.viewing,mean.R.V,mean.L.V)) %>%
  ungroup() %>%
  group_by(neuron) %>%
  # filter(neuron=='Bee-110') %>%
  do(getPreferredDirectionFixSin(.,eye='viewing',min_amp = 15)) %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  dpfix

multiplot(
  ggplot(dpfix)+
    geom_segment(aes(y=0,yend=pFR,x=dirpref-180,xend=dirpref-180,color=monkey))+
    scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
    coord_polar(start=pi/2,direction=-1)+
    theme_minimal()+
    theme(legend.position='none')+
    facet_wrap(~monkey,ncol=3)+
    xlab('Direction preference')+
    ylab('Average Maximum FR')
  ,
  ggplot(dpfix)+
    geom_segment(aes(y=0,yend=R2,x=dirpref-180,xend=dirpref-180,color=monkey))+
    scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
    coord_polar(start=pi/2,direction=-1)+
    theme_minimal()+
    theme(legend.position='none')+
    facet_wrap(~monkey,ncol=3)+
    xlab('Direction preference')+
    ylab('Goodness of Fit')
)
```

```{r testing viewingeye bootstraps}


getObservedcoef<-function(z){
  modR <- lm(meanFR ~ mean.R.H+mean.R.V,data=z)
  modL <- lm(meanFR ~ mean.L.H+mean.L.V,data=z)
  modRL<- lm(meanFR ~ mean.H+mean.V,data=z)
  modV <- lm(meanFR ~ mean.H.viewing+mean.V.viewing,data=z)
  rn<- c('right','left','cyclopean','viewing')
  dt<-as_tibble(rbind(as.numeric(coef(modR)),
                      as.numeric(coef(modL)),
                      as.numeric(coef(modRL)),
                      as.numeric(coef(modV))))
  names(dt)<-c('intercept_o','horizontal_o','vertical_o')
  dt$type=rn
  dt 
}

bootstrapDirPref<-function(zboot,nreps){
  
  getcoef<-function(n,z){
    z <- sample_frac(z,size= 1,replace=TRUE)
    modR <- lm(meanFR ~ mean.R.H+mean.R.V,data=z)
    modL <- lm(meanFR ~ mean.L.H+mean.L.V,data=z)
    modRL<- lm(meanFR ~ mean.H+mean.V,data=z)
    modV <- lm(meanFR ~ mean.H.viewing+mean.V.viewing,data=z)
    
    rn<- c('right','left','cyclopean','viewing')
    
    dt<-as_tibble(rbind(as.numeric(coef(modR)),
                        as.numeric(coef(modL)),
                        as.numeric(coef(modRL)),
                        as.numeric(coef(modV))))
    names(dt)<-c('intercept','horizontal','vertical')
    dt$type=rn
    dt$repN=n
    dt 
  }
  
  n<- matrix(1:nreps)
  neuronName<- zboot$neuron[1]
  x<- as.data.frame(rbindlist(lapply(n,getcoef,zboot))) #calls the function n times
  x<- mutate(x,neuron=neuronName)
}


##########################################################
#THIS BLOCK TAKES A LONG TIME SINCE IT FITS >600k linear models
###########################################################
# zb<-readRDS('INCbootstrap-4-24-2018.RDS')
zp %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE) %>%
  filter(monkey !='Bee', #Bee looks with both eyes
         !(is.na(right.eye.viewing)&is.na(left.eye.viewing))) %>% #get rid of ones with no viewing eye
  mutate(mean.H.viewing=ifelse(right.eye.viewing,mean.R.H,mean.L.H),
         mean.V.viewing=ifelse(right.eye.viewing,mean.R.V,mean.L.V)) ->
  zve


zve %>%
  group_by(neuron) %>%
  do(bootstrapDirPref(.,nreps=199)) %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  zb
# saveRDS(zb,'INCbootstrap-4-24-2018.RDS')

zve %>%
  group_by(neuron) %>%
  do(getObservedcoef(.)) %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  zo



zb %>%
  group_by(neuron,type) %>%
  summarize(lowH=quantile(horizontal,probs=0.025),
            lowV=quantile(vertical,probs=0.025),
            highH=quantile(horizontal,probs=0.975),
            highV=quantile(vertical,probs=0.975)) %>%
  mutate(zerocrossH=lowH*highH < 0,
         zerocrossV=lowV*highV < 0)->
  zci

zo<- left_join(zo,zci)
```




```{r Bootstrapplots2}
ggplot(zo,aes(abs(horizontal_o),abs(vertical_o)))+
  geom_errorbar(aes(ymin=lowV*sign(vertical_o),ymax=highV*sign(vertical_o)),
                 width=0,size=0.5,alpha=0.3)+
  geom_errorbarh(aes(xmin=lowH*sign(horizontal_o),xmax=highH*sign(horizontal_o)),
                 height=0,size=0.5,alpha=0.3)+
  geom_point(aes(color=monkey),size=2)+
  geom_abline(size=2,linetype=2,alpha=0.2)+
  coord_fixed()+
  facet_wrap(~type,ncol=4)+
  # ylim(c(NA,3.9))+
  theme_minimal()+
  geom_vline(xintercept = 0,color='hotpink')+
  geom_hline(yintercept = 0,color='hotpink')+
  xlab('Sensitivity to Horizontal Eye Position ((spk/s)/(deg/s))')+
  ylab('Sensitivfity to Vertical Eye Position ((spk/s)/(deg/s))')+
  theme(legend.position='bottom')
```

##Old Stuff

```{r Fixation_Analysis,cache=FALSE,warning=FALSE}


zp %>%
    filter(meanFR>0,dur<1000,mean.conj.velocity<10) %>%
  group_by(neuron) %>%
  mutate(n=n()) %>%
  filter(n>20) %>%
  do(calculateDirPrefFixations(.)) %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  zm



```
#Results

```{r RegularCells,fig.height=7,fig.width=6}
Ncell<- 'Patos-107'
Scell<- 'Patos-110'



tab<-zmc %>%
  filter(neuron %in% c(Ncell,Scell)) %>%
  select(neuron,R2,H.R2,V.R2,dir.pref.slope,dir.pref.imp)

multiplot(plotlist=compare2cells(zp,zmc,Ncell,Scell,color1='purple',color2='orange',
                                 c1name=Ncell,c2name=Scell),cols=2)

kable(tab,digits=2)

```

\pagebreak

###Direction Preferences
Using RIGHT EYE only
```{r,fig.height=6}
multiplot(
ggplot(zm)+
  geom_segment(aes(y=0,yend=1,x=dir.imp.R,xend=dir.imp.R,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('')+
  ylab(''),
ggplot(zm)+
  geom_segment(aes(y=0,yend=R2R,x=dir.imp.R,xend=dir.imp.R,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('Direction preference\nusing relative importance')+
  ylab('R-squared'),
cols=1
)

```

```{r lefteye, fig.height=6}
multiplot(
ggplot(zm)+
  geom_segment(aes(y=0,yend=1,x=dir.imp.L,xend=dir.imp.L,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('')+
  ylab(''),
ggplot(zm)+
  geom_segment(aes(y=0,yend=R2L,x=dir.imp.L,xend=dir.imp.L,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('Direction preference\nusing relative importance')+
  ylab('R-squared'),
cols=1
)

```


CONJUGATE
```{r conjugate, fig.height=6}
multiplot(
ggplot(zm)+
  geom_segment(aes(y=0,yend=1,x=dir.pref.imp, xend=dir.pref.imp,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('')+
  ylab(''),
ggplot(zm)+
  geom_segment(aes(y=0,yend=R2,x=dir.pref.imp,xend=dir.pref.imp,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('Direction preference\nusing relative importance')+
  ylab('R-squared'),
cols=1
)

```


When Mark asked me about the methods for how I was calculating direction preference for his grant, he wanted to avoid using the relative importance metric, but using slopes directly introduces noise unnecessarily because the magnitude of the slope isn't related to how good the fit is.

My new idea was to replace any non-significant slope with zero. At this point, I am using a p-value of 0.001 for the linear model. I came up with that number because it's 0.05 divided by 50, but I have also been considering doing a bootstrap confidence interval. 


```{r goodslopes_R, fig.height=6}
multiplot(
ggplot(zm)+
  geom_segment(aes(y=0,yend=1,x=dir.goodslopes.R, xend=dir.goodslopes.R,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('')+
  ylab(''),
ggplot(zm)+
  geom_segment(aes(y=0,yend=R2R,x=dir.goodslopes.R,xend=dir.goodslopes.R,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('Direction preference\nusing only significant slopes and RIGHT eye only')+
  ylab('R-squared'),
cols=1
)

```


```{r goodslopes_L, fig.height=6}
multiplot(
ggplot(zm)+
  geom_segment(aes(y=0,yend=1,x=dir.goodslopes.L, xend=dir.goodslopes.L,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('')+
  ylab(''),
ggplot(zm)+
  geom_segment(aes(y=0,yend=R2L,x=dir.goodslopes.L,xend=dir.goodslopes.L,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('Direction preference\nusing only significant slopes and LEFT eye only')+
  ylab('R-squared'),
cols=1
)

```


```{r goodslopes_conj, fig.height=6}
multiplot(
ggplot(zm)+
  geom_segment(aes(y=0,yend=1,x=dir.goodslopes, xend=dir.goodslopes,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('')+
  ylab(''),
ggplot(zm)+
  geom_segment(aes(y=0,yend=R2,x=dir.goodslopes,xend=dir.goodslopes,color=monkey))+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  theme_minimal()+
  theme(legend.position='none')+
  facet_wrap(~monkey,ncol=4)+
  xlab('Direction preference\nusing only significant slopes and LEFT eye only')+
  ylab('R-squared'),
cols=1
)

```

Let's compare methods now... The right eye seems to be the best for DC

```{r dirpref_compare, fig.height=15,fig.width=6}
multiplot(
  #slopes
    ggplot(zm)+
    geom_segment(aes(y=0,yend=R2L,x=dir.pref.L,xend=dir.pref.L,color=monkey))+
    scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
    coord_polar(start=pi/2,direction=-1)+
    theme_minimal()+
    theme(legend.position='none')+
    facet_wrap(~monkey,ncol=4)+
    xlab('Direction preference\nusing slopes and LEFT eye only')+
    ylab('R-squared'),
      ggplot(zm)+
    geom_segment(aes(y=0,yend=R2R,x=dir.pref.R,xend=dir.pref.R,color=monkey))+
    scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
    coord_polar(start=pi/2,direction=-1)+
    theme_minimal()+
    theme(legend.position='none')+
    facet_wrap(~monkey,ncol=4)+
    xlab('Direction preference\nusing slopes and RIGHT eye only')+
    ylab('R-squared'),
  #Relative Importance  
    ggplot(zm)+
    geom_segment(aes(y=0,yend=R2L,x=dir.imp.L,xend=dir.imp.L,color=monkey))+
    scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
    coord_polar(start=pi/2,direction=-1)+
    theme_minimal()+
    theme(legend.position='none')+
    facet_wrap(~monkey,ncol=4)+
    xlab('Direction preference\nusing relative importance and LEFT eye only')+
    ylab('R-squared'),
    ggplot(zm)+
    geom_segment(aes(y=0,yend=R2R,x=dir.imp.R,xend=dir.imp.R,color=monkey))+
    scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
    coord_polar(start=pi/2,direction=-1)+
    theme_minimal()+
    theme(legend.position='none')+
    facet_wrap(~monkey,ncol=4)+
    xlab('Direction preference\nusing relative importance and RIGHT eye only')+
    ylab('R-squared'),
  #Significant Slopes
    
  ggplot(zm)+
    geom_segment(aes(y=0,yend=R2L,x=dir.goodslopes.L,xend=dir.goodslopes.L,color=monkey))+
    scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
    coord_polar(start=pi/2,direction=-1)+
    theme_minimal()+
    theme(legend.position='none')+
    facet_wrap(~monkey,ncol=4)+
    xlab('Direction preference\nusing only significant slopes and LEFT eye only')+
    ylab('R-squared'),
  ggplot(zm)+
    geom_segment(aes(y=0,yend=R2R,x=dir.goodslopes.R,xend=dir.goodslopes.R,color=monkey))+
    scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
    coord_polar(start=pi/2,direction=-1)+
    theme_minimal()+
    theme(legend.position='none')+
    facet_wrap(~monkey,ncol=4)+
    xlab('Direction preference\nusing only significant slopes and RIGHT eye only')+
    ylab('R-squared'),

  cols=1
)

```