---
title: "Analysis of INC in strabismus"
author: "Adam Pallus"
output:
  pdf_document: default
  html_document: default
---
#Introduction
Previous work from our lab has shown that saccadic burst generators can have abnormal preferred directions in monkey models of infantile pattern strabismus. Additionally, microstimulation of the superior colliculus and saccadic burst generators can evoke disconjugate movements. This, along with behavioral evidence, suggests a neural origin of the "cross-talk" seen in pattern strabismus.

The intersitial nucleus of cajal (INC) is the location of the vertical neural integrator for eye position. If abnormal signals are present in the burst generators, then these signals should be integrated by the INC. In this report, we assess the direction preference of INC neurons in strabismus and compare with the normal monkey. 


```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE,cache=FALSE)
```

```{r,message=FALSE,echo=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
library(broom)
# library(grid)
library(relaimpo)
library(leaps)
library(stringr)
library(cladoRcpp)
library(boot)
source('Adamhelperfunctions.R')
select<- dplyr::select
```

```{r quickload,echo=FALSE}

t<- loadnewcsv2(path="C:/Users/setup/Desktop/NRTP Vergence/INCstrab/",referencefile=NULL)

t %>% group_by(neuron) %>%
  mutate(time=row_number()) ->
  t

o<-NULL

```

```{r mark saccades}
t %>%
  filter(monkey=='DC') %>%
  group_by(neuron) %>%
  mutate(blinks=markSaccades(rep,buffer=80,threshold=70),
         # dsnum=markSaccadesDouble(conj.velocity,threshold1=30,threshold2=15),
         dsnum=markSaccadesDouble(replace(conj.velocity,blinks>0,150),
                                  threshold1=30,threshold2=15,maxreject=100000),
         sdf=spikedensity(rasters,10),
         sdf10=lag(sdf,10),
         conj.vert=(repV+lepV)/2,
         conj.vert.vel=(revV+levV)/2,
         conj.hor=(rep+lep)/2,
         conj.hor.v=(rev+lev)/2) ->
  tdc

t %>%
  filter(monkey %in% c('Kopachuck','Bee')) %>%
  group_by(neuron) %>%
  mutate(dsnum=markSaccadesDouble(conj.velocity,threshold1=30,threshold2=15),
         sdf=spikedensity(rasters,10),
         sdf10=lag(sdf,10),
         conj.vert=(repV+lepV)/2,
         conj.vert.vel=(revV+levV)/2,
         conj.hor=(rep+lep)/2,
         conj.hor.v=(rev+lev)/2) ->
  tkb

t<- rbind(select(tdc,-blinks),tbk)
```

```{r Measure_Fixations}
t %>%
  group_by(neuron)%>%
  mutate(time=row_number()) %>%
  filter(dsnum<0) %>% #fixations only
  group_by(neuron,dsnum) %>%
  summarize(sd.conj.velocity=sd(conj.velocity),
            mean.conj.velocity=mean(conj.velocity),
            spread=max(conj.velocity)-min(conj.velocity),
            qrange=quantile(conj.velocity,0.975)-quantile(conj.velocity,0.025),
            dur=n(),
            starttime=first(time),
            c2eyes=cor(repV,lepV),
            meanFR=sum(rasters)/dur*1000,
            mean.V=mean(conj.vert),
            mean.H=mean(conj.hor),
            mean.R.H=mean(rep),
            mean.L.H=mean(lep),
            mean.R.V=mean(repV),
            mean.L.V=mean(lepV),
            mean.T.V=mean(tvp),
            mean.T.H=mean(thp),
            asleep=sd.conj.velocity>7.5 || dur>2000)->
  zp
```

```{r Fixation_Analysis}
#In this chunk, we calculate direction preferences for each  neuron based on the measured fixations

measureCell<-function(x){
  #Remove bad fixations that are too short or are outside of the normal range of eye movements
  x<- filter(x,dur>200,abs(mean.R.H)<50,abs(mean.L.H)<50)
  
  #calculate linear regression models on horizontal, vertical and combined
  #calculate each eye separately 
  mRH<-lm(meanFR~mean.R.H,data=x)
  mLH<-lm(meanFR~mean.L.H,data=x)
  mRV<-lm(meanFR~mean.R.V,data=x)
  mLV<-lm(meanFR~mean.L.V,data=x)
  mRHV<-lm(meanFR~mean.R.H+mean.R.V,data=x)
  mLHV<-lm(meanFR~mean.L.H+mean.L.V,data=x)
  
  #Summarize desired information about models
  RH.p=anova(mRH)$'Pr(>F)'[1]
  LH.p=anova(mLH)$'Pr(>F)'[1]
  LV.p<- anova(mLV)$'Pr(>F)'[1]
  RV.p<- anova(mRV)$'Pr(>F)'[1]
  RH<-as.numeric(coef(mRHV)[2])
  RV<-as.numeric(coef(mRHV)[3]) 
  LH<-as.numeric(coef(mLHV)[2])
  LV<-as.numeric(coef(mLHV)[3])  
  
  #two methods to calculate direction preferences:

  #calculate direction preference using slopes of regression lines
  dir.pref.R<-as.numeric(atan2(RV,RH))*180/pi
  dir.pref.L<-as.numeric(atan2(LV,LH))*180/pi
  
  #calculate direction preference using relative importance of horizontal and vertical
  br=as.numeric(calc.relimp(mRHV)$lmg)
  bl=as.numeric(calc.relimp(mLHV)$lmg)
  dir.imp.R<- atan2(br[2]*sign(RV),br[1]*sign(RH))*180/pi
  dir.imp.L<- atan2(bl[2]*sign(LV),bl[1]*sign(LH))*180/pi
  
  any.sig=RV.p<0.001 | LV.p<0.001| LH.p <0.001| RH.p<0.001
  R2R<-summary(mRHV)$r.squared
  R2L<- summary(mLHV)$r.squared
  
  #Calculate RMSE - compare with R-squared?
  # rmseR=sqrt(c(crossprod(mRHV$residuals))/mRHV$df.residual)
  # rmseL=sqrt(c(crossprod(mLHV$residuals))/mLHV$df.residual)
  rmseR=summary(mRHV)$sigma
  rmseL=summary(mLHV)$sigma
  
  #This data frame that I am returning is getting kind of big. 
  #I plan to remove the unused measurements once I am past the exploratory phase
  d<-data.frame(neuron=unique(x$neuron),
                RH=RH,RV=RV,LH=LH,LV=LV,dir.pref.R=dir.pref.R,dir.pref.L=dir.pref.L,
                RH.p=RH.p,LH.p=LH.p,RV.p=RV.p,LV.p=LV.p,any.sig=any.sig,
                R2R,R2L,dir.imp.R,dir.imp.L,
                rmseR=rmseR,rmseL=rmseL)
}
zp %>%
  group_by(neuron) %>%
  do(measureCell(.)) %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  zm

```


```{r plotting}

zm %>% 
  select(neuron,monkey,cellnum,R2R,R2L,dir.pref.R,dir.pref.L) %>% 
  mutate(r.skew=90-abs(dir.pref.R),
         l.skew=90-abs(dir.pref.L),
         m.skew=90-abs((dir.pref.R+dir.pref.L)/2))->
  skew

ggplot(skew)+
  geom_point(aes(m.skew,R2R))

ggplot(skew)+
  geom_point(aes(m.skew,R2R))+
  geom_point(aes(l.skew,R2L),color='blue')+
  geom_point(aes(r.skew,R2R),color='red')

ggplot(skew)+
  geom_point(aes(abs(m.skew),R2R))+
  stat_smooth(aes(abs(m.skew),R2R),se=FALSE)

zp<- filter(zp,dur>200,abs(mean.R.H)<50,abs(mean.L.H)<50,abs(mean.R.V)<50,abs(mean.L.V)<50,meanFR<500)

chosenCell='DC-915'

zm %>% filter(neuron==chosenCell) %>% select(neuron,R2R,R2L,dir.pref.R,dir.pref.L) %>% kable()


ggplot(zp %>% filter(neuron==chosenCell))+
  geom_point(aes(mean.R.H,meanFR),color='red')+
  geom_point(aes(mean.L.H,meanFR),color='blue')

ggplot(zp %>% filter(neuron==chosenCell))+
  geom_point(aes(mean.R.V,meanFR),color='red')+
  geom_point(aes(mean.L.V,meanFR),color='blue')

ggplot(zp %>% filter(neuron==chosenCell))+
  geom_point(aes(mean.V,meanFR),color='purple')+
  geom_point(aes(mean.H,meanFR),color='orange')+
  stat_smooth(aes(mean.V,meanFR),color='purple',method='lm')+
  stat_smooth(aes(mean.H,meanFR),color='orange',method='lm')

ggplot(zm %>% filter(neuron==chosenCell,any.sig))+
  geom_segment(aes(y=0,yend=1,x=dir.pref.R,xend=dir.pref.R),color='red')+
  geom_segment(aes(y=0,yend=1,x=dir.pref.L,xend=dir.pref.L),color='blue')+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  facet_wrap(~monkey)+
  theme_minimal()

ggplot(zm %>% filter(neuron==chosenCell))+
  geom_segment(aes(y=0,yend=1,x=dir.pref.R,xend=dir.pref.R),color='red')+
  geom_segment(aes(y=0,yend=1,x=dir.pref.L,xend=dir.pref.L),color='blue')+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  coord_polar(start=pi/2,direction=-1)+
  facet_wrap(~monkey)+
  theme_minimal()


zp %>% filter(neuron==chosenCell) %>% lm(meanFR~mean.R.V+mean.R.H,data=.) -> m

zp %>% filter(neuron==chosenCell) %>% mutate(pFR=predict(m,newdata=.))->
  zpp

qplot(mean.V,pFR,data=zpp)+geom_point(aes(mean.V,meanFR),color='hotpink')
qplot(mean.H,pFR,data=zpp)+geom_point(aes(mean.H,meanFR),color='hotpink')
```


```{r Unfinished}
#Analysis
"""
Based on the above plots and careful examination of the data, it seems that the most significant
difference between the normal INC cells and those found in strabismus is simply the goodness of the
position have such varied mean firing rates.
"""
#Bee-118 - oblique direction cell from a normal animal
#Bee-110 - perfect vertical (down) cell 

zp %>%
  group_by(neuron) %>%
  mutate(bin.R.V=cut(mean.R.V,seq(-25,25,by=10)))->
  zp
  
zp %>%
  # filter(neuron %in% c('Bee-110','Bee-118'),
  filter(neuron %in% c('DC-912','DC-915'),
         bin.R.V=='(-5,5]') %>%
  ggplot()+
  # geom_boxplot(aes(bin.R.V,meanFR,color=neuron))+
  geom_point(aes(mean.R.V,meanFR,color=neuron))

tt %>% 
  filter(neuron==chosenCell) %>%
  left_join(filter(zp,neuron==chosenCell),by='dsnum') ->
  tplot
  
tplot<-left_join(filter(t,neuron==chosenCell),filter(zp,neuron==chosenCell),by='dsnum')

tplot<-left_join(t,zp,by='dsnum')

tplot %>%
  group_by(dsnum) %>%
  mutate(counter=row_number(),
         dur=n()) %>%
  filter(dsnum<0)%>%
  # filter(dur<2000,dsnum<0,max(rep)<75)%>%
  ggplot()+
  geom_line(aes(counter,rep,group=dsnum))+
  geom_line(aes(counter,repV,group=dsnum))


blinks<-markSaccades(vtest$rep,buffer=80,threshold=70)
  
qplot(time,rep,data=vtest,geom='line')+
  geom_line(aes(time,lep),color='blue')+
  geom_point(aes(time,blinks*10))

vb<- replace(v,blinks>0,200)
bb<- markSaccadesDouble(vb,30,15)

qplot(time,rep,data=vtest,geom='line')+
  # geom_line(aes(time,lep),color='blue')+
  geom_point(aes(time,bb*10))

qplot(1:length(vb),vb,geom='line')
```