---
title: "Analysis of INC in strabismus"
author: "Adam Pallus"
output:
  pdf_document: default
  html_document: default
---
#Introduction
Previous work from our lab has shown that saccadic burst generators can have abnormal preferred directions in monkey models of infantile pattern strabismus. Additionally, microstimulation of the superior colliculus and saccadic burst generators can evoke disconjugate movements. This, along with behavioral evidence, suggests a neural origin of the "cross-talk" seen in pattern strabismus.

The intersitial nucleus of cajal (INC) is the location of the vertical neural integrator for eye position. If abnormal signals are present in the burst generators, then these signals should be integrated by the INC. In this report, we assess the direction preference of INC neurons in strabismus and compare with the normal monkey. 


```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE,cache=FALSE)
```

```{r,message=FALSE,echo=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
library(broom)
# library(grid)
library(relaimpo)
library(leaps)
library(stringr)
library(cladoRcpp)
library(boot)
source('Adamhelperfunctions.R')
select<- dplyr::select
```

```{r quickload,echo=FALSE,cache=TRUE}
LoadFromFile<- TRUE

if (LoadFromFile){
  o<- readRDS('INCstrab.RDS')
}else{
  o<-NULL
}

t<- loadnewcsv2(path="C:/Users/setup/Desktop/NRTP Vergence/INCstrab/",referencefile=o)


t<- rbind(o,t)

o<-NULL

```

```{r mark saccades,cache=TRUE}
#it would be really nice to fix this block so I don't have to use rbind at the end
#the problem was that some of the non-DC cells were erroring when I tried to run it through
#the blink detector... 
#An idea would be to set up a little function called markBlinks that just checks to see
#what the monkey is and just returns NA if it's not DC (or other visual tracking monkeys)
t %>%
  filter(monkey=='DC') %>%
  group_by(neuron) %>%
  mutate(blinks=markSaccades(rep,buffer=80,threshold=70),
         # dsnum=markSaccadesDouble(conj.velocity,threshold1=30,threshold2=15),
         dsnum=markSaccadesDouble(replace(conj.velocity,blinks>0,150),
                                  threshold1=30,threshold2=15,maxreject=100000),
         sdf=spikedensity(rasters,10),
         sdf10=lag(sdf,10),
         conj.vert=(repV+lepV)/2,
         conj.vert.vel=(revV+levV)/2,
         conj.hor=(rep+lep)/2,
         conj.hor.v=(rev+lev)/2) ->
  tdc

t %>%
  filter(monkey %in% c('Kopachuck','Bee')) %>%
  group_by(neuron) %>%
  mutate(dsnum=markSaccadesDouble(conj.velocity,threshold1=30,threshold2=15),
         sdf=spikedensity(rasters,10),
         sdf10=lag(sdf,10),
         conj.vert=(repV+lepV)/2,
         conj.vert.vel=(revV+levV)/2,
         conj.hor=(rep+lep)/2,
         conj.hor.v=(rev+lev)/2) ->
  tkb

t<- rbind(select(tdc,-blinks),tkb)
tdc<- NULL
tkb<- NULL
```

```{r Measure_Fixations,cache=TRUE}
t %>%
  group_by(neuron)%>%
  mutate(time=row_number()) %>%
  filter(dsnum<0) %>% #fixations only
  group_by(neuron,dsnum) %>%
  summarize(sd.conj.velocity=sd(conj.velocity),
            mean.conj.velocity=mean(conj.velocity),
            spread=max(conj.velocity)-min(conj.velocity),
            qrange=quantile(conj.velocity,0.975)-quantile(conj.velocity,0.025),
            dur=n(),
            starttime=first(time),
            c2eyes=cor(repV,lepV),
            meanFR=sum(rasters)/dur*1000,
            mean.V=mean(conj.vert),
            mean.H=mean(conj.hor),
            mean.R.H=mean(rep),
            mean.L.H=mean(lep),
            mean.R.V=mean(repV),
            mean.L.V=mean(lepV),
            mean.T.V=mean(tvp),
            mean.T.H=mean(thp),
            sd.sdf=sd(sdf10),
            asleep=sd.conj.velocity>7.5 || dur>2000)->
  zp


```

```{r Fixation_Analysis,cache=TRUE}
#In this chunk, we calculate direction preferences for each  neuron based on the measured fixations

measureCell<-function(x){
  #Remove bad fixations that are too short or are outside of the normal range of eye movements
  x<- filter(x,dur>200,abs(mean.R.H)<50,abs(mean.L.H)<50)
  
  #calculate linear regression models on horizontal, vertical and combined
  #calculate each eye separately 
  mRH<-lm(meanFR~mean.R.H,data=x)
  mLH<-lm(meanFR~mean.L.H,data=x)
  mRV<-lm(meanFR~mean.R.V,data=x)
  mLV<-lm(meanFR~mean.L.V,data=x)
  mRHV<-lm(meanFR~mean.R.H+mean.R.V,data=x)
  mLHV<-lm(meanFR~mean.L.H+mean.L.V,data=x)
  
  #Summarize desired information about models
  RH.p=anova(mRH)$'Pr(>F)'[1]
  LH.p=anova(mLH)$'Pr(>F)'[1]
  LV.p<- anova(mLV)$'Pr(>F)'[1]
  RV.p<- anova(mRV)$'Pr(>F)'[1]
  RH<-as.numeric(coef(mRHV)[2])
  RV<-as.numeric(coef(mRHV)[3]) 
  LH<-as.numeric(coef(mLHV)[2])
  LV<-as.numeric(coef(mLHV)[3])  
  
  #two methods to calculate direction preferences:

  #calculate direction preference using slopes of regression lines
  dir.pref.R<-as.numeric(atan2(RV,RH))*180/pi
  dir.pref.L<-as.numeric(atan2(LV,LH))*180/pi
  
  #calculate direction preference using relative importance of horizontal and vertical
  br=as.numeric(calc.relimp(mRHV)$lmg)
  bl=as.numeric(calc.relimp(mLHV)$lmg)
  dir.imp.R<- atan2(br[2]*sign(RV),br[1]*sign(RH))*180/pi
  dir.imp.L<- atan2(bl[2]*sign(LV),bl[1]*sign(LH))*180/pi
  
  any.sig=RV.p<0.001 | LV.p<0.001| LH.p <0.001| RH.p<0.001
  R2R<-summary(mRHV)$r.squared
  R2L<- summary(mLHV)$r.squared
  
  #Calculate RMSE - compare with R-squared?
  # rmseR=sqrt(c(crossprod(mRHV$residuals))/mRHV$df.residual)
  # rmseL=sqrt(c(crossprod(mLHV$residuals))/mLHV$df.residual)
  rmseR=summary(mRHV)$sigma
  rmseL=summary(mLHV)$sigma
  
  #Calculate relationship between firing rate and standard deviation
  msd=lm(sd.sdf~meanFR,data=x)
  sd.int=as.numeric(coef(msd)[1])
  sd.slope=as.numeric(coef(msd)[2])
  
  #This data frame that I am returning is getting kind of big. 
  #I plan to remove the unused measurements once I am past the exploratory phase
  d<-data.frame(neuron=unique(x$neuron),
                RH=RH,RV=RV,LH=LH,LV=LV,dir.pref.R=dir.pref.R,dir.pref.L=dir.pref.L,
                RH.p=RH.p,LH.p=LH.p,RV.p=RV.p,LV.p=LV.p,any.sig=any.sig,
                R2R,R2L,dir.imp.R,dir.imp.L,
                rmseR=rmseR,rmseL=rmseL,sd.int,sd.slope)
}
zp %>%
  group_by(neuron) %>%
  do(measureCell(.)) %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  zm

```

#Results

##Fixation Analysis
A significant challenge in comparing the activity of INC neurons between normal and strabismic animals is the variety of neuronal types present in the normal INC. So-called irregular cells have been identified with lower firing rates and less consistent firing rates. Some of these cells may be burst neurons that become tonically active when the animals are drowsy. Others may have activity related to the position or movement of the head. Fukushima (1990a) described pitch cells with higher coefficients of variation (standard deviation divided by mean of firing rate) and lower mean firing rates in cats. Because our animals did not move their heads.

Here is an example of a normal burst tonic cell:
```{r normalCell}
Ncell<- 'Bee-106'
Scell<- 'DC-902'

zp<- filter(zp,dur>200,abs(mean.R.H)<50,abs(mean.L.H)<50,abs(mean.R.V)<50,abs(mean.L.V)<50,meanFR<500)

nV<-ggplot(zp %>% filter(neuron==Ncell))+
  geom_point(aes(mean.V,meanFR),color='purple')+
  xlab('Mean Vertical Eye Position')

nH<-ggplot(zp %>% filter(neuron==Ncell))+
  geom_point(aes(mean.H,meanFR),color='orange')+
  xlab('Mean Horizontal Eye Position')

sV<-ggplot(zp %>% filter(neuron==Scell))+
  geom_point(aes(mean.V,meanFR),color='purple')+
  xlab('Mean Vertical Eye Position')

sH<-ggplot(zp %>% filter(neuron==Scell))+
  geom_point(aes(mean.H,meanFR),color='orange')+
  xlab('Mean Horizontal Eye Position')

multiplot(nV,sV,nH,sH,cols=2)


```

<!-- ```{r plotting} -->

<!-- zm %>%  -->
<!--   select(neuron,monkey,cellnum,R2R,R2L,dir.pref.R,dir.pref.L) %>%  -->
<!--   mutate(r.skew=90-abs(dir.pref.R), -->
<!--          l.skew=90-abs(dir.pref.L), -->
<!--          m.skew=90-abs((dir.pref.R+dir.pref.L)/2))-> -->
<!--   skew -->

<!-- ggplot(skew)+ -->
<!--   geom_point(aes(m.skew,R2R)) -->

<!-- ggplot(skew)+ -->
<!--   geom_point(aes(m.skew,R2R))+ -->
<!--   geom_point(aes(l.skew,R2L),color='blue')+ -->
<!--   geom_point(aes(r.skew,R2R),color='red') -->

<!-- ggplot(skew)+ -->
<!--   geom_point(aes(abs(m.skew),R2R))+ -->
<!--   stat_smooth(aes(abs(m.skew),R2R),se=FALSE) -->

<!-- zp<- filter(zp,dur>200,abs(mean.R.H)<50,abs(mean.L.H)<50,abs(mean.R.V)<50,abs(mean.L.V)<50,meanFR<500) -->

<!-- chosenCell='DC-915' -->

<!-- zm %>% filter(neuron==chosenCell) %>% select(neuron,R2R,R2L,dir.pref.R,dir.pref.L) %>% kable() -->


<!-- ggplot(zp %>% filter(neuron==chosenCell))+ -->
<!--   geom_point(aes(mean.R.H,meanFR),color='red')+ -->
<!--   geom_point(aes(mean.L.H,meanFR),color='blue') -->

<!-- ggplot(zp %>% filter(neuron==chosenCell))+ -->
<!--   geom_point(aes(mean.R.V,meanFR),color='red')+ -->
<!--   geom_point(aes(mean.L.V,meanFR),color='blue') -->

<!-- ggplot(zp %>% filter(neuron==chosenCell))+ -->
<!--   geom_point(aes(mean.V,meanFR),color='purple')+ -->
<!--   geom_point(aes(mean.H,meanFR),color='orange')+ -->
<!--   stat_smooth(aes(mean.V,meanFR),color='purple',method='lm')+ -->
<!--   stat_smooth(aes(mean.H,meanFR),color='orange',method='lm') -->

<!-- ggplot(zm %>% filter(neuron==chosenCell,any.sig))+ -->
<!--   geom_segment(aes(y=0,yend=1,x=dir.pref.R,xend=dir.pref.R),color='red')+ -->
<!--   geom_segment(aes(y=0,yend=1,x=dir.pref.L,xend=dir.pref.L),color='blue')+ -->
<!--   scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+ -->
<!--   coord_polar(start=pi/2,direction=-1)+ -->
<!--   facet_wrap(~monkey)+ -->
<!--   theme_minimal() -->

<!-- ggplot(zm %>% filter(neuron==chosenCell))+ -->
<!--   geom_segment(aes(y=0,yend=1,x=dir.pref.R,xend=dir.pref.R),color='red')+ -->
<!--   geom_segment(aes(y=0,yend=1,x=dir.pref.L,xend=dir.pref.L),color='blue')+ -->
<!--   scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+ -->
<!--   coord_polar(start=pi/2,direction=-1)+ -->
<!--   facet_wrap(~monkey)+ -->
<!--   theme_minimal() -->


<!-- zp %>% filter(neuron==chosenCell) %>% lm(meanFR~mean.R.V+mean.R.H,data=.) -> m -->

<!-- zp %>% filter(neuron==chosenCell) %>% mutate(pFR=predict(m,newdata=.))-> -->
<!--   zpp -->

<!-- qplot(mean.V,pFR,data=zpp)+geom_point(aes(mean.V,meanFR),color='hotpink') -->
<!-- qplot(mean.H,pFR,data=zpp)+geom_point(aes(mean.H,meanFR),color='hotpink') -->
<!-- ``` -->

<!-- ```{r multiplot} -->
<!-- for (chosenCell in unique(zp$neuron)){ -->
<!--   print( -->
<!-- ggplot(zp %>% filter(neuron==chosenCell))+ -->
<!--   geom_point(aes(mean.V,meanFR),color='purple')+ -->
<!--   geom_point(aes(mean.H,meanFR),color='orange')+ -->
<!--   stat_smooth(aes(mean.V,meanFR),color='purple',method='lm')+ -->
<!--   stat_smooth(aes(mean.H,meanFR),color='orange',method='lm')+ -->
<!--   ggtitle(chosenCell) -->
<!-- )} -->
<!-- ``` -->

<!-- ```{r boxplots} -->
<!-- #Analysis -->
<!-- # """ -->
<!-- # Based on the above plots and careful examination of the data, it seems that the most significant -->
<!-- # difference between the normal INC cells and those found in strabismus is simply the goodness of the -->
<!-- # position have such varied mean firing rates. -->
<!-- # """ -->
<!-- #Bee-118 - oblique direction cell from a normal animal -->
<!-- #Bee-110 - perfect vertical (down) cell  -->

<!-- zp %>% -->
<!--   group_by(neuron) %>% -->
<!--   mutate(bin.R.V=cut(mean.R.V,seq(-25,25,by=10)))-> -->
<!--   zp -->

<!-- for (chosenCell in unique(zp$neuron)){ -->
<!--   print(   -->
<!-- zp %>% -->
<!--   filter(neuron==chosenCell, -->
<!--          !is.na(bin.R.V)) %>% -->
<!--   # filter(neuron %in% c('Bee-110','Bee-118'), -->
<!--   # filter(neuron %in% c('DC-912','DC-915'), -->
<!--   #        bin.R.V=='(-5,5]') %>% -->
<!--   ggplot()+ -->
<!--   geom_boxplot(aes(bin.R.V,meanFR,color=neuron))#+ -->
<!--   # geom_point(aes(mean.R.V,meanFR,color=neuron)) -->
<!-- )} -->
<!-- ``` -->

<!-- ```{r irregular} -->
<!-- #This chunk I will use to estimate the standard deviation of the firing rate during fixation. -->
<!-- #The hypothesis is that the irregular cells have more variability of the ISI -->
<!-- #Cells where there are missing spikes seem to show reduced variability at higher firing rates -->
<!-- #so just fit a linear model and look at the intercept and the  -->
<!-- slope -->
<!-- ``` -->

<!-- ```{r unfinished} -->
<!-- chosenCell='Bee-108' -->
<!-- t %>%  -->
<!--   filter(neuron==chosenCell) %>% -->
<!--   left_join(filter(zp,neuron==chosenCell),by='dsnum') -> -->
<!--   tplot -->

<!-- tplot %>% -->
<!--   group_by(dsnum) %>% -->
<!--   mutate(counter=row_number(), -->
<!--          dur=n(), -->
<!--          sd.sdf=sd(sdf10))-> -->
<!--   tplot -->

<!-- tplot%>% -->
<!--   filter(dsnum<0)%>% -->
<!--   # filter(dur<2000,dsnum<0,max(rep)<75)%>% -->
<!--   ggplot()+ -->
<!--   geom_line(aes(counter,rep,group=dsnum))+ -->
<!--   geom_line(aes(counter,repV,group=dsnum))+ -->
<!--   ggtitle('Eye position during identified fixations- a test of the algorithm') -->


<!-- tplot %>% -->
<!--   mutate(showrasters=replace(rasters,rasters<1,NA)) %>% -->
<!--   filter(dsnum<0,dur<1000,dur>200,bin.R.V=='(-5,5]')%>% -->
<!--   ggplot()+ -->
<!--   geom_point(aes(counter,showrasters*meanFR,color=as.factor(dsnum)),shape='|')+ -->
<!--   theme_minimal()+ -->
<!--   ggtitle('Spike rasters during fixations within 5 degrees of centered vertically')+ -->
<!--   theme(legend.position='none')+ -->
<!--   xlab(chosenCell) -->

<!-- tplot %>% -->
<!--   filter(dsnum<0) %>% -->
<!--   group_by(dsnum) %>% -->
<!--   summarize_each(funs(first))-> -->
<!--   stplot -->

<!-- qplot(meanFR, sd.sdf,data=stplot) -->

<!-- ggplot(zm,aes(sd.slope,R2R))+ -->
<!--   geom_text(aes(label=neuron),data=filter(zmm,abs(sd.slope)>0.15))+ -->
<!--   geom_point(size=3,aes(color=abs(90-abs(dir.imp.R)))) -->



<!-- #The ultimate goal here is to try to identify what the unexplained variance is caused by -->

<!-- #This may be a goal that needs to be abandoned. If the other variance is due to factors that we don't record, such as body position, torsion, etc, then we will just have to call them irregular cells.  -->

<!-- #King et al 1981 suggests that irregular cells are related to eye position during pursuit but not spontaneous movement. I wonder why.  -->

<!-- ``` -->

<!-- ```{r CV} -->

<!-- for (chosenCell in unique(zp$neuron)){ -->
<!--   print(   -->
<!--     zp %>% -->
<!--       filter(neuron==chosenCell,meanFR>1) %>% -->
<!--       ggplot()+ -->
<!--       geom_point(aes(mean.V,sd.sdf/meanFR))+ -->
<!--       ggtitle(chosenCell) -->
<!--   )} -->
<!-- ``` -->