---
title: "Gaze Shifts"
author: "Adam"
date: "January 26, 2018"
output: 
html_document: 
self_contained: no
runtime: shiny
---

* Thick gray line is target position.
* Green line is gaze position.
* Blue line is head position.
* Dashed green line is gaze velocity (plotted 1/10th scale)
* Dashed blue line is head velocity (plotted 1/10th scale)  
     + The highlighted segments of the gaze and head velocity traces are the identified movements.
     + The first eye-saccade and head movement that occur after the target moves is marked on the velocity trace.
     + Additional saccades and head movements are marked with horizontal lines
     + Trials where there is missing data within the first 1000 ms of the target's movement are labeled


```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE)
```

```{r,message=FALSE}

library(ggplot2)
library(dplyr)
#library(knitr)
#library(tidyr)
#library(broom)
#library(grid)
# library(relaimpo)
# library(leaps)
#library(data.table)

```


```{R SHINYTRY, warning=FALSE}
#In order to make the shiny app load fast, I'm just saving the output. See BoostrapSaccades.Rmd for the actual analysis.
# z<-readRDS(file="Bee13forshiny.RDS")
# hh<- readRDS('knightdemo.RDS')
hh<- readRDS('knightdemo2.RDS')

plotTrial<- function(hh){
  # cat(hh$blinktrial[1])
  gp<- ggplot(hh)+
    geom_line(aes(tcounter,H),color='blue')+
    # geom_line(aes(tcounter,Ef),color='red')+
    geom_line(aes(tcounter,G),color='darkgreen')+
    geom_line(aes(tcounter,T),size=2,alpha=0.5)+
    geom_line(aes(tcounter,Hv/10),color='blue',linetype=2)+
    # geom_line(aes(tcounter,EV/10),color='red')+
    geom_line(aes(tcounter,Gv/10),color='darkgreen',linetype=2)+
    # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
    geom_point(aes(tcounter,sign(gazeshifts)*50),color='darkgreen')+
    geom_point(aes(tcounter,sign(headmovement)*25),color='blue')+
    geom_line(aes(tcounter,sign(primarygazeshifts)*Gv/10),size=2,color='darkgreen',alpha=0.5)+
    # geom_line(aes(tcounter,sign(gazeshifts)*Gv/10),size=2,color='yellow',alpha=0.5)+
    geom_line(aes(tcounter,sign(primaryheadmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
    xlab('Time (ms)')
    
    # geom_line(aes(tcounter,sign(headmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
    blink<- hh$blinktrial[1]
    if(blink | is.na(blink)){
      gp<-gp+geom_label(x=0,y=0,label='BLINK INTERRUPTED')
    }
    gp
    
}


inputPanel(
  
  selectInput(inputId= 'blockChoice',
              label='Choose block:',
              choices=list('A-01','A-02')),
  
  sliderInput("TrialChoice", label = "Select a movement:",
              min=1,
              max=length(unique(hh$sacnum)),
              value=1,
              step=1)
  

)

renderPlot({
  
    chosentrial<-input$TrialChoice
    blockchoice<- input$blockChoice
    
    plotTrial(filter(hh,sacnum==chosentrial,block==blockchoice))
    # 
    # ggplot(filter(hh,sacnum==chosentrial))+
    #           geom_line(aes(counter,H),color='blue')+
    #          # geom_line(aes(counter,Ef),color='red')+
    #          geom_line(aes(counter,G),color='darkgreen')+
    #          geom_line(aes(counter,T),size=2,alpha=0.5)+
    #          geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
    #          # geom_line(aes(counter,EV/10),color='red')+
    #          geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
    #          # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
    #          # geom_text(x=0,y=60,aes(label=firstshift[1]))+
    #          geom_line(aes(counter,sign(gazeshifts)*Gv/10),size=2,color='darkgreen',alpha=0.5)+
    #          geom_line(aes(counter,sign(headmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
    #   theme_minimal()

})

```



