---
title: "Gaze Shift Analysis"
author: "Adam Pallus"
output: 
  html_document: 
    keep_md: yes
  pdf_document: 
    highlight: espresso
---
#Introduction
I wrote up a quick analysis in R that should demonstrate the possibilities of automating this process. I've included the source code in this document, but we could do the same kind of analysis in Matlab. I'm just currently using R more for this kind of stuff and I think it will take a few more lines of code to work with Matlab. 

##Process:

* load text file
* take gaze, head and target position columns
* calculate velocity by convolving with a parabola (smoothing)
* identify when the target changes position 
* break file into "trials" consisting of 200ms before target movement and 600ms after
* mark gaze shifts using a two-threshold algorithm 
* mark head movements using same algorithm with lower thresholds
* Identify the "first" gaze shift that happens after target movement
* measure onsets/offsets/durations etc
* make plots

```{r setup, include=FALSE,message=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(knitr)
library(tidyr)
library(manipulate)
# library(broom)
# library(grid)
# library(relaimpo)
# library(leaps)
#library(data.table)
# library(stringr)
library(dplyr)
library(cladoRcpp)
select<-dplyr::select
# source('joinsaccadesuniform.R')
source('Adamhelperfunctions.R')
source('markSaccadesDouble2.R')
markTagetMovements<-function(t,buffer=200,threshold=1000,saccade.length=1000){
  
  findSaccades<-function(ev,threshold=40){
    mindur<- 1
    i<-which(abs(ev)>threshold) #find all the times when speed > threshold
    sacoff<-which(diff(i)>mindur) #minimum duration of an accepted saccade
    sacon<-c(1,sacoff+1) #first saccade
    sacoff<-c(sacoff,length(i)) #end of last saccade
    saccade.onset<-i[sacon] #get actual times
    saccade.offset<-i[sacoff] 
    
    return(data.frame(saccade.onset,saccade.offset))
  }
  
  jsac<- function(stimes){
    summary(stimes)
    #input should be an array of length 2: c(onsettime,offsettime, saccade.number,saccade.dur)
    df<- data.frame(time=stimes[[1]]:stimes[[2]])
    df$sacnum<- stimes[[4]]
    df$saccade.dur<- stimes[[3]]
    return(df)
    # return(stimes[[1]]:stimes[[2]])
  }
  
  stimes<-findSaccades(t$target.velocity,threshold)
  stimes %>%
    mutate(dur=saccade.offset-saccade.onset,
           s=row_number(),
           saccade.onset=saccade.onset-buffer,
           ###########HERE IS WHERE i MAKE SACCADES UNIFORM #######
           saccade.offset=saccade.onset+saccade.length+2*buffer)->
    stimes
  
  x<- as.data.frame(rbindlist(apply(stimes,1,jsac)))
  x %>%
    group_by(sacnum) %>%
    mutate(counter=time-first(time)) ->
    x
  left_join(t,x,by='time')
}

loadnewheadfree<- function(referencefile=NULL,path="~/kdata/"){
  require(stringr)
  require(dplyr)
  #This function loads .csv files in a particular folder. They must have the same columns for rbind
  #Saves time by only reading the csv when necessary
  
  #get names of all files in path
  files <- list.files(path=path,pattern='*.txt')
  #extract neuron name eg. Bee-01
  names<-sapply(files, str_match,"^[a-zA-Z]+-[0-9]+",USE.NAMES=FALSE)
  # check for new cells
  if (!is.null(referencefile)){
    files<-files[!names %in% referencefile$neuron] #comparison
  }
  
  nfiles<-length(files)
  
  if (nfiles>0){
    message(c('New Files: ',files))
    loadedfiles <- lapply(paste(path,files,sep=''),read.csv,sep='\t',header=FALSE)
    t<-data.frame()
    temp<- NULL
    # t.old<-NULL
    for (i in 1:nfiles) {
      f<- files[i]
      message(paste('Loading:',f))
      # temp[[i]]=loadedfiles[[i]]
      names<-str_match(f,"(^[a-zA-Z]+)-([0-9]+)")
      loadedfiles[[i]]$block<-names[1]
      loadedfiles[[i]]$subject<-names[2]
      loadedfiles[[i]]$blocknum<-as.numeric(names[3])
      
    }
    t <-rbindlist(loadedfiles)
    # t<- dplyr::select(t, -thp,-tvp,-time)
  }else{
    message('********NO NEW DATA********')
    t<-NULL
  }
  return(t)
}
```

```{r load}
samplerate<- 304.7508/1000
# path<- "C:/Users/User/Documents/GitHub/NPH-Analysis/Vergence/kdata/"
path<-"C:/Users/setup/Desktop/NRTP Vergence/kdata/"
h<- loadnewheadfree(NULL,path)

# h<- read.csv('HEADFREE.txt',sep="\t",header=FALSE)
h<- select(h,-V9)
names(h)<- c('G','GV','H','HV','E','EV','time','T','block','subject','blocknum')



h %>% 
  # filter(block=='A-02')%>%
  select(G,H,T,block) %>% #these are the only data we need 
  group_by(block) %>%
  mutate(G=replace(G,G==0,NA), #mark missing data as NA rather than 0
         #G=na.approx(G,na.rm=FALSE),
         time=row_number(),
         Gv=parabolicdiff(G,7)*samplerate, #calculate velocity
         Hv=parabolicdiff(H,7)*samplerate,
         target.velocity=parabolicdiff(T,7)*samplerate,
         # gazeshifts=markSaccades(Gv,buffer=5,threshold=30),
         gazeshifts=markSaccadesDouble(Gv,threshold1=100,threshold2=10),
         headmovement=markSaccadesDouble(Hv,threshold1=10,threshold2=4),
         #algorithm marks non-movements (fixations) as negative so remove them
         headmovement=replace(headmovement,headmovement<0,0), 
         gazeshifts=replace(gazeshifts,gazeshifts<0,0)) ->
  htesta

htesta%>%
  # filter(block=='A-02')%>%
  group_by(block) %>%
  #identify movements and mark 200ms before and 500ms after each movement as "sacnum"
  do(markTagetMovements(t=.,buffer=200,threshold=200,saccade.length=500)) ->
  htest

htest%>%
  filter(!is.na(sacnum))%>% #get rid of all data that isn't part of the marked target movement periods
  group_by(block,sacnum) %>% #look at each target movement individually
  #time of first gaze shift - we want to ignore gaze shifts that start before the target actually moved
  mutate(firstshift=min(gazeshifts[counter>220&gazeshifts>0],na.rm=T), 
         firsthead=min(headmovement[counter>220&headmovement>0],na.rm=T),
         primarygazeshifts=replace(gazeshifts,
                            gazeshifts!=firstshift|is.na(firstshift),
                            0), #the first "eye saccade" we're calling the primary gaze shift
         primaryheadmovement=replace(headmovement,
                                      headmovement!=firsthead|is.na(firsthead),
                                      0),
         #for easier analysis/plotting, use NA rather than 0 for non-movements 
         gazeshifts=replace(gazeshifts,gazeshifts==0,NA),
         primarygazeshifts=replace(primarygazeshifts,primarygazeshifts==0,NA),
         headmovement=replace(headmovement,headmovement==0,NA),
         primaryheadmovement=replace(primaryheadmovement,primaryheadmovement==0,NA),
         counter=counter-200,
         tcounter=round(counter/samplerate))->
  hh
```

```{r measure}

# hh %>% 
#   group_by(block,sacnum) %>%
#   mutate(gvsd=round(sd(Gv[1:300])))->
#   hh

#this block just gets rid of all trials where there is no detected gaze shift
#I did this as a separate block to avoid errors in the larger measurement 
hh %>% 
  # filter(sacnum==10)%>%
  group_by(block,sacnum) %>%
  mutate(gaze.dur=length(counter[!is.na(gazeshifts)])) %>%
  ungroup() %>%
  filter(gaze.dur>1) ->
  hint

hint%>%
  group_by(block,sacnum)%>%
  #We're going to measure the trial now and just report the measurements in the data frame "hp"
  summarize(blinktrial=any(is.na(G[counter>0&counter<300])),
            gaze.onset=counter[!is.na(primarygazeshifts)][1],
         gaze.offset=max(counter[!is.na(primarygazeshifts)]),
         total.gaze.offset=max(counter[!is.na(gazeshifts)]),
         gaze.dur=gaze.offset-gaze.onset,
         gaze.dur.ms=gaze.dur/samplerate,
         gaze.amp=G[counter==gaze.offset]-G[counter==gaze.onset],
         total.gaze.amp=G[counter==total.gaze.offset]-G[counter==gaze.onset],
         IHP=H[counter==gaze.onset],
         IGP=G[counter==gaze.onset],
         IEP=IGP-IHP,
         IEPs=IEP*sign(gaze.amp), #positive number indicates eyes deviated in direction of saccade
         peak.gaze.velocity=maxabs(Gv[!is.na(gazeshifts)]),
         peak.head.velocity=maxabs(Hv[100:n()]),
         target.amp=T[300]-T[1],
         head.contribution=H[counter==gaze.offset]-IHP,
         eye.contribution=gaze.amp-head.contribution
         ) %>%
  #junk any trials where there is no gaze shift within 200 samples (~650ms) of target movement
  filter(gaze.onset>0,gaze.onset<200)->
  hp
hh <- left_join(hh,hp) #add mesurements back to original data file

goodsacs=unique(hp$sacnum)
goodsacs=unique(filter(hp,gaze.dur.ms>250)$sacnum)
goodsacs=unique(filter(hp,gaze.dur.ms<200,IEPs>20))$sacnum
```

##Example plot
Here is an example of a trial with the first gaze shift and head movement marked.
Velocity is shown on the same plot as position scaled down by a factor of 10.

```{r demoplot,echo=FALSE,warning=FALSE}

plotTrial<- function(hh){
  # cat(hh$blinktrial[1])
  gp<- ggplot(hh)+
    geom_line(aes(counter,H),color='blue')+
    # geom_line(aes(counter,Ef),color='red')+
    geom_line(aes(counter,G),color='darkgreen')+
    geom_line(aes(counter,T),size=2,alpha=0.5)+
    geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
    # geom_line(aes(counter,EV/10),color='red')+
    geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
    # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
    geom_point(aes(counter,sign(gazeshifts)*50),color='darkgreen')+
    geom_point(aes(counter,sign(headmovement)*25),color='blue')+
    geom_line(aes(counter,sign(primarygazeshifts)*Gv/10),size=2,color='darkgreen',alpha=0.5)+
    # geom_line(aes(counter,sign(gazeshifts)*Gv/10),size=2,color='yellow',alpha=0.5)+
    geom_line(aes(counter,sign(primaryheadmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
    xlab('Time (ms)')+
    
  # geom_line(aes(counter,sign(headmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
  blink<- hh$blinktrial[1]
  if(blink | is.na(blink)){
    gp<-gp+geom_label(x=0,y=0,label='BLINK INTERRUPTED')
  }
  gp
  
}

plotTrial<- function(hh){
  # cat(hh$blinktrial[1])
  gp<- ggplot(hh)+
    geom_line(aes(tcounter,H),color='blue')+
    # geom_line(aes(tcounter,Ef),color='red')+
    geom_line(aes(tcounter,G),color='darkgreen')+
    geom_line(aes(tcounter,T),size=2,alpha=0.5)+
    geom_line(aes(tcounter,Hv/10),color='blue',linetype=2)+
    # geom_line(aes(tcounter,EV/10),color='red')+
    geom_line(aes(tcounter,Gv/10),color='darkgreen',linetype=2)+
    # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
    geom_point(aes(tcounter,sign(gazeshifts)*50),color='darkgreen')+
    geom_point(aes(tcounter,sign(headmovement)*25),color='blue')+
    geom_line(aes(tcounter,sign(primarygazeshifts)*Gv/10),size=2,color='darkgreen',alpha=0.5)+
    # geom_line(aes(tcounter,sign(gazeshifts)*Gv/10),size=2,color='yellow',alpha=0.5)+
    geom_line(aes(tcounter,sign(primaryheadmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
    xlab('Time (ms)')
    
    # geom_line(aes(tcounter,sign(headmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
    blink<- hh$blinktrial[1]
    if(blink | is.na(blink)){
      gp<-gp+geom_label(x=0,y=0,label='BLINK INTERRUPTED')
    }
    gp
    
}

plotTrial(filter(hh,sacnum==31,block=='A-01'))

ggplot(filter(hh,sacnum==31,block=='A-01'))+
  geom_line(aes(counter,H),color='blue')+
  # geom_line(aes(counter,Ef),color='red')+
  geom_line(aes(counter,G),color='darkgreen')+
  geom_line(aes(counter,T),size=2,alpha=0.5)+
  geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
  # geom_line(aes(counter,EV/10),color='red')+
  geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
  # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
  geom_point(aes(counter,sign(gazeshifts)*50),color='darkgreen')+
  geom_point(aes(counter,sign(headmovement)*25),color='blue')+
  annotate('text',x=-100,y=50,label='Target Position')+
  annotate('text',x=500,y=20,label='Head Position')+
  annotate('text',x=320,y=5,label='Head Velocity')+
  annotate('text',x=270,y=40,label='Gaze Velocity')+
  annotate('text',x=250,y=70,label='Gaze Position')+
  annotate('text',x=125,y=55,label='First Gaze Shift')+
  annotate('text',x=300,y=28,label='Head Movement')+
  geom_line(aes(counter,sign(primarygazeshifts)*Gv/10),size=2,color='darkgreen',alpha=0.5)+
  # geom_line(aes(counter,sign(gazeshifts)*Gv/10),size=2,color='yellow',alpha=0.5)+
  geom_line(aes(counter,sign(primaryheadmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
  # geom_line(aes(counter,sign(headmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
  geom_label(aes(label=paste0('Target Amplitude: ',T[300]-T[1]),x=0,y=-50))+
  geom_label(aes(label=paste0('Total Gaze Amplitude: ',total.gaze.amp),x=0,y=-60))

library(manipulate)
manipulate(plotTrial(filter(hh,sacnum==trialchoice,block==blockchoice)),
           trialchoice=slider(1,max = max(hh$sacnum),step=1),
           blockchoice=picker('A-01','A-02'))
                            
plotTrial(filter(hh,sacnum==31,block=='A-01'))
  

```

#Summary Figures
Some simple summary figures

```{r SummaryFigures,warning=FALSE}

hpp<- filter(hp,gaze.dur/samplerate<400)

qplot(gaze.onset/samplerate,bins=30,data=hpp,fill=blinktrial,position='dodge')+
  xlab('Gaze Shift Latency (ms)')+
  facet_wrap(~block)

qplot(IEP,peak.head.velocity,data=hpp)
qplot(IEP,peak.gaze.velocity,data=hpp)

ggplot(aes(gaze.dur/samplerate,abs(peak.gaze.velocity)),
       data=hpp)+
  geom_point()+
  stat_smooth(method='lm',se=FALSE)+
  xlab('Gaze Shift duration (ms)')+
  ylab('Peak Gaze Velocity (deg/s)')+
  facet_wrap(~block)

ggplot(aes(gaze.amp,peak.gaze.velocity),data=hpp)+
  geom_point()+
  # stat_smooth(method='lm',se=FALSE)+
  # ggtitle('Main Sequence')+
  xlab('Gaze Shift Amplitude (deg)')+
  ylab('Peak Gaze Velocity (deg/s)')+
  facet_wrap(~block)

ggplot(aes(abs(gaze.amp),abs(peak.gaze.velocity)),data=hpp)+
  geom_point()+
  stat_smooth(method='lm',se=FALSE)+
  stat_smooth(color='red',se=FALSE)+
  ggtitle('Main Sequence')+
  xlab('Gaze Shift Amplitude (deg)')+
  ylab('Peak Gaze Speed (deg/s)')+
  facet_wrap(~block)
    
ggplot(aes(abs(gaze.amp),head.contribution/gaze.amp),data=hpp)+
  geom_point()+facet_wrap(~block)

ggplot(aes(IEPs,head.contribution),data=hpp)+
  geom_point()+facet_wrap(~block)

qplot(abs(gaze.amp),abs(gaze.amp)-abs(head.contribution),color=IEP,data=hpp)+
  geom_abline()+facet_wrap(~block)

```

```{r requestedplots}

ggplot(hpp,aes(gaze.amp,color=block))+
  geom_density()

ggplot(hpp,aes(target.amp,color=block))+
  geom_density()
# 
# a. comparison of pre and post mean Gaze peak velocity
ggplot(hpp,aes(abs(gaze.amp),abs(peak.gaze.velocity),color=block))+
  geom_point()+
  stat_smooth(method='lm')+
  xlab('Gaze shift amplitude (deg)')+
  ylab('Peak gaze shift velocity (deg/s)')
# b. comparison of pre and post mean Gaze latency
ggplot(hpp,aes(abs(gaze.amp),gaze.onset/samplerate,color=block))+
  geom_point()+
  stat_smooth(method='lm')+
  xlab('Gaze shift latency (ms)')+
  ylab('Gaze shift amplitude (deg)')

# c. comparison of pre and post mean primary Gaze gain
ggplot(hpp,aes(abs(target.amp),abs(gaze.amp),color=block))+
  geom_point()+
  geom_abline()+
  stat_smooth(method='lm')+
  xlab('target amplitude (deg)')+
  ylab('Gaze shift amplitude (deg)')+
  annotate('text',30,80,label='First saccade only; both directions')
# 
# d. comparison of pre and post mean Head peak velocity
ggplot(hpp,aes(abs(gaze.amp),abs(peak.head.velocity),color=block))+
  geom_point()+
  stat_smooth(method='lm')+
  xlab('Gaze shift amplitude (deg)')+
  ylab('Peak head speed (deg/s)')
# e.comparison of pre and post mean Head latency

# f. comparison of pre and post mean head contribution to gaze\
ggplot(hpp,aes(abs(gaze.amp),abs(head.contribution),color=block))+
  geom_point()+
  stat_smooth(method='lm')+
  xlab('Gaze shift amplitude (deg)')+
  ylab('Head Contribution (deg)')

ggplot(filter(hpp,abs(head.contribution)<10),aes(abs(gaze.amp),abs(head.contribution),color=block))+
  geom_point()+
  stat_smooth(method='lm')+
  xlab('Gaze shift amplitude (deg)')+
  ylab('Head Contribution (deg)')+
  ggtitle('Outliers removed')

# g. comparison of pre and post mean head contribution gain
# h. comparison of pre and post mean head total amp

# i. comparison of pre and post mean head total amp gain
# 
# j. comparison of pre and post mean final eye position re: head
```

```{r boxplots}

hpp <- mutate(hpp,amp.bins.right=cut(gaze.amp,breaks=c(0,10,20,30,40,50,60,70)))
hpp <- mutate(hpp,amp.bins.left=cut(gaze.amp,breaks=c(0,-10,-20,-30,-40,-50,-60,-70)))
hpp <- mutate(hpp,amp.bins=cut(gaze.amp,breaks=c(-70,-60,-50,-40,-30,-20,-10,0,10,20,30,40,50,60,70)))

# hpp<-mutate(hpp,amp.bins=cut(gaze.amp,breaks=c(-75,-50,-25,-10,0,10,25,50,75)))
# hpp<- mutate(hpp,amp.bins=cut(abs(gaze.amp),breaks=c(0,10,20,30,40,50,60,70)))
# hpp <- mutate(hpp,amp.bins=cut(abs(target.amp),breaks=c(0,10,20,30,40,50,60,70)))


ggplot(filter(hpp,!is.na(amp.bins)))+
  geom_boxplot(aes(amp.bins,gaze.onset/samplerate,color=block))+
  ylab('Gaze Shift Latency (ms)')+
  xlab('Gaze shift amplitude bins (deg)')

ggplot(filter(hpp,!is.na(amp.bins)))+
  geom_boxplot(aes(amp.bins,head.contribution,color=block))+
  ylab('Head Contribution (deg)')+
  xlab('Gaze shift amplitude bins (deg)')

ggplot(filter(hpp,!is.na(amp.bins.right)))+
  geom_boxplot(aes(amp.bins.right,gaze.onset/samplerate,color=block))+
  ylab('Gaze Shift Latency (ms)')+
  xlab('Gaze shift amplitude bins (deg)')

ggplot(filter(hpp,!is.na(amp.bins.right)))+
  geom_boxplot(aes(amp.bins.right,head.contribution,color=block))+
  ylab('Head Contribution (deg)')+
  xlab('Gaze shift amplitude bins (deg)')

ggplot(filter(hpp,!is.na(amp.bins.left)))+
  geom_boxplot(aes(amp.bins.left,gaze.onset/samplerate,color=block))+
  ylab('Gaze Shift Latency (ms)')+
  xlab('Gaze shift amplitude bins (deg)')

ggplot(filter(hpp,!is.na(amp.bins.left)))+
  geom_boxplot(aes(amp.bins.left,head.contribution,color=block))+
  ylab('Head Contribution (deg)')+
  xlab('Gaze shift amplitude bins (deg)')

# ggplot(filter(hpp))+
#   geom_boxplot(aes(target.amp,gaze.onset/samplerate,color=block))
# 
# ggplot(filter(hpp))+
#   geom_boxplot(aes(as.factor(target.amp),gaze.onset/samplerate,color=block))

hpp %>%
  filter(is.na(amp.bins)) %>%
  group_by(block,amp.bins)%>%
  summarize(n=n())->
  tcount

hpp %>%
  filter(!is.na(amp.bins)) %>%
  group_by(amp.bins) %>%
  do(g.onset=t.test(gaze.onset~block,data=.),
     hc=t.test(head.contribution~block,data=.))->
  hps

g.onset.t.test<- select(tidy(hps,g.onset),amp.bins,p.value)
g.onset.t.test<- rename(g.onset.t.test,GS_Latency_p_value=p.value)
h.contri.t.test<- select(tidy(hps,hc),amp.bins,p.value)
h.contri.t.test<- rename(h.contri.t.test,H_Contribution_p_value=p.value)
kable(g.onset.t.test)
kable(h.contri.t.test)

hpp %>%
  ungroup()%>%
  filter(!is.na(amp.bins)) %>%
  do(g.onset=t.test(gaze.onset~block,data=.),
     hc=t.test(head.contribution~block,data=.))->
  hpsa


ggplot(filter(hpp,!is.na(amp.bins)))+
  geom_boxplot(aes(block,gaze.onset/samplerate,color=block))


ggplot(filter(hpp,!is.na(amp.bins)))+
  geom_boxplot(aes(block,abs(head.contribution),color=block))

# t.test(head.contribution~block,data=hpp)
```
#All trials
Next I just plot all of the trials that have a detectable gaze shift after the movement. As you can see, there are a lot of failed trials. More effort could be put into refining the algorithm to ignore gaze shifts that are too small or start too early or to reject trials with too much missing data.

```{r plotstuff, warning=FALSE}
for(i in 1:length(unique(hh$sacnum))){
  print(
    ggplot(filter(hh,sacnum==i))+
             geom_line(aes(counter,H),color='blue')+
             # geom_line(aes(counter,Ef),color='red')+
             geom_line(aes(counter,G),color='darkgreen')+
             geom_line(aes(counter,T),size=2,alpha=0.5)+
             geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
             # geom_line(aes(counter,EV/10),color='red')+
             geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
             # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
             geom_point(aes(counter,sign(gazeshifts)*50))+
             geom_point(aes(counter,sign(headmovement)*25),color='blue')
  )
}
```


```{r plotgod, warning=FALSE,include=FALSE}

  print(
    ggplot(filter(hh,sacnum==i))+
             geom_line(aes(counter,H),color='blue')+
             # geom_line(aes(counter,Ef),color='red')+
             geom_line(aes(counter,G),color='darkgreen')+
             geom_line(aes(counter,T),size=2,alpha=0.5)+
             geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
             # geom_line(aes(counter,EV/10),color='red')+
             geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
             # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
             # geom_text(x=0,y=60,aes(label=firstshift[1]))+
             geom_point(aes(counter,sign(gazeshifts)*50))+
             geom_point(aes(counter,sign(headmovement)*25),color='blue')
  )

hh2<-filter(hh,block=='A-01')
hh2<- filter(htest,block=='A-02')
manipulate(ggplot(filter(hh,sacnum==chosensac))+
              geom_line(aes(counter,H),color='blue')+
             # geom_line(aes(counter,Ef),color='red')+
             geom_line(aes(counter,G),color='darkgreen')+
             geom_line(aes(counter,T),size=2,alpha=0.5)+
             geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
             # geom_line(aes(counter,EV/10),color='red')+
             geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
             # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
             # geom_text(x=0,y=60,aes(label=firstshift[1]))+
             geom_line(aes(counter,sign(gazeshifts)*Gv/10),size=2,color='darkgreen')+
             geom_line(aes(counter,sign(headmovement)*Hv/10),color='blue',size=2)
           ,
           chosensac=slider(1,length(unique(hh$sacnum))))

#goodsacs only
manipulate(ggplot(filter(hh,sacnum==goodsacs[chosensac]))+
              geom_line(aes(counter,H),color='blue')+
             # geom_line(aes(counter,Ef),color='red')+
             geom_line(aes(counter,G),color='darkgreen')+
             geom_line(aes(counter,T),size=2,alpha=0.5)+
             geom_line(aes(counter,G-H),color='orange')+
             geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
             # geom_line(aes(counter,EV/10),color='red')+
             geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
             # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
             # geom_text(x=0,y=60,aes(label=firstshift[1]))+
             geom_line(aes(counter,sign(gazeshifts)*Gv/10),size=2,color='darkgreen')+
             geom_line(aes(counter,sign(headmovement)*Hv/10),color='blue',size=2)
           ,
           chosensac=slider(1,length(goodsacs)))

}
```


