---
title: "Gaze Shift Analysis"
author: "Adam Pallus"
output: 
  html_document: 
    keep_md: yes
  pdf_document: 
    highlight: espresso
---
#Introduction
I wrote up a quick analysis in R that should demonstrate the possibilities of automating this process. I've included the source code in this document, but we could do the same kind of analysis in Matlab. I'm just currently using R more for this kind of stuff and I think it will take a few more lines of code to work with Matlab. 

##Process:

* load text file
* take gaze, head and target position columns
* calculate velocity by convolving with a parabola (smoothing)
* identify when the target changes position 
* break file into "trials" consisting of 200ms before target movement and 600ms after
* mark gaze shifts using a two-threshold algorithm 
* mark head movements using same algorithm with lower thresholds
* Identify the "first" gaze shift that happens after target movement
* measure onsets/offsets/durations etc
* make plots

```{r setup, include=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(knitr)
library(tidyr)
# library(broom)
# library(grid)
# library(relaimpo)
# library(leaps)
#library(data.table)
# library(stringr)
library(dplyr)
library(cladoRcpp)
select<-dplyr::select
# source('joinsaccadesuniform.R')
source('Adamhelperfunctions.R')
source('markSaccadesDouble2.R')
markTagetMovements<-function(t,buffer=200,threshold=1000,saccade.length=1000){
  
  findSaccades<-function(ev,threshold=40){
    mindur<- 1
    i<-which(abs(ev)>threshold) #find all the times when speed > threshold
    sacoff<-which(diff(i)>mindur) #minimum duration of an accepted saccade
    sacon<-c(1,sacoff+1) #first saccade
    sacoff<-c(sacoff,length(i)) #end of last saccade
    saccade.onset<-i[sacon] #get actual times
    saccade.offset<-i[sacoff] 
    
    return(data.frame(saccade.onset,saccade.offset))
  }
  
  jsac<- function(stimes){
    summary(stimes)
    #input should be an array of length 2: c(onsettime,offsettime, saccade.number,saccade.dur)
    df<- data.frame(time=stimes[[1]]:stimes[[2]])
    df$sacnum<- stimes[[4]]
    df$saccade.dur<- stimes[[3]]
    return(df)
    # return(stimes[[1]]:stimes[[2]])
  }
  
  stimes<-findSaccades(t$target.velocity,threshold)
  stimes %>%
    mutate(dur=saccade.offset-saccade.onset,
           s=row_number(),
           saccade.onset=saccade.onset-buffer,
           ###########HERE IS WHERE i MAKE SACCADES UNIFORM #######
           saccade.offset=saccade.onset+saccade.length+2*buffer)->
    stimes
  
  x<- as.data.frame(rbindlist(apply(stimes,1,jsac)))
  x %>%
    group_by(sacnum) %>%
    mutate(counter=time-first(time)) ->
    x
  left_join(t,x,by='time')
}

```

```{r load}
samplerate<- 304.7508/1000
h<- read.csv('HEADFREE.txt',sep="\t",header=FALSE)
h<- select(h,-V9)
names(h)<- c('G','GV','H','HV','E','EV','time','T')



h %>% 
  select(G,H,T) %>% #these are the only data we need 
  mutate(G=replace(G,G==0,NA), #mark missing data as NA rather than 0
         #G=na.approx(G,na.rm=FALSE),
         Gv=parabolicdiff(G,7)*samplerate,
         Hv=parabolicdiff(H,7)*samplerate,
         target.velocity=parabolicdiff(T,7)*samplerate,
         time=row_number(),
         # gazeshifts=markSaccades(Gv,buffer=5,threshold=30),
         gazeshifts=markSaccadesDouble(Gv,threshold1=100,threshold2=10),
         headmovement=markSaccadesDouble(Hv,threshold1=10,threshold2=4),
         headmovement=replace(headmovement,headmovement<0,0),
         gazeshifts=replace(gazeshifts,gazeshifts<0,0)) %>%
  markTagetMovements(buffer=200,threshold=200,saccade.length=500) ->
  htest

htest%>%
  group_by(sacnum) %>%
  mutate(firstshift=min(gazeshifts[counter>220&gazeshifts>0],na.rm=T),
         gazeshifts=replace(gazeshifts,
                            gazeshifts!=firstshift|is.na(firstshift),
                            0),
         gazeshifts=replace(gazeshifts,gazeshifts==0,NA),
         headmovement=replace(headmovement,headmovement==0,NA),
         counter=counter-200)->
  hh
```

```{r measure}

hh %>% 
  group_by(sacnum) %>%
  mutate(gvsd=round(sd(Gv[1:300])))->
  hh

hh %>% 
  # filter(sacnum==10)%>%
  group_by(sacnum) %>%
  mutate(gaze.dur=length(counter[!is.na(gazeshifts)])) %>%
  ungroup() %>%
  filter(gaze.dur>1) ->
  hint

hint%>%
  group_by(sacnum)%>%
  summarize(gaze.onset=counter[!is.na(gazeshifts)][1],
         gaze.offset=max(counter[!is.na(gazeshifts)]),
         gaze.dur=gaze.offset-gaze.onset,
         gaze.dur.ms=gaze.dur/samplerate,
         gaze.amp=G[counter==gaze.offset]-G[counter==gaze.onset],
         IHP=H[counter==gaze.onset],
         IGP=G[counter==gaze.onset],
         IEP=IGP-IHP,
         IEPs=IEP*sign(gaze.amp), #positive number indicates eyes deviated in direction of saccade
         peak.gaze.velocity=maxabs(Gv[!is.na(gazeshifts)]),
         peak.head.velocity=maxabs(Hv[100:n()]),
         target.amp=T[200]-T[1],
         head.contribution=H[counter==gaze.offset]-IHP,
         eye.contribution=gaze.amp-head.contribution
         ) %>%
  filter(gaze.onset>0,gaze.onset<200)->
  hp

goodsacs=unique(hp$sacnum)
goodsacs=unique(filter(hp,gaze.dur.ms>250)$sacnum)
goodsacs=unique(filter(hp,gaze.dur.ms<200,IEPs>4))$sacnum
```

##Example plot
Here is an example of a trial with the first gaze shift and head movement marked.
Velocity is shown on the same plot as position scaled down by a factor of 10.

```{r demoplot,echo=FALSE,warning=FALSE}
ggplot(filter(hh,sacnum==31))+
  geom_line(aes(counter,H),color='blue')+
  # geom_line(aes(counter,Ef),color='red')+
  geom_line(aes(counter,G),color='darkgreen')+
  geom_line(aes(counter,T),size=2,alpha=0.5)+
  geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
  # geom_line(aes(counter,EV/10),color='red')+
  geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
  # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
  geom_point(aes(counter,sign(gazeshifts)*50))+
  geom_point(aes(counter,sign(headmovement)*25),color='blue')+
  annotate('text',x=-100,y=50,label='Target Position')+
  annotate('text',x=500,y=20,label='Head Position')+
  annotate('text',x=320,y=5,label='Head Velocity')+
  annotate('text',x=270,y=40,label='Gaze Velocity')+
  annotate('text',x=250,y=70,label='Gaze Position')+
  annotate('text',x=125,y=55,label='First Gaze Shift')+
  annotate('text',x=300,y=28,label='Head Movement')+
  geom_line(aes(counter,sign(gazeshifts)*Gv/10),size=2,color='darkgreen',alpha=0.5)+
  geom_line(aes(counter,sign(headmovement)*Hv/10),color='blue',size=2,alpha=0.5)
  

```

#Summary Figures
Some simple summary figures

```{r SummaryFigures,warning=FALSE}

hpp<- filter(hp,gaze.dur/samplerate<200)

qplot(gaze.onset/samplerate,bins=30,data=hpp)+xlab('Gaze Shift Latency (ms)')
qplot(IEP,peak.head.velocity,data=hpp)
qplot(IEP,peak.gaze.velocity,data=hpp)

ggplot(aes(gaze.dur/samplerate,abs(peak.gaze.velocity)),
       data=hpp)+
  geom_point()+
  stat_smooth(method='lm',se=FALSE)+
  xlab('Gaze Shift duration (ms)')+
  ylab('Peak Gaze Velocity (deg/s)')

ggplot(aes(gaze.amp,peak.gaze.velocity),data=hpp)+
  geom_point()+
  # stat_smooth(method='lm',se=FALSE)+
  # ggtitle('Main Sequence')+
  xlab('Gaze Shift Amplitude (deg)')+
  ylab('Peak Gaze Velocity (deg/s)')

ggplot(aes(abs(gaze.amp),abs(peak.gaze.velocity)),data=hpp)+
  geom_point()+
  stat_smooth(method='lm',se=FALSE)+
  stat_smooth(color='red',se=FALSE)+
  ggtitle('Main Sequence')+
  xlab('Gaze Shift Amplitude (deg)')+
  ylab('Peak Gaze Speed (deg/s)')
    
ggplot(aes(abs(gaze.amp),head.contribution/gaze.amp),data=hpp)+
  geom_point()

ggplot(aes(IEPs,head.contribution),data=hpp)+
  geom_point()

qplot(abs(gaze.amp),abs(gaze.amp)-abs(head.contribution),color=IEP,data=hpp)+
  geom_abline()

```

#All trials
Next I just plot all of the trials that have a detectable gaze shift after the movement. As you can see, there are a lot of failed trials. More effort could be put into refining the algorithm to ignore gaze shifts that are too small or start too early or to reject trials with too much missing data.

```{r plotstuff, warning=FALSE}
for(i in 1:length(unique(hh$sacnum))){
  print(
    ggplot(filter(hh,sacnum==i))+
             geom_line(aes(counter,H),color='blue')+
             # geom_line(aes(counter,Ef),color='red')+
             geom_line(aes(counter,G),color='darkgreen')+
             geom_line(aes(counter,T),size=2,alpha=0.5)+
             geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
             # geom_line(aes(counter,EV/10),color='red')+
             geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
             # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
             geom_point(aes(counter,sign(gazeshifts)*50))+
             geom_point(aes(counter,sign(headmovement)*25),color='blue')
  )
}
```


```{r plotgod, warning=FALSE,include=FALSE}

  print(
    ggplot(filter(hh,sacnum==i))+
             geom_line(aes(counter,H),color='blue')+
             # geom_line(aes(counter,Ef),color='red')+
             geom_line(aes(counter,G),color='darkgreen')+
             geom_line(aes(counter,T),size=2,alpha=0.5)+
             geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
             # geom_line(aes(counter,EV/10),color='red')+
             geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
             # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
             # geom_text(x=0,y=60,aes(label=firstshift[1]))+
             geom_point(aes(counter,sign(gazeshifts)*50))+
             geom_point(aes(counter,sign(headmovement)*25),color='blue')
  )

manipulate(ggplot(filter(hh,sacnum==chosensac))+
              geom_line(aes(counter,H),color='blue')+
             # geom_line(aes(counter,Ef),color='red')+
             geom_line(aes(counter,G),color='darkgreen')+
             geom_line(aes(counter,T),size=2,alpha=0.5)+
             geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
             # geom_line(aes(counter,EV/10),color='red')+
             geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
             # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
             # geom_text(x=0,y=60,aes(label=firstshift[1]))+
             geom_line(aes(counter,sign(gazeshifts)*Gv/10),size=2,color='darkgreen')+
             geom_line(aes(counter,sign(headmovement)*Hv/10),color='blue',size=2)
           ,
           chosensac=slider(1,length(unique(hh$sacnum))))

#goodsacs only
manipulate(ggplot(filter(hh,sacnum==goodsacs[chosensac]))+
              geom_line(aes(counter,H),color='blue')+
             # geom_line(aes(counter,Ef),color='red')+
             geom_line(aes(counter,G),color='darkgreen')+
             geom_line(aes(counter,T),size=2,alpha=0.5)+
             geom_line(aes(counter,G-H),color='orange')+
             geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
             # geom_line(aes(counter,EV/10),color='red')+
             geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
             # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
             # geom_text(x=0,y=60,aes(label=firstshift[1]))+
             geom_line(aes(counter,sign(gazeshifts)*Gv/10),size=2,color='darkgreen')+
             geom_line(aes(counter,sign(headmovement)*Hv/10),color='blue',size=2)
           ,
           chosensac=slider(1,length(goodsacs)))

}
```


