---
title: "Gaze Shifts"
author: "Adam"
date: "September 1, 2017"
output: 
html_document: 
self_contained: no
runtime: shiny
---

* Counter is in sample time. Multiply by samplerate/1000 to convert to ms. 
* Thick gray line is target position.
* Green line is gaze position.
* Blue line is head position.
* Dashed green line is gaze velocity (plotted 1/10th scale)
* Dashed blue line is head velocity (plotted 1/10th scale)  
     + The highlighted segments of the gaze and head velocity traces are the identified movements.
     + Only the first gaze shift that occurs after the target moves is marked.


```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE)
```

```{r,message=FALSE}

library(ggplot2)
library(dplyr)
#library(knitr)
#library(tidyr)
#library(broom)
#library(grid)
# library(relaimpo)
# library(leaps)
#library(data.table)

```


```{R SHINYTRY, warning=FALSE}
#In order to make the shiny app load fast, I'm just saving the output. See BoostrapSaccades.Rmd for the actual analysis.
# z<-readRDS(file="Bee13forshiny.RDS")
hh<- readRDS('knightdemo.RDS')

inputPanel(
  
  sliderInput("TrialChoice", label = "Select a movement:",
              min=1,
              max=length(unique(hh$sacnum)),
              value=1,
              step=1)
  

)

renderPlot({
  
    chosentrial<-input$TrialChoice
    ggplot(filter(hh,sacnum==chosentrial))+
              geom_line(aes(counter,H),color='blue')+
             # geom_line(aes(counter,Ef),color='red')+
             geom_line(aes(counter,G),color='darkgreen')+
             geom_line(aes(counter,T),size=2,alpha=0.5)+
             geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
             # geom_line(aes(counter,EV/10),color='red')+
             geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
             # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
             # geom_text(x=0,y=60,aes(label=firstshift[1]))+
             geom_line(aes(counter,sign(gazeshifts)*Gv/10),size=2,color='darkgreen',alpha=0.5)+
             geom_line(aes(counter,sign(headmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
      theme_minimal()

})

```



