---
title: "Gaze Shifts"
author: "Adam"
date: "January 26, 2018"
output: 
html_document: 
self_contained: no
runtime: shiny
---

* Thick gray line is target position.
* Green line is gaze position.
* Blue line is head position.
* Dashed green line is gaze velocity (plotted 1/10th scale)
* Dashed blue line is head velocity (plotted 1/10th scale)  
     + The highlighted segments of the gaze and head velocity traces are the identified movements.
     + The first eye-saccade and head movement that occur after the target moves is marked on the velocity trace.
     + Additional saccades and head movements are marked with horizontal lines
     + Trials where there is missing data within the first 1000 ms of the target's movement are labeled


```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE)
```

```{r,message=FALSE}

```{r setup, include=FALSE,message=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(knitr)
library(tidyr)
library(manipulate)
# library(broom)
# library(grid)
# library(relaimpo)
# library(leaps)
#library(data.table)
# library(stringr)
library(dplyr)
library(cladoRcpp)
select<-dplyr::select
# source('joinsaccadesuniform.R')
source('Adamhelperfunctions.R')
source('markSaccadesDouble2.R')
markTagetMovements<-function(t,buffer=200,threshold=1000,saccade.length=1000){
  
  findSaccades<-function(ev,threshold=40){
    mindur<- 1
    i<-which(abs(ev)>threshold) #find all the times when speed > threshold
    sacoff<-which(diff(i)>mindur) #minimum duration of an accepted saccade
    sacon<-c(1,sacoff+1) #first saccade
    sacoff<-c(sacoff,length(i)) #end of last saccade
    saccade.onset<-i[sacon] #get actual times
    saccade.offset<-i[sacoff] 
    
    return(data.frame(saccade.onset,saccade.offset))
  }
  
  jsac<- function(stimes){
    summary(stimes)
    #input should be an array of length 2: c(onsettime,offsettime, saccade.number,saccade.dur)
    df<- data.frame(time=stimes[[1]]:stimes[[2]])
    df$sacnum<- stimes[[4]]
    df$saccade.dur<- stimes[[3]]
    return(df)
    # return(stimes[[1]]:stimes[[2]])
  }
  
  stimes<-findSaccades(t$target.velocity,threshold)
  stimes %>%
    mutate(dur=saccade.offset-saccade.onset,
           s=row_number(),
           saccade.onset=saccade.onset-buffer,
           ###########HERE IS WHERE i MAKE SACCADES UNIFORM #######
           saccade.offset=saccade.onset+saccade.length+2*buffer)->
    stimes
  
  x<- as.data.frame(rbindlist(apply(stimes,1,jsac)))
  x %>%
    group_by(sacnum) %>%
    mutate(counter=time-first(time)) ->
    x
  left_join(t,x,by='time')
}

loadnewheadfree<- function(filename){
  h<- read.csv(filename,sep='\t',header=FALSE)
  h<- select(h,-V9)
  
  names(h)<- c('G','GV','H','HV','E','EV','time','T','block','subject','blocknum')
  
  h %>% 
    # filter(block=='A-02')%>%
    select(G,H,T,block) %>% #these are the only data we need 
    group_by(block) %>%
    mutate(G=replace(G,G==0,NA), #mark missing data as NA rather than 0
           #G=na.approx(G,na.rm=FALSE),
           time=row_number(),
           Gv=parabolicdiff(G,7)*samplerate, #calculate velocity
           Hv=parabolicdiff(H,7)*samplerate,
           target.velocity=parabolicdiff(T,7)*samplerate,
           # gazeshifts=markSaccades(Gv,buffer=5,threshold=30),
           gazeshifts=markSaccadesDouble(Gv,threshold1=100,threshold2=10),
           headmovement=markSaccadesDouble(Hv,threshold1=10,threshold2=4),
           #algorithm marks non-movements (fixations) as negative so remove them
           headmovement=replace(headmovement,headmovement<0,0), 
           gazeshifts=replace(gazeshifts,gazeshifts<0,0)) ->
    htesta
  
  htesta%>%
    # filter(block=='A-02')%>%
    group_by(block) %>%
    #identify movements and mark 200ms before and 500ms after each movement as "sacnum"
    do(markTagetMovements(t=.,buffer=200,threshold=200,saccade.length=500)) ->
    htest
  
  htest%>%
    filter(!is.na(sacnum))%>% #get rid of all data that isn't part of the marked target movement periods
    group_by(block,sacnum) %>% #look at each target movement individually
    #time of first gaze shift - we want to ignore gaze shifts that start before the target actually moved
    mutate(firstshift=min(gazeshifts[counter>220&gazeshifts>0],na.rm=T), 
           firsthead=min(headmovement[counter>220&headmovement>0],na.rm=T),
           primarygazeshifts=replace(gazeshifts,
                                     gazeshifts!=firstshift|is.na(firstshift),
                                     0), #the first "eye saccade" we're calling the primary gaze shift
           primaryheadmovement=replace(headmovement,
                                       headmovement!=firsthead|is.na(firsthead),
                                       0),
           #for easier analysis/plotting, use NA rather than 0 for non-movements 
           gazeshifts=replace(gazeshifts,gazeshifts==0,NA),
           primarygazeshifts=replace(primarygazeshifts,primarygazeshifts==0,NA),
           headmovement=replace(headmovement,headmovement==0,NA),
           primaryheadmovement=replace(primaryheadmovement,primaryheadmovement==0,NA),
           counter=counter-200,
           tcounter=round(counter/samplerate))->
    hh
}
```




```{R SHINYTRY, warning=FALSE}
#In order to make the shiny app load fast, I'm just saving the output. See BoostrapSaccades.Rmd for the actual analysis.
# z<-readRDS(file="Bee13forshiny.RDS")
# hh<- readRDS('knightdemo.RDS')
hh<- readRDS('knightdemo2.RDS')

plotTrial<- function(hh){
  # cat(hh$blinktrial[1])
  gp<- ggplot(hh)+
    geom_line(aes(tcounter,H),color='blue')+
    # geom_line(aes(tcounter,Ef),color='red')+
    geom_line(aes(tcounter,G),color='darkgreen')+
    geom_line(aes(tcounter,T),size=2,alpha=0.5)+
    geom_line(aes(tcounter,Hv/10),color='blue',linetype=2)+
    # geom_line(aes(tcounter,EV/10),color='red')+
    geom_line(aes(tcounter,Gv/10),color='darkgreen',linetype=2)+
    # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
    geom_point(aes(tcounter,sign(gazeshifts)*50),color='darkgreen')+
    geom_point(aes(tcounter,sign(headmovement)*25),color='blue')+
    geom_line(aes(tcounter,sign(primarygazeshifts)*Gv/10),size=2,color='darkgreen',alpha=0.5)+
    # geom_line(aes(tcounter,sign(gazeshifts)*Gv/10),size=2,color='yellow',alpha=0.5)+
    geom_line(aes(tcounter,sign(primaryheadmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
    xlab('Time (ms)')
    
    # geom_line(aes(tcounter,sign(headmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
    blink<- hh$blinktrial[1]
    if(blink | is.na(blink)){
      gp<-gp+geom_label(x=0,y=0,label='BLINK INTERRUPTED')
    }
    gp
    
}


inputPanel(
  
  selectInput(inputId= 'blockChoice',
              label='Choose block:',
              choices=list('A-01','A-02')),
  
  sliderInput("TrialChoice", label = "Select a movement:",
              min=1,
              max=length(unique(hh$sacnum)),
              value=1,
              step=1)
  

)

renderPlot({
  
    chosentrial<-input$TrialChoice
    blockchoice<- input$blockChoice
    
    plotTrial(filter(hh,sacnum==chosentrial,block==blockchoice))
    # 
    # ggplot(filter(hh,sacnum==chosentrial))+
    #           geom_line(aes(counter,H),color='blue')+
    #          # geom_line(aes(counter,Ef),color='red')+
    #          geom_line(aes(counter,G),color='darkgreen')+
    #          geom_line(aes(counter,T),size=2,alpha=0.5)+
    #          geom_line(aes(counter,Hv/10),color='blue',linetype=2)+
    #          # geom_line(aes(counter,EV/10),color='red')+
    #          geom_line(aes(counter,Gv/10),color='darkgreen',linetype=2)+
    #          # geom_text(x=0,y=50,aes(label=round(sd(Gv),2)))+
    #          # geom_text(x=0,y=60,aes(label=firstshift[1]))+
    #          geom_line(aes(counter,sign(gazeshifts)*Gv/10),size=2,color='darkgreen',alpha=0.5)+
    #          geom_line(aes(counter,sign(headmovement)*Hv/10),color='blue',size=2,alpha=0.5)+
    #   theme_minimal()

})

```



