---
title: "Analysis of INC in strabismus"
author: "Adam Pallus"
output:
  pdf_document: default
  html_document: default
---
#Introduction
We recorded neurons in the INC of a monkeys with esotropia and pattern strabismus. In this document, we analyze the position and velocity sensitivity of these cells. 


```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE,cache=FALSE)
```

```{r,message=FALSE,echo=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
library(broom)
# library(grid)
library(relaimpo)
library(leaps)
library(stringr)
library(cladoRcpp)
library(boot)
source('Adamhelperfunctions.R')
select<- dplyr::select
```

```{r quickload,echo=FALSE}
# o<-readRDS('KopachuckINC.RDS')
# o<-readRDS('KopaBeeINC.RDS')
o<- NULL
t<- loadnewcsv2(path="C:/Users/setup/Documents/GitHub/NPH-Analysis/data/",referencefile=o)

if (!is.null(t)){
  t<- rbind(o,t)
  saveRDS(t,paste('NPHdata',substr(date(),1,10),'.RDS'))
}else{
  t<-o
}

# t<- rbind(o,t)

t %>% group_by(neuron) %>%
  mutate(time=row_number()) ->
  t

o<-NULL

#Calculate ISI
# t %>%
#   group_by(neuron) %>%
#   dplyr::select(neuron, rasters,time) %>%
#   # mutate(time=row_number()) %>%
#   filter(rasters==1) %>%
#   mutate(isi=time-lag(time,1)) %>%
#   left_join(t,.,by=c('neuron','time','rasters')) ->
#   t

```
#Results
```{r simple model INC}

t%>%
  group_by(neuron) %>%
  mutate(sdf10=lag(sdf,10))->
  t

r<- makeRelImp(t,formula='sdf10~repV+revV',norm=FALSE)


t %>% group_by(neuron) %>%
  do(tidy(lm('sdf10~repV+revV',data=.)))->
  ttest

ttest %>%
  dplyr::select(neuron,term,estimate) %>%
  spread(term,estimate) ->
  tp
         
tp$b<-tp$'(Intercept)'
tp$'(Intercept)'=NULL



tp %>%
  ungroup() %>%
  mutate(absb=abs(b),
         absrepV=abs(repV),
         absrevV=abs(revV)) %>%
  dplyr::select(neuron,absb,absrepV,absrevV)->
  tpa
names(tp)<- c('neuron','V_Posion','V_Velocity','b')

tp<- left_join(tp,dplyr::select(r,neuron,R2),by='neuron')

kable(tp,digits=c(0,2,2,2,2))

tpa<- separate(tpa,neuron,c('monkey','cellnum'),remove=FALSE)

#add R^2 since tidy doesn't automatically grab that
tpa<- left_join(tpa,dplyr::select(r,neuron,R2),by='neuron')


tpa %>%
  filter(monkey=='Kopachuck') %>%
  dplyr::select(-neuron,-monkey,-cellnum)->
  xx

kable(summary(xx))

tpa %>%
  filter(monkey=='Bee') %>%
  dplyr::select(-neuron,-monkey,-cellnum)->
  xx

kable(summary(xx))



ggplot(r)+geom_histogram(aes(R2))+
  ggtitle('Goodness of Fit')+
  facet_wrap(~monkey)+
  geom_vline(xintercept = 0.1)+
  annotate("text", x=0.25,y=6,label= "R^2 == 0.1",parse=TRUE)



removeIrregular=TRUE

if (removeIrregular){
  tpa<- filter(tpa,R2>0.1)
}

tpa %>%
  group_by(monkey) %>%
  dplyr::select(-neuron,-cellnum) %>%
  summarize_each(funs(mean))->
  vs

ggplot(tpa)+
  geom_histogram(aes(absb),bins=20)+
  xlab('Bias (absolute value)')+
  facet_wrap(~monkey)+
  geom_vline(aes(xintercept = absb),data=vs)+
  geom_label(aes(x=absb,y=3.5,label=round(absb,2)),data=vs)

ggplot(tpa)+
  geom_histogram(aes(absrepV),bins=20)+
  geom_vline(aes(xintercept = absrepV),data=vs)+
  xlab('Right Eye Vertical Position Sensitivity (absolute value)')+
  facet_wrap(~monkey)+
    geom_label(aes(x=absrepV,y=3.5,label=round(absrepV,2)),data=vs)

ggplot(tpa)+
  geom_histogram(aes(absrevV),bins=20)+
  geom_vline(aes(xintercept = absrevV),data=vs)+
  xlab('Right Eye Vertical Velocity Sensitivity (absolute value)')+
  facet_wrap(~monkey)+
    geom_label(aes(x=absrevV,y=3.5,label=round(absrevV,2)),data=vs)

ggplot(tpa)+
  geom_boxplot(aes(monkey,absb))+
  ylab("Intercept")

ggplot(tpa)+
  geom_boxplot(aes(monkey,absrepV))+
  ylab("Sensitivity to Right Eye Position")

ggplot(tpa)+
  geom_boxplot(aes(monkey,absrevV))+
  ylab("Sensitivity to Right Eye Velocity")

```
Sensitivity to vertical right eye position is reduced in the strabismic animal. Sensitivity to vertical velocity is not statistically significantly different. Many more cells with poor *R^2*. 
```{r simpleH model INC}


r<- makeRelImp(t,formula='sdf10~rep+rev',norm=FALSE)


t %>% group_by(neuron) %>%
  do(tidy(lm('sdf10~rep+rev',data=.)))->
  ttest

ttest %>%
  dplyr::select(neuron,term,estimate) %>%
  spread(term,estimate) ->
  tp
         
tp$b<-tp$'(Intercept)'
tp$'(Intercept)'=NULL



tp %>%
  ungroup() %>%
  mutate(absb=abs(b),
         absrep=abs(rep),
         absrev=abs(rev)) %>%
  dplyr::select(neuron,absb,absrep,absrev)->
  tpa
names(tp)<- c('neuron','H_Posion','H_Velocity','b')

kable(tp,digits=c(0,2,2,2))

tpa<- separate(tpa,neuron,c('monkey','cellnum'),remove=FALSE)

#add R^2 since tidy doesn't automatically grab that
tpa<- left_join(tpa,dplyr::select(r,neuron,R2),by='neuron')


tpa %>%
  filter(monkey=='Kopachuck') %>%
  dplyr::select(-neuron,-monkey,-cellnum)->
  xx

kable(summary(xx))

tpa %>%
  filter(monkey=='Bee') %>%
  dplyr::select(-neuron,-monkey,-cellnum)->
  xx

kable(summary(xx))



ggplot(r)+geom_histogram(aes(R2))+
  ggtitle('Goodness of Fit')+
  facet_wrap(~monkey)+
  geom_vline(xintercept = 0.1)+
  annotate("text", x=0.25,y=6,label= "R^2 == 0.1",parse=TRUE)



removeIrregular=FALSE

if (removeIrregular){
  tpa<- filter(tpa,R2>0.1)
}

tpa %>%
  group_by(monkey) %>%
  dplyr::select(-neuron,-cellnum) %>%
  summarize_each(funs(mean))->
  vs

ggplot(tpa)+
  geom_histogram(aes(absb),bins=20)+
  xlab('Bias (absolute value)')+
  facet_wrap(~monkey)+
  geom_vline(aes(xintercept = absb),data=vs)+
  geom_label(aes(x=absb,y=3.5,label=round(absb,2)),data=vs)

ggplot(tpa)+
  geom_histogram(aes(absrep),bins=20)+
  geom_vline(aes(xintercept = absrep),data=vs)+
  xlab('Right Eye Horizontal Position Sensitivity (absolute value)')+
  facet_wrap(~monkey)+
    geom_label(aes(x=absrep,y=3.5,label=round(absrep,2)),data=vs)

ggplot(tpa)+
  geom_histogram(aes(absrev),bins=20)+
  geom_vline(aes(xintercept = absrev),data=vs)+
  xlab('Right Eye Horizontal Velocity Sensitivity (absolute value)')+
  facet_wrap(~monkey)+
    geom_label(aes(x=absrev,y=3.5,label=round(absrev,2)),data=vs)

ggplot(tpa)+
  geom_boxplot(aes(monkey,absb))+
  ylab("Intercept")

ggplot(tpa)+
  geom_boxplot(aes(monkey,absrep))+
  ylab("Sensitivity to Right Eye HORIZONTAL Position")

ggplot(tpa)+
  geom_boxplot(aes(monkey,absrev))+
  ylab("Sensitivity to Right Eye HORIZONTAL Velocity")

```
Sensitivity to horizontal velocity is significantly greater in the strabismic INC cells. No significant difference in horizontal position sensitivity. 
##Time Series Bootstrapping
The boot package for R provides a function called tsboot. This function deals with the problem of time series data continaing autocorrelated data. Instead of treating each point individually for bootstrapping, it chooses chunks of the data set. We can set how large each chunk is. Let's try 1000ms per chunk.
```{r timeseriesbootstrapping}

#------TSBOOT
inc.fun <- function(tsb) {
       fit <- lm(data=tsb,formula='sdf10~repV+revV')
       return(coef(fit)) }

# tb<-tsboot(t, inc.fun, R=999,sim="geom", l=1000)
# plot(tb)
# tbs<-tidy(tb)
# tbs<-mutate(tbs,low95=statistic-2*std.error,high95=statistic+2*std.error)

#---- 
t %>%
  group_by(neuron) %>%
  do(tidy(tsboot(.,inc.fun,R=1999,sim="geom",l=1000))) %>%
  mutate(low95=statistic-2*std.error,high95=statistic+2*std.error)->
  tsba

tsba %>%
  mutate(zerocross=low95*high95<0)->
  tsba

tsba %>%
  dplyr::select(neuron,term,statistic) %>%
  spread(term,statistic)->
  tplot


tsba %>%
  dplyr::select(neuron,term,low95) %>%
  spread(term,low95) %>%
  rename(repV.low=repV,revV.low=revV)->
  tlow



tsba %>%
  dplyr::select(neuron,term,high95) %>%
  spread(term,high95) %>%
  rename(repV.high=repV,revV.high=revV)->
  thigh

tplot<- left_join(tplot,tlow,by='neuron')
tplot<- left_join(tplot,thigh,by='neuron')

ggplot(tplot,aes(repV,revV))+
  geom_point()+
  geom_errorbar(aes(ymin=revV.low,ymax=revV.high))+
  geom_errorbarh(aes(xmin=repV.low,xmax=repV.high))+
  geom_hline(yintercept = 0,color='pink')+
  geom_vline(xintercept = 0,color='pink')

saveRDS(tplot, 'tsbootstrapresults1999.RDS')


```
##Dynamic Modeling
We fit the entire data set with a linear model considering conjugate horizontal and vertical position and velocity:

```{r model INC}
t%>%
  group_by(neuron) %>%
  mutate(sdf10=lag(sdf,20),
         conj.VP=(lepV+repV)/2,
         conj.HP=(lep+rep)/2,
         conj.VV=(levV+revV)/2,
         conj.HV=(lev+rev)/2)->
  t

t %>% group_by(neuron) %>%
  do(tidy(lm('sdf10~conj.VP+conj.HP+conj.VV+conj.HV',data=.)))->
  ttest


ttest %>%
  dplyr::select(neuron,term,estimate) %>%
  spread(term,estimate) ->
  tp

r<- makeRelImp(t,formula='sdf10~conj.VP+conj.HP+conj.VV+conj.HV',norm=FALSE)

tp<- left_join(tp,dplyr::select(r,neuron,R2),by='neuron')

kable(tp,digits=c(0,2,2,2,2,2,2))


#direction preference:
# tp %>%
#   summarize(dir.pref=atan2(conj.VP+conj.VV,conj.HP+conj.HV)*180/pi) %>%
#   left_join(r,.,by='neuron')->
#   r
tp %>%
  summarize(dir.pref=atan2(conj.VP,conj.HP)*180/pi) %>%
  left_join(r,.,by='neuron')->
  r
  
```

We plot the *R^2* for each neuron then calculate relative importance of the 4 parameters and plot those comparisons:

```{r makeplots,fig.height=5,fig.width=5}

ggplot(r)+geom_bar(aes(as.numeric(cellnum) %% 100,R2),stat='identity')+
  ggtitle('Goodness of Fit')+
  facet_wrap(~monkey,scales='free_x')

ggplot(r)+geom_histogram(aes(R2))+
  ggtitle('Goodness of Fit')

ggplot(r,aes(conj.HP,conj.VP,label=cellnum,color=monkey))+
  geom_point(size=3,alpha=1/2)+
  geom_text(alpha=1/2,color='black',data=filter(r,R2>0.1))+
  geom_abline(slope=1)+
  ggtitle('Comparing Importantance of \nHorizontal and Vertical Position')+
  xlab('Horizontal Position')+
  ylab('Vertical Position')+
  coord_fixed()+
  expand_limits(x=-0.1,y=-0.1)+
  theme(legend.position = 'bottom')

ggplot(r,aes(conj.HV,conj.VV,label=cellnum))+
  geom_point(size=3)+
  geom_label()+
  geom_abline(slope=1)+
  ggtitle('Comparing Importantance of Horizontal and Vertical Velocity')+
  xlab('Horizontal Velocity')+
  ylab('Vertical Velocity')+
  facet_wrap(~monkey)

ggplot(r,aes(conj.VP,conj.VV,label=cellnum))+
  geom_point(size=3)+
  geom_label()+
  geom_abline(slope=1)+
  ggtitle('Comparing Importance of Vertical Position and Velocity')+
  xlab('Vertical Position')+
  ylab('Vertical Velocity')+
  facet_wrap(~monkey)


ggplot(r,aes(conj.HP,conj.HV,label=cellnum))+
  geom_point(size=3)+
  geom_label()+
  geom_abline(slope=1)+
  ggtitle('Comparing Importance of Horizontal Position and Velocity')+
  xlab('Horizontal Position')+
  ylab('Horizontal Velocity')+
  facet_wrap(~monkey)

##Error Bars for parameter estimates
# ggplot(filter(ttest,term!='(Intercept)'))+
#   geom_point(aes(term,estimate))+
#   geom_errorbar(aes(x=term,ymin=estimate-2*std.error,
#                     ymax=estimate+2*std.error,color=neuron,width=0.25))
```

We calculate direction preference by the arctangent of the relative importance of the horizontal and conjugate position on firing rate. First, plotted with the radius of the arrow indicating the *R^2*, then just showing the direction: 

```{r Direction Preference}  
ggplot(r)+
    geom_segment(aes(yend=R2,xend=dir.pref,y=0,x=dir.pref,color=cellnum),
               alpha=0.5,arrow=arrow(type='closed',length =unit(0.1,"inches")))+
  # geom_text(aes(dir.pref,R2+0.05,label=cellnum),alpha=1)+
  coord_polar(direction=-1,start=pi/2)+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  theme_bw()+
  ggtitle('Direction preference and goodness of fit')+
  ylab('Goodness of Fit')+
  xlab('Preferred Direction')+
  facet_wrap(~monkey)

ggplot(r)+
    geom_segment(aes(yend=1,xend=dir.pref,y=0,x=dir.pref,color=cellnum),
               alpha=0.5,arrow=arrow(type='closed',length =unit(0.1,"inches")))+
  # geom_text(aes(dir.pref,R2+0.05,label=cellnum),alpha=1)+
  coord_polar(direction=-1,start=pi/2)+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  theme_bw()+
  ggtitle('Direction preference')+
  ylab('')+
  xlab('Preferred Direction')+
  facet_wrap(~monkey)

ggplot(filter(r,R2>0.1))+
    geom_segment(aes(yend=R2,xend=dir.pref,y=0,x=dir.pref,color=cellnum),
               alpha=0.5,arrow=arrow(type='closed',length =unit(0.1,"inches")))+
  # geom_text(aes(dir.pref,R2+0.05,label=cellnum),alpha=1)+
  coord_polar(direction=-1,start=pi/2)+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  theme_bw()+
  ggtitle('Direction preference and goodness of fit')+
  ylab('Goodness of Fit')+
  xlab('Preferred Direction')+
  facet_wrap(~monkey)+
  ggtitle("Irregular Cells Removed")

ggplot(filter(r,R2>0.1))+
    geom_segment(aes(yend=1,xend=dir.pref,y=0,x=dir.pref,color=cellnum),
               alpha=0.5,arrow=arrow(type='closed',length =unit(0.1,"inches")))+
  geom_text(aes(dir.pref,1,label=cellnum),alpha=1)+
  coord_polar(direction=-1,start=pi/2)+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  theme_bw()+
  ggtitle('Direction preference')+
  ylab('')+
  xlab('Preferred Direction')+
  facet_wrap(~monkey)+
  ggtitle('Irregular Cells Removed')

ggplot(filter(r,R2>0.1,monkey=='Patos'))+
    geom_segment(aes(yend=R2,xend=dir.pref,y=0,x=dir.pref),
               alpha=0.5,arrow=arrow(type='closed',length =unit(0.1,"inches")))+
  # geom_text(aes(dir.pref,R2+0.05,label=cellnum),alpha=1)+
  coord_polar(direction=-1,start=pi/2)+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  theme_bw()+
  ggtitle('Direction preference and goodness of fit')+
  ylab('Goodness of Fit')+
  xlab('Preferred Direction')+
  facet_wrap(~monkey)+
  ggtitle("Irregular Cells Removed")

ggplot(filter(r,R2>0.1,monkey=='Bee'))+
    geom_segment(aes(yend=R2,xend=dir.pref,y=0,x=dir.pref),
               alpha=0.5,arrow=arrow(type='closed',length =unit(0.1,"inches")))+
  # geom_text(aes(dir.pref,R2+0.05,label=cellnum),alpha=1)+
  coord_polar(direction=-1,start=pi/2)+
  scale_x_continuous(limits=c(-180,180),breaks=c(0,90,180,-90))+
  theme_bw()+
  ggtitle('Direction preference and goodness of fit')+
  ylab('Goodness of Fit')+
  xlab('Preferred Direction')+
  facet_wrap(~monkey)+
  ggtitle("Irregular Cells Removed")

```

\newpage
##Saccades
Next, we analyze the activity during saccades. We plot peak firing rate as a function of peak vertical and horizontal velocity: 

```{r saccadeburst,fig.height=9,fig.width=7}
t %>% group_by(neuron) %>%
  do(joinsaccadesuniform(.,buffer=50,threshold=30))->
  ts

ts %>%
  group_by(neuron) %>%
  # mutate(bin.velocity=cut(verg.velocity,c(seq(-200,200,by=20)))) %>%
  # filter(!is.na(sacnum)) %>%
  group_by(neuron, sacnum) %>%
  mutate(peak.H.vel=maxabs(lev+rev)/2,
         peak.V.vel=maxabs((levV+revV)/2),
         conj.h=(lep+rep)/2,
         conj.v=(lepV+repV)/2,
         conj.h.amp=last(conj.h)-first(conj.h),
         conj.v.amp=last(conj.v)-first(conj.v),
         conj.angle=atan2(conj.v,conj.h)*180/pi,
         peak.verg.velocity=maxabs(verg.velocity),
         r.amp=sqrt(conj.h.amp^2+conj.v.amp^2),
         peak.FR=max(sdf10)) ->
  ts

ts %>%
  group_by(neuron,sacnum) %>%
  summarize(saccade.amp=first(r.amp),
            peak.H.vel=first(peak.H.vel),
            peak.V.vel=first(peak.V.vel),
            peak.FR=first(peak.FR),
            conj.h.amp=first(conj.h.amp),
            conj.v.amp=first(conj.v.amp)) %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  sp
```

```{r bigplots, fig.height=8,fig.width=5}
# qplot(peak.V.vel,peak.FR,data=filter(sp,abs(peak.V.vel)>100))+
#   facet_wrap(~neuron,scales='free',ncol=3)+
#   stat_smooth(method='lm')

qplot(conj.h.amp,peak.FR,data=filter(sp,abs(conj.h.amp)>4))+
facet_wrap(~neuron,scales='free',ncol=3)+
stat_smooth(method='lm')+
  xlab('Horizontal Saccade Amplitude (deg)')+
  ylab('Peak firing rate (deg/s)')

```

\pagebreak

```{r plot2, fig.height=8,fig.width=5}
# qplot(peak.H.vel,peak.FR,data=filter(sp,abs(peak.H.vel)>100))+
#   facet_wrap(~neuron,scales='free',ncol=3)+
#   stat_smooth(method='lm')

qplot(conj.v.amp,peak.FR,data=filter(sp,abs(conj.v.amp)>4))+
facet_wrap(~neuron,scales='free',ncol=3)+
stat_smooth(method='lm')+
    xlab('Vertical Saccade Amplitude (deg)')+
  ylab('Peak firing rate (deg/s)')

# ggplot(filter(sp,abs(conj.v.amp)>5))+
#   geom_point(aes(peak.V.vel,peak.FR))+
#   facet_wrap(~neuron,scales='free')
# 
# ggplot(filter(sp,abs(conj.h.amp)>5))+
#   geom_point(aes(peak.H.vel,peak.FR))+
#   facet_wrap(~neuron,scales='free')

# ggplot(filter(ts,conj.v.amp>5))+
#   geom_line(aes(counter,sdf10,group=sacnum))+
#   facet_wrap(~neuron)+
#   coord_cartesian(xlim=c(0,500))


```

\newpage
##Monocularity
We assess the cells for monocular preference. 

```{r monoculartest}
r<- makeRelImp(t,formula='sdf10~rep+lep+rev+lev',norm=FALSE)

ggplot(r,aes(rep,lep,label=cellnum))+
  geom_point(size=3)+
  geom_label()+
  geom_abline(slope=1)+
  ggtitle('Comparing Importantance of Left and Right Eye Vertical Position')+
  xlab('Right Eye')+
  ylab('Left Eye')

t %>% group_by(neuron) %>%
  do(tidy(lm('sdf10~repV+lepV+revV+levV',data=.)))->
  ttest

# #Error Bars for parameter estimates
# ggplot(filter(ttest,term %in% c('repV','lepV')))+
#   geom_point(aes(term,estimate))+
#   geom_errorbar(aes(x=term,ymin=estimate-2*std.error,
#                     ymax=estimate+2*std.error,color=neuron,width=1))

ttest %>%
  dplyr::select(neuron,term,std.error) %>%
  spread(term,std.error) %>%
  dplyr::select(neuron,lepV,repV) %>%
  rename(lepV.e=lepV,repV.e=repV)->
  tp.e

ttest %>%
  dplyr::select(neuron,term,estimate) %>%
  spread(term,estimate) %>%
  left_join(.,tp.e,by='neuron') %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  tp

# ggplot(tp,aes(repV,lepV,label=cellnum))+
#   # geom_point(size=3)+
#   # geom_label()+
#   geom_abline(slope=-1)+
#   geom_errorbar(aes(ymin=lepV-2*lepV.e,ymax=lepV+2*lepV.e))+
#   geom_errorbarh(aes(xmin=repV-2*repV.e,xmax=repV+2*repV.e))
# 
#   ggtitle('Comparing Sensitivity Left and Right Eye to Vertical Position')+
#   xlab('Right Eye')+
#   ylab('Left Eye')

```

```{r monocularBOOT}

#------TSBOOT
inc.mono.fun <- function(tsb) {
       fit <- lm(data=tsb,formula='sdf10~repV+lepV')
       return(coef(fit)) }

# tb<-tsboot(t, inc.fun, R=999,sim="geom", l=1000)
# plot(tb)
# tbs<-tidy(tb)
# tbs<-mutate(tbs,low95=statistic-2*std.error,high95=statistic+2*std.error)

#---- 
t %>%
  group_by(neuron) %>%
  do(tidy(tsboot(.,inc.mono.fun,R=99,sim="geom",l=1000))) %>%
  mutate(low95=statistic-2*std.error,high95=statistic+2*std.error)%>%
  mutate(zerocross=low95*high95<0)->
  tsba

tsba %>%
  dplyr::select(neuron,term,statistic) %>%
  spread(term,statistic)->
  tplot


tsba %>%
  dplyr::select(neuron,term,low95) %>%
  spread(term,low95) %>%
  rename(repV.low=repV,lepV.low=lepV)->
  tlow



tsba %>%
  dplyr::select(neuron,term,high95) %>%
  spread(term,high95) %>%
  rename(repV.high=repV,lepV.high=lepV)->
  thigh

tplot<- left_join(tplot,tlow,by='neuron')
tplot<- left_join(tplot,thigh,by='neuron')

ggplot(tplot,aes(repV,lepV))+
  geom_point()+
  geom_errorbar(aes(ymin=lepV.low,ymax=lepV.high))+
  geom_errorbarh(aes(xmin=repV.low,xmax=repV.high))+
  geom_hline(yintercept = 0,color='pink')+
  geom_vline(xintercept = 0,color='pink')+
  geom_abline()+
  geom_abline(slope=-1)
```

```{R isi}
#Calculate ISI
# t %>%
#   group_by(neuron) %>%
#   dplyr::select(neuron, rasters,time) %>%
#   # mutate(time=row_number()) %>%
#   filter(rasters==1) %>%
#   mutate(isi=time-lag(time,1)) %>%
#   left_join(t,.,by=c('neuron','time','rasters')) ->
#   t

t %>%
  group_by(neuron) %>%
  mutate(s=markSaccades(conj.velocity,buffer=20,threshold=25),
    isfixation=s<0) %>%
  filter(isfixation) %>% #This removes all saccades from the dataframe
  group_by(neuron,s) %>%
  summarize(meanfr=mean(sdf),
         maxfr=max(sdf),
         R.Hor=mean(rep),
         R.Ver=mean(repV),
         L.Hor=mean(lep),
         L.Ver=mean(lepV),
         dur=n(),
         mean.Spikerate=sum(rasters)/dur*1000,
         mean.ISI=mean(isi,na.rm=T),
         var.ISI=var(isi,na.rm=T),
         R.H.Amp=rep[1]-rep[length(rep)],
         L.H.Amp=lep[1]-lep[length(lep)],
         R.V.Amp=repV[1]-repV[length(repV)],
         L.V.Amp=lepV[1]-lepV[length(lepV)],
         maxamp=max(abs(R.H.Amp),abs(R.V.Amp),abs(L.H.Amp),abs(L.V.Amp)))->
  m


qplot(mean.ISI,sqrt(var.ISI),data=m)+facet_wrap(~neuron,ncol=3,scales='free')

ggplot(m)
  geom_histogram(aes(dur))+
  facet_wrap(~neuron,ncol=3,scales='free')

ggplot(filter(m,dur>50,dur<500))+
  geom_point(aes(R.Ver,mean.Spikerate))+
  facet_wrap(~neuron,ncol=3,scales='free')


m %>%
  group_by(neuron,s) %>%
  summarize(CV=sqrt(var.ISI)/mean.ISI) %>%
  summarize(CV=mean(CV,na.rm=T)) %>%
  separate(neuron,c('monkey','cellnum'),remove=FALSE)->
  sm

```


```{r gaussianfit}
# First present the data in a data-frame
# tab <- data.frame(x=seq_along(r), r=r)
#Apply function nls
m %>% 
  filter(neuron=='Bee-102') %>%
  ungroup() %>%
  mutate(direc=atan2(R.V.Amp,R.H.Amp)*180/pi) %>%
  select(meanfr,direc) ->
  tab

res <- nls( meanfr ~ direc*exp(-1/2*(direc-mu)^2/sigma^2), start=c(mu=15,sigma=5,k=1) , data = tab)

And from the output, I was able to obtain the following fitted "Gaussian curve":

v <- summary(res)$parameters[,"Estimate"]
plot(r~x, data=tab)
plot(function(x) v[3]*exp(-1/2*(x-v[1])^2/v[2]^2),col=2,add=T,xlim=range(tab$x) )



x <- tab$direc  
r<- tab$meanfr

f <- function(par)
{
    m <- par[1]
    sd <- par[2]
    k <- par[3]
    rhat <- k * exp(-0.5 * ((x - m)/sd)^2)
    sum((r - rhat)^2)
}

zz<- optim(c(15, 2, 1), f, method="BFGS", control=list(reltol=1e-9))

```





