---
title: "Modeling NRTP 3"
author: "Adam"
date: "June 22, 2016"
output: 
  pdf_document: 
    fig_height: 7
    fig_width: 8
---

```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE,cache=FALSE)
```

```{r loaddata, message=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(xtable)
library(tidyr)
# library(broom)
# library(grid)
# library(relaimpo)
# library(leaps)
# library(data.table)
# library(stringr)
source('joinsaccadesuniform.R')
source('Adamhelperfunctions.R')
source('markEnhancement.R')
# z<-readRDS('SOA-NRTP.RDS')
# z<-readRDS('SOA-NRTP.RDS')
# z<- readRDS('NRTP-TransientsRemoved.RDS')
# z<- readRDS('SOA-TransientsRemoved.RDS')
z<- readRDS('SOA-Pausers-TransientsRemoved.RDS')

s<- readRDS('transientstemplate.RDS')


#####
cellchoice<- 'Bee-218'
######
z<- dplyr::filter(z,neuron==cellchoice)
# head(z)
qplot(counter2,mean.transient,data=s)+facet_wrap(~monkey)

```


```{r setupdata}

z$time=z$time-first(z$time)
z %>%
  group_by(time) %>%
  summarize_each(funs(first)) %>%
  ungroup() ->
  z

xx<- markEnhancement(z$real.verg.velocity)


xx %>%
  rename(real.enhancenum=enhancenum,
         real.verg.velocity=v) %>%
  select(-real.verg.velocity) ->
  xx

z<- left_join(z,xx,by='time')

z %>%
  mutate(real.verg.enhance=!is.na(real.enhancenum),
           real.transient.type='none',
           real.verg.direction=real.verg.velocity>0)->
  z

i<- z$real.verg.enhance & !z$real.verg.direction
z$real.transient.type[i]<- 'divergence'
i<- z$real.verg.enhance & z$real.verg.direction
z$real.transient.type[i]<- 'convergence'



xx<- markEnhancement(z$verg.velocity)


xx <- select(xx,-v)
  

z<- left_join(z,xx,by='time')

z %>%
  mutate(verg.enhance=!is.na(enhancenum),
           transient.type='none',
           verg.direction=verg.velocity>0)->
  z

i<- z$verg.enhance & !z$verg.direction
z$transient.type[i]<- 'divergence'
i<- z$verg.enhance & z$verg.direction
z$transient.type[i]<- 'convergence'

z<- mutate(z, sdfsmooth=spikedensity(rasters,sd=20))

z<- mutate(z,is.convergent.trans=transient.type=='convergence',
           is.real.convergent.trans=real.transient.type=='convergence')

```

```{r findlag}
rnum<- seq(0,250,by=5)
m1<- rnum
m2<- rnum
m3<- rnum
m4<- rnum
count<- 0
isconvergent<- cor(z$verg.angle,z$sdf)>0
if(!isconvergent){message('divergent cell!')}

for (i in rnum) {
  count<- count+1
  z<- mutate(z,sdflead=lag(sdfsmooth,i))
  mcontrol<- lm(sdflead~verg.angle+verg.velocity,data=z)
  # mtest<- lm(sdflead~verg.angle+verg.velocity:transient.type,data=z)
  mcontrol2<-lm(sdflead~verg.angle+real.verg.velocity,data=z)
  if (isconvergent){
    mtest<- lm(sdflead~verg.angle+verg.velocity:is.convergent.trans,
               data=filter(z,!transient.type=='divergence'))
    mtransient<- lm(sdflead~verg.angle+real.verg.velocity:is.real.convergent.trans,
                    data=filter(z,!real.transient.type=='divergence'))
  }else{
    mtest<- lm(sdflead~verg.angle+verg.velocity:is.convergent.trans,
               data=filter(z,!transient.type=='convergence'))
    mtransient<- lm(sdflead~verg.angle+real.verg.velocity:is.real.convergent.trans,
                    data=filter(z,!real.transient.type=='convergence'))
  }
  m1[count]=summary(mcontrol)$r.squared
  m2[count]=summary(mtest)$r.squared
  m3[count]=summary(mtransient)$r.squared
  m4[count]=summary(mcontrol2)$r.squared
}

lagtest<-data.frame(shift=rnum, control=m1, test=m2,transient=m3,control2=m4)

# qplot(shift,control,data=lagtest,geom='text',label=shift)+ggtitle('control')
# qplot(shift,test,data=lagtest,geom='text',label=shift)+ggtitle('piecewise')
# qplot(shift,control2,data=lagtest,geom='text',label=shift)+ggtitle('transients removed')
# qplot(shift,transient,data=lagtest,geom='text',label=shift)+ggtitle('piecewise, transients removed')

bestlag<- lagtest$shift[lagtest$test==max(lagtest$test)]
z<- mutate(z,sdflead=lag(sdfsmooth,bestlag))
bestlag<- lagtest$shift[lagtest$transient==max(lagtest$transient)]
z<- mutate(z,sdflead.transient=lag(sdfsmooth,bestlag))

```


```{r fitmodel}

mcontrol<- lm(sdflead~verg.angle+verg.velocity,data=z)
mcontrol2<- lm(sdflead.transient~verg.angle+real.verg.velocity,data=z)
if(isconvergent){
  mtest<- lm(sdflead~verg.angle+verg.velocity:is.convergent.trans,data=filter(z,!transient.type=='divergence'))
  mtemplate<- lm(sdflead~verg.angle+real.verg.velocity:is.real.convergent.trans,
                    data=filter(z,!real.transient.type=='divergence'))
}else{
  mtest<- lm(sdflead~verg.angle+verg.velocity:is.convergent.trans,data=filter(z,!transient.type=='convergence'))
  mtemplate<- lm(sdflead~verg.angle+real.verg.velocity:is.real.convergent.trans,
                    data=filter(z,!real.transient.type=='convergence'))
}

z<- mutate(z,econtrol=predict(mcontrol,newdata=z),
           econtrol=replace(econtrol,econtrol<0,0),
           etemplate=predict(mtemplate,newdata=z),
           etemplate=replace(etemplate,etemplate<0,0),
           etest=predict(mtest,newdata=z),
           etest=replace(etest,etest<0,0),
           verg.angle.shifted=lag(verg.angle,bestlag),
           showrasters=replace(rasters,rasters<1,NA))

etest.prob<- z$etest/1000

z <-mutate(z,predict.spikes1=rbinom(length(etest.prob),1,etest.prob),
           predict.spikes1=replace(predict.spikes1,predict.spikes1<1,NA),
           predict.spikes2=rbinom(length(etest.prob),1,etest.prob),
           predict.spikes2=replace(predict.spikes2,predict.spikes2<1,NA),
           predict.spikes3=rbinom(length(etest.prob),1,etest.prob),
           predict.spikes3=replace(predict.spikes3,predict.spikes3<1,NA))

purple=cor(z$sdflead[200:nrow(z)],z$etest[200:nrow(z)])^2
orange=cor(z$sdflead[200:nrow(z)],z$etemplate[200:nrow(z)])^2

```

\newpage


#Modeling NRTP firing rate
In this document, we calculate a simple linear model to predict the firing rate of neurons in NRTP.

##Procedure

* Calculate spike density function by convolving rasters with a guassian with sigma=20ms

* Calculate vergence velocity

* Mark periods of convergent and divergent enhancement (when vergence angle changes faster than 15 deg/s)

* Model firing rate using this model: FR ~ verg.angle+verg.velocity:transient.type 
    + Transient.type can be either convergence, divergence or none (non-saccadic vergence velocity)
    + The colon operator indicates an interaction, so the model will fit three separate parameters for vergence velocity

We show the parameters for this fit for the cell `r cellchoice`

```{r show_parameters, results='asis'}
xtable(summary(mtest))
xtable(summary(mtemplate))
# xtable(mc)
```

The model with interactions (purple) gives a $R^2$ of `r purple`. 

The model with interactions and transients removed(orange) gives a $R^2$ of `r orange`. 

```{r plotloop}


z %>%
  group_by(time) %>%
  summarize_each(funs(first))->
  z
windowsize<- 5000
maxtime<-nrow(z)
maxplot<- round(maxtime/windowsize)*windowsize

# if (maxplot>200000){maxplot=200000}

# maxplot=15000

for (window in seq(0,maxplot,by=windowsize)){
  print(
    ggplot(filter(z,time>window,time<window+windowsize))+
      geom_area(aes(time,sdflead))+
      # geom_line(aes(time,econtrol),color='orange')+
      # geom_area(aes(time,econtrol),fill='orange',alpha=.5)+
      geom_area(aes(time,etest),fill='purple',alpha=.5)+
      geom_area(aes(time,etemplate),fill='orange',alpha=0.5)+
      #       geom_line(aes(time,etest),color='purple',alpha=0.7,size=1)+
      # geom_line(aes(time,etemplate),color='orange',alpha=0.7,size=1)+
      # geom_hline(yintercept=-115)+
      # geom_hline(yintercept=-85)+
      
      geom_line(aes(time,verg.velocity-100),color='red')+
      geom_point(aes(time,verg.velocity-100,color=transient.type),size=1,data=filter(z, time>window,time<window+windowsize,enhancenum>0))+
      geom_line(aes(time,real.verg.velocity-200),color='maroon')+
      # geom_line(aes(time,verg.vel.smooth-100),color='black')+
      
      geom_point(aes(time,showrasters+200),shape='|',size=2)+
      # geom_point(aes(time,predict.spikes1+220),shape='|',size=2,color='purple')+
      # geom_point(aes(time,predict.spikes2+225),shape='|',size=2,color='purple')+
      # geom_point(aes(time,predict.spikes3+230),shape='|',size=2,color='purple')+
      
      # geom_point(aes(time,enhancenum*0-50,color=transient.type))+
      
      # geom_line(aes(time,rep*10),color='red')+
      # geom_line(aes(time,lep*10),color='blue'),
      geom_line(aes(time,verg.angle.shifted*5),color='darkgreen',size=1.5)+
      theme(legend.position='bottom')
  )
}

```