---
title: "Modeling NRTP"
author: "Adam"
date: "May 19, 2016"
output: pdf_document
---

```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE,cache=FALSE)
```

```{r,message=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(xtable)
library(tidyr)
# library(broom)
# library(grid)
# library(relaimpo)
# library(leaps)
# library(data.table)
# library(stringr)
source('joinsaccadesuniform.R')
source('Adamhelperfunctions.R')
t<-readRDS('SOA-NRTP.RDS')
#####
cellchoice<- 'Bee-04'
######
t<- filter(t,neuron==cellchoice)
```



```{r}
t %>%
  mutate(time=row_number(),
         sdf=spikedensity(rasters,sd=20),
        verg.velocity=parabolicdiff(verg.angle,14),
         transient.type='none',
         transient.type=replace(transient.type, verg.velocity > 15,'convergence'),
         transient.type=replace(transient.type, verg.velocity < -15, 'divergence'))->
  t

m<- lm(sdf~verg.angle+verg.velocity:transient.type,data=t)

mc<- lm(sdf~verg.angle+verg.velocity,data=t)

t<- mutate(t,e=predict(m,newdata=t),
           ec=predict(mc,newdata=t))

r<- summary(m)$r.squared
rc<- summary(mc)$r.squared

```

#Modeling NRTP firing rate
In this document, we calculate a simple linear model to predict the firing rate of neurons in NRTP.

##Procedure

* Calculate spike density function by convolving rasters with a guassian with sigma=20ms

* Calculate vergence velocity

* Mark periods of convergent and divergent enhancement (when vergence angle changes faster than 15 deg/s)

* Model firing rate using this model: FR ~ verg.angle+verg.velocity:transient:type 
    + Transient.type can be either convergence, divergence or none (non-saccadic vergence velocity)
    + The colon operator indicates an interaction, so the model will fit three separate parameters for vergence velocity

We show the parameters for this fit for the cell `r cellchoice`

```{r show_parameters, results='asis'}
xtable(summary(m))
xtable(mc)
```

The model with interactions gives a $R^2$ of `r r` while the model without considering enhancement has an $R^2$ of `r rc`.


```{r plotmodel, fig.height=8}
window<- 12500
ggplot(filter(t,time>window,time<window+1000))+
             geom_line(aes(time,sdf))+
             geom_line(aes(time,ec),color='orange')+
             geom_line(aes(time,e),color='purple',alpha=1)+
             geom_line(aes(time,verg.velocity),color='pink')+
           # geom_line(aes(time,rep*10),color='red')+
           # geom_line(aes(time,lep*10),color='blue'),
           geom_line(aes(time,verg.angle*10),color='darkgreen')

window<- 22000
ggplot(filter(t,time>window,time<window+2000))+
             geom_line(aes(time,sdf))+
             geom_line(aes(time,ec),color='orange')+
             geom_line(aes(time,e),color='purple',alpha=1)+
             geom_line(aes(time,verg.velocity),color='pink')+
           # geom_line(aes(time,rep*10),color='red')+
           # geom_line(aes(time,lep*10),color='blue'),
           geom_line(aes(time,verg.angle*10),color='darkgreen')
# window<- 74000
# ggplot(filter(t,time>window,time<window+5000))+
#              geom_line(aes(time,sdf))+
#              geom_line(aes(time,ec),color='orange')+
#              geom_line(aes(time,e),color='purple',alpha=1)+
#              geom_line(aes(time,verg.velocity),color='pink')+
#            # geom_line(aes(time,rep*10),color='red')+
#            # geom_line(aes(time,lep*10),color='blue'),
#            geom_line(aes(time,verg.angle*10),color='darkgreen')

window<- 26000
ggplot(filter(t,time>window,time<window+1000))+
             geom_line(aes(time,sdf))+
             geom_line(aes(time,ec),color='orange')+
             geom_line(aes(time,e),color='purple',alpha=1)+
             geom_line(aes(time,verg.velocity),color='pink')+
           # geom_line(aes(time,rep*10),color='red')+
           # geom_line(aes(time,lep*10),color='blue'),
           geom_line(aes(time,verg.angle*10),color='darkgreen')
window<- 44000
ggplot(filter(t,time>window,time<window+5000))+
             geom_line(aes(time,sdf))+
             geom_line(aes(time,ec),color='orange')+
             geom_line(aes(time,e),color='purple',alpha=1)+
             geom_line(aes(time,verg.velocity),color='pink')+
           # geom_line(aes(time,rep*10),color='red')+
           # geom_line(aes(time,lep*10),color='blue'),
           geom_line(aes(time,verg.angle*10),color='darkgreen')

```



```{r peak.fr,fig.height=8}
bufferlength<- 200
saccade.length<- 150

t<-joinsaccadesuniform(t,buffer=200,threshold=20,saccade.length=saccade.length)
  
t %>%
  group_by(neuron,sacnum) %>%
  summarize(peak.verg.velocity=maxabs(verg.velocity),
            Actual=max(sdf),
            Transients=max(e),
            VelocityOnly=max(ec)) %>%
  gather("Model","peakfr",4:6)->
  summaryforplot

ggplot(summaryforplot)+
  geom_point(aes(peak.verg.velocity,peakfr,color=Model),alpha=1/3,size=2)+
  theme(legend.position="top")+
  scale_color_manual(values=c('black','purple','orange'))



  
```

Here we demonstrate the model, shown in purple.
Black is the spike density function.
Pink is the vergence velocity.
Orange is the model that does not consider transients to be different.

\newpage

The coefficients for all cells:
```{r coefficients,results='asis'}
z<- readRDS('TransientModel.RDS')
kable(z)

```