---
title: "Vergence Sensitive Cells in Brainstem"
author: "Adam"
date: "November 1, 2016"
output: 
html_document: 
self_contained: no
runtime: shiny
---

#Introduction
This app shows the activity of vergence-sensitive cells recorded in the supra-oculomotor area (SOA) and the nucleus reticularis tegmenti pontis (NRTP). Cells show sensitivity to both vergence angle (position) and vergence velocity.

* In dark blue is the vergence velocity (difference in left eye velocity and right eye velocity)
* In dark green is the vergence angle (left eye position minus right eye position)
* If the show eye position box is checked:
    + Left eye is blue, right eye is red
    + Solid lines indicate horizontal 
    + Dashed lines indicate vertical position

```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE)
```

```{r,message=FALSE}

library(ggplot2)
library(dplyr)
#library(knitr)
#library(tidyr)
#library(broom)
#library(grid)
# library(relaimpo)
# library(leaps)
#library(data.table)

```


```{R SHINYTRY}
#In order to make the shiny app load fast, I'm just saving the output. See BoostrapSaccades.Rmd for the actual analysis.
# z<-readRDS(file="Bee13forshiny.RDS")
z<-readRDS(file='shinySOANRTP.RDS')
tp<-readRDS('ModelFitValues.RDS')
neurons=unique(z$neuron)
windowsize<-5000
inputPanel(
  
  selectInput("neuronchoice", label = "Select a Neuron:",
                 choices = neurons),
  
  sliderInput("timechoice", label = "Select a time to plot:",
              min=1,
              max=max(z$time-windowsize),
              value=1,
              step=windowsize),
  
  checkboxInput("showeyes",label='Show eye position?')
  # 
  # sliderInput("sdfsd",label='Choose spike density kernel width (ms)',
  #             min=5,
  #             value=15,
  #             max=40,
  #             step=5)
)

renderPlot({
  starttime<-input$timechoice
  neuronchoice<- input$neuronchoice
  showeyes<- input$showeyes
  
  pz<-filter(z,neuron==neuronchoice,time>=starttime,time<starttime+windowsize)
  if (showeyes){
  ggplot(pz)+
    geom_area(aes(time,sdf),alpha=1/10)+
    geom_line(aes(time,lev-rev),color='darkblue',alpha=1)+
    geom_line(aes(time,(lep-rep)*5-100),color='darkgreen',size=1)+
    geom_point(aes(time,showrasters+50),shape='|')+
    geom_line(aes(time,rep+100),color='darkred')+
    geom_line(aes(time,lep+100),color='blue')+
    geom_line(aes(time,repV+120),color='darkred',linetype=2)+
    geom_line(aes(time,lepV+120),color='blue',linetype=2)+
    ylim(c(-100,200))
  }else{
      ggplot(pz)+
    geom_area(aes(time,sdf),alpha=1/10)+
    geom_line(aes(time,lev-rev),color='darkblue',alpha=1)+
    geom_line(aes(time,(lep-rep)*5-100),color='darkgreen')+
    geom_point(aes(time,showrasters+50),shape='|')+
    ylim(c(-100,200))
  }
  
})
renderPlot({
  neuronchoice<- input$neuronchoice
  
  ggplot(tp)+
    geom_point(aes(verg.angle,Slow.Vergence,shape=area),size=3,alpha=0.2)+
    geom_point(aes(verg.angle,Slow.Vergence,shape=area),size=3,color='red',data=filter(tp,neuron==neuronchoice))+
    geom_abline(slope=1)+
    geom_vline(xintercept=0,linetype=2)+
    xlab('Sensitivity to Vergence Angle')+
    ylab('Sensitivity to Vergence Velocity')
  
})

renderPlot({
  showeyes<- input$showeyes
  if (showeyes) {
    
  starttime<-input$timechoice
  neuronchoice<- input$neuronchoice
  
  pz<-filter(z,neuron==neuronchoice,time>=starttime,time<starttime+windowsize)
  start
  ggplot(pz)+
    geom_point(aes(lep,lepV),color='blue',alpha=1/2)+
    geom_point(aes(rep,repV),color='red',alpha=1/2)+
    geom_point(aes((lep[1]+rep[1])/2,(lepV[1]+repV[1])/2),size=9,shape='+')+
    coord_cartesian(xlim=c(-25,25),ylim=c(-25,25))
  }
  
})
# 
# renderPlot({
#   nc<-input$neuronchoice
#   x<-filter(bb,neuron==nc)
#   #plot(x$b[[1]],main=nc)
#   plot(x$bic[[1]],main=nc)
# })

```



