---
title: "NRTP Vergence"
author: "Adam"
date: "February 16, 2016"
output: html_document
---
#Introduction
This is an analysis of the activity of individual neurons in the NRTP of monkeys while they make combined saccade vergence movements. 

#Data Processing
* Load .csv files from the appropriate directory. These .csv files were creating using matlab.
* Calclate the lead time for each neuron.
+ shift data from cell and eye coils to align based on lead time
* Identify saccades.

```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE)
```

```{r,message=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
# library(broom)
# library(grid)
library(relaimpo)
library(leaps)
#library(data.table)
library(stringr)
```

```{r helperfunctions}

spikedensity<-function (rasters,sd=100) {
  gsize<- sd*10
  g<-dnorm(-gsize:gsize,mean=0,sd=sd)
  sdf<-convolve(rasters,g,type="open")
  sdf<-sdf[gsize:(length(sdf)-(gsize+1))]*1000
  sdf
}

dynamiclead<-function(p,lags=seq(10,300,by=10)) {
  
  rsq<-NULL
  for (i in 1:length(lags)) {
    if (lags[i] > 0){
      p$sdflag<-dplyr::lag(p$sdf,lags[i])
    }
    else{
      p$sdflag<-dplyr::lead(p$sdf,lags[i]*-1)
    }
    
    rsq[i]<- summary(lm(sdflag~rep+lep+repV+lepV,data=p))$r.squared
  }
  #return(rsq)
  return(lags[rsq==max(rsq)])
}

findSaccades<-function(ev,threshold=40){
  
  i<-which(abs(ev)>threshold) #find all the times when speed > threshold
  sacoff<-which(diff(i)>15) #minimum duration of an accepted saccade
  sacon<-c(1,sacoff+1) #first saccade
  sacoff<-c(sacoff,length(i)) #end of last saccade
  saccade.onset<-i[sacon] #get actual times
  saccade.offset<-i[sacoff] 
  return(data.frame(saccade.onset,saccade.offset))
}

markSaccades<-function(ev,buffer=15,threshold=40){
  #this function finds and marks saccades given a velocity input
  stimes<-findSaccades(ev,threshold)
  
  nsaccades=nrow(stimes)
  
  #add 10ms buffer to saccade onset and offset
  #extra code to make sure there is at least that much space in the data

  if(stimes$saccade.onset[1]>buffer+1){
  stimes$saccade.onset=stimes$saccade.onset-buffer
  }else{
    stimes$saccade.onset[2:nsaccades] = stimes$saccade.onset[2:nsaccades]-buffer
    stimes$saccade.onset[1]=1
  }
  if (stimes$saccade.offset[nsaccades]+buffer<length(ev)){
    stimes$saccade.offset=stimes$saccade.offset+buffer
  }else{
    stimes$saccade.offset[1:nsaccades-1]=stimes$saccade.offset[1:nsaccades-1]+buffer
    stimes$saccade.offset[nsaccades]=length(ev)
  }
    
  s<-1:length(ev)*0
  
  for (k in 1:nsaccades){
    s[stimes$saccade.onset[k]:stimes$saccade.offset[k]]<- k
    if(k>1){
      s[stimes$saccade.offset[k-1]:stimes$saccade.onset[k]]<-(k*-1)
    }
  }
  s[1:stimes$saccade.onset[1]]<- -1
  s[stimes$saccade.offset[nrow(stimes)]:length(s)]<- (nrow(stimes)*-1)-1
  return(s)
}

parabolicdiff <- function(pos,n=7){
  q <- sum(2*((1:n)^2))
  convoutput<- convolve(pos,c(-n:-1, 1:n),type="open")
  convoutput<- convoutput[(n*2):(length(pos)-((n*2)+1))]
  vels<- c(array(convoutput[1],dim=n*2),convoutput,array(convoutput[length(convoutput)],dim=n*2))
  vels <- vels/q*1000
}

```

```{r loadfiles,cache=TRUE}
#load all the .csv files in the data folder, then add a column naming the neuron, 
#using the file name as the default name, then put them all together in one long data frame

# path<-"C:/Users/User/Desktop/NRTP/"
path<- "C:/Users/setup/Desktop/NRTP Vergence/"

files <- list.files(path=path,pattern='*.csv')
# files<-files[grepl('Patos',files)] # just look at patos files
# files<-files[grepl('Bee',files)] # just look at bee files

nfiles<-length(files)
 # nfiles=1
 
 loadedfiles <- list()
 for (i in 1:nfiles){
   f<- files[i]
   loadedfiles[[i]]<- read.csv(paste(path,f,sep=''))
 }
 
 
```

```{r mergefiles,cache=TRUE}
 #this function puts all the files loaded together into one data.frame

t<-data.frame()
buffer<- 200  
for (i in 1:nfiles) {
  f<- files[i]
  temp=loadedfiles[[i]]
  
  names<-str_match(f,"(^[a-zA-Z]+)-([0-9]+)")
  temp$neuron<-names[1]
  temp$monkey<-names[2]
  temp$cellnum<-names[3]
  temp$sdf<-spikedensity(temp$rasters,sd=10)
  leadtime<-dynamiclead(temp)
  temp<-mutate(temp,
               sdflag=lag(sdf,leadtime),
               s=markSaccades((sqrt(rev^2)+sqrt(revV^2))/2,buffer=buffer,threshold=10),
               time=row_number(),
               verg.angle=rep-lep,
               verg.velocity=parabolicdiff(verg.angle,7),
               isfixation=s<0,
               s=abs(s))
  
  t <-rbind(t,temp)

  }
```

```{r measureMovements,cache=TRUE}
t %>%
  group_by(neuron,s,isfixation) %>%
  mutate(meanfr=mean(sdflag),
         maxfr=max(sdflag),
         R.Hor=mean(rep),
         R.Ver=mean(repV),
         L.Hor=mean(lep),
         L.Ver=mean(lepV),
         mean.Verg.Angle=mean(verg.angle),
         max.Verg.Vel = max(verg.velocity),
         max.Verg.Ang = max(verg.angle),
         nspikes=sum(rasters),
         dur=n(),
         mean.Spikerate=sum(rasters)/dur*1000,
         R.H.Amp=rep[1]-rep[length(rep)],
         L.H.Amp=lep[1]-lep[length(lep)],
         R.V.Amp=repV[1]-repV[length(repV)],
         L.V.Amp=lepV[1]-lepV[length(lepV)],
         maxamp=max(abs(R.H.Amp),abs(R.V.Amp),abs(L.H.Amp),abs(L.V.Amp)))->
  m


#write.csv(m,"NPHFullData.csv")

# 
# 
# t %>%
#   group_by(neuron,s) %>%
#   summarize(meanfr=mean(sdflag),
#             R.Hor=mean(rep),
#             R.Ver=mean(repV),
#             L.Hor=mean(lep),
#             L.Ver=mean(lepV),
#             nspikes=sum(rasters),
#             
#             dur=n(),
#             nspk=sum(rasters)/dur*1000)->
#   summaryforplot
# 
# 
# m %>%
#   filter(isfixation=F,dur>150) %>%
#   group_by(neuron,s) %>%
#   mutate(counter=time-time[1]) ->
# mm

```

```{r verg.fixations,fig.height=10}
m %>%
  filter(isfixation=T,dur>200) %>%
  summarize(mean.Spikerate=mean.Spikerate[1],
            mean.Verg.Angle=mean.Verg.Angle[1],
            dur=dur[1]) ->
summaryforplot

ggplot(aes(mean.Verg.Angle,mean.Spikerate),data=summaryforplot)+
  geom_point(size=2,alpha=1/5)+
  facet_wrap(~neuron)+
  stat_smooth(method='lm')+
  ggtitle('Firing Rate as a function of Vergence Angle during Fixations')

# qplot(mean.Verg.Angle,mean.Spikerate,data=summaryforplot)+
#   geom_point()+
#   stat_smooth(method='lm')+
#   facet_wrap(~neuron)+
#   ggtitle('Firing Rate as a function of Vergence Angle during Fixations')

```

We plot the firing rate of each cell during saccades, including 100ms before and after the movement. Convergent saccades have an amplitude change of +3, divergent, -3 and version saccades are the rest. 

```{r is.there.a.burst, fig.height=20,fig.width=13}

maxabs<- function(x){
  m1<-max(x,na.rm=T)
  m2<-min(x,na.rm=T)
  if (abs(m1)>abs(m2)) {
    return(m1)
  } else{
    return(m2)
  }
  
}
t%>%
  group_by(neuron) %>%
  #   mutate(s=markSaccades((sqrt(rev^2)+sqrt(revV^2))/2,100),
  #          isfixation=s<0,
  #          s=abs(s),
  #          sdf=spikedensity(temp$rasters,sd=20)) %>%
  filter(isfixation == F) %>%
  group_by(neuron,s) %>%
  mutate(dur=n(),
         peak.R.H= maxabs(rev),
         peak.R.V= maxabs(revV),
         peak.L.H= maxabs(lev),
         peak.L.V= maxabs(levV),
         R.H.Amp=rep[n()]-rep[1],
         L.H.Amp=lep[n()]-lep[1],
         R.V.Amp=repV[n()]-repV[1],
         L.V.Amp=lepV[n()]-lepV[1],
         r.angle=atan2(R.V.Amp,R.H.Amp)*180/pi,
         r.amp=sqrt(R.H.Amp^2+R.V.Amp^2),
         nspikes=sum(rasters),
         vect.amp= (sqrt(R.H.Amp^2+R.V.Amp^2)+sqrt(L.H.Amp^2+L.V.Amp^2))/2,
         maxamp=max(abs(R.H.Amp),abs(R.V.Amp),abs(L.H.Amp),abs(L.V.Amp)),
         verg.amp=verg.angle[n()]-verg.angle[1],
         peak.verg.velocity= maxabs(verg.velocity),
         min.verg.trans = min(verg.velocity),
         max.verg.trans = max(verg.velocity),
         maxfr=max(sdf),
         counter=time-time[1])%>%
  group_by(neuron) %>%
  mutate(saccade.type='version',
         saccade.type=replace(saccade.type,verg.amp > 2,'convergence'),
         saccade.type=replace(saccade.type,verg.amp < -2, 'divergence'))->
  p


g<- ggplot(aes(counter-buffer,sdf),data=filter(p,dur<(80+buffer*2)))
g+stat_smooth(method='auto',size=2)+
  facet_wrap(~neuron,ncol=2,scales='free')+
  geom_vline(x=0)+
  ggtitle('Average Spike Rate During Saccades')+
  ylab('Spike Density Function')+
  xlab('Time from Saccade Onset (ms)')
```

```{r verg.amp.scatter, fig.height=10,fig.width=10}

# qplot(verg.amp,maxfr,data=p)+facet_wrap(~neuron,ncol=2)
```


```{r horizontal.direction.burst,fig.height=20,fig.width=13}
# g+
#   # geom_point(alpha=1/30,aes(color=saccade.type))+
#   stat_smooth(method='auto',size=2,aes(color=R.H.Amp>0))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('Average Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('Time from Saccade Onset (ms)')+
#   theme(legend.position="top")

```

```{r spike.histogram, fig.height=10}

# qplot(counter[rasters>0],data=p)+facet_wrap(~neuron)

```
```{r vertical.direction.burst,fig.height=20,fig.width=13}
# g+
#   # geom_point(alpha=1/30,aes(color=saccade.type))+
#   stat_smooth(method='auto',size=2,aes(color=R.V.Amp>0))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('Average Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('Time from Saccade Onset (ms)')+
#   theme(legend.position="top")

```

```{r direction,fig.height=10,fig.width=8}
# qplot(r.angle,r.amp,data=p,color=maxfr)+facet_wrap(~neuron,ncol=2)+
#   coord_polar(theta="x")+
#   theme(legend.position="top")
```

```{r verg.amp,fig.height=10,fig.width=8}
# qplot(r.angle,verg.amp,data=filter(p,verg.amp>0),color=maxfr)+facet_wrap(~neuron,ncol=2)+
#   coord_polar(theta="x")+
#   theme(legend.position="top")+
#   ggtitle('Polar plot by vergence change')
```

```{r verg.change,fig.height=20,fig.width=13}
g+
  # geom_point(alpha=1/30,aes(color=saccade.type))+
  stat_smooth(method='auto',size=2,aes(color=saccade.type))+
  facet_wrap(~neuron,ncol=2,scales='free')+
  geom_vline(x=0)+
  ggtitle('Average Spike Rate During Saccades')+
  ylab('Spike Density Function')+
  xlab('Time from Saccade Onset (ms)')+
  theme(legend.position="top")
```

```{r peak.verg.velocity,fig.height=14,fig.width=10,echo=F}
qplot(peak.verg.velocity,maxfr,data=p,color=saccade.type)+
  facet_wrap(~neuron,ncol=3,scales='free')+
  geom_point(size=3,alpha=1/20)+
  theme(legend.position="top")
# qplot(max.verg.trans,maxfr,data=p,color=verg.amp)+facet_wrap(~neuron,ncol=2)+geom_point(size=3,alpha=1/20)
```

```{r max.verg.velocity,fig.height=14,fig.width=10,echo=F}
qplot(max.verg.trans,maxfr,data=p,color=saccade.type)+
  facet_wrap(~neuron,ncol=3,scales='free')+
  geom_point(size=3,alpha=1/20)+
  theme(legend.position="top")
# qplot(max.verg.trans,maxfr,data=p,color=verg.amp)+facet_wrap(~neuron,ncol=2)+geom_point(size=3,alpha=1/20)
```

##Model Fitting: Peak transient velocity or amplitude of vergence angle change?
In this next section we attempt to distinguish between two factors that are correlated with the peak firing rates of the vergence-burster cells: the amplitude of the vergence angle change and the peak velocity of the vergence transient. It may be possible to distinguish these because there are vergence transients even during saccades without a significant change in vergence angle. The above plot demonstrates this. In some cells, the blue points are below the red points, and above the green ones. This means that for a given peak transient velocity, the cell will fire more if the vergence angle changes more. 

```{r model.fitting,echo=F}
# p %>%
#   group_by(neuron) %>%
#   do(b=calc.relimp(lm(maxfr~verg.angle+peak.verg.velocity,data=.)),
#      bic=regsubsets(maxfr~verg.angle+peak.verg.velocity,.)) ->
#   bb
#     
# for (i in 1:nrow(bb)){
# #  b<-booteval.relimp(bb$b[[i]])
#   b<-bb$b[[i]]
#   plot(b, main=bb$neuron[i])
#   # plot(bb$bic[[i]],main=bb$neuron[i])
#   # plot(bb$bic[[i]],scale=c('adjr2'),main=bb$neuron[i])
# }
```


```{r model.fitting.positive only,echo=F}
# p %>%
#   filter(verg.amp>0) %>%
#   group_by(neuron) %>%
#   do(b=calc.relimp(lm(maxfr~verg.angle+peak.verg.velocity,data=.)),
#      bic=regsubsets(maxfr~verg.angle+peak.verg.velocity,.)) ->
#   bb
#     
# for (i in 1:nrow(bb)){
# #  b<-booteval.relimp(bb$b[[i]])
#   b<-bb$b[[i]]
#   plot(b, main=bb$neuron[i])
#   # plot(bb$bic[[i]],main=bb$neuron[i])
#   # plot(bb$bic[[i]],scale=c('adjr2'),main=bb$neuron[i])
# }
# for (i in 1:nrow(bb)){
# #  b<-booteval.relimp(bb$b[[i]])
#   # b<-bb$b[[i]]
#   # plot(b, main=bb$neuron[i])
#   # plot(bb$bic[[i]],main=bb$neuron[i])
#   plot(bb$bic[[i]],scale=c('adjr2'),main=bb$neuron[i])
# }
```

### Only fit saccades with positive transient higher than negative
```{r model.fitting.peak.verg.vel only,echo=F}
p %>%
  filter(peak.verg.velocity>0) %>%
  group_by(neuron) %>%
  do(b=calc.relimp(lm(maxfr~verg.angle+peak.verg.velocity,data=.)),
     bic=regsubsets(maxfr~verg.angle+peak.verg.velocity,.)) ->
  bb
r <- data.frame()
for (i in 1:nrow(bb)){
  b<- bb$b[[i]]$lmg
  r<-rbind(r,b)
}

r$neuron<-bb$neuron
names(r)<- c(names(bb$b[[1]]$lmg),'neuron')


ggplot(aes(verg.angle,peak.verg.velocity),data=r)+
  geom_point(size=4,aes(color=verg.angle>peak.verg.velocity))+
  geom_text(aes(label=neuron),check_overlap=TRUE,hjust="inward")+
  # coord_cartesian(xlim=c(-0.5,1),ylim=c(-0.5,1))+
  ggtitle('Relative Importance')

# qplot(verg.angle,peak.verg.velocity,data=r, color=neuron,size=4)
# for (i in 1:nrow(bb)){
# #  b<-booteval.relimp(bb$b[[i]])
#   b<-bb$b[[i]]
#   plot(b, main=bb$neuron[i])
#   # plot(bb$bic[[i]],main=bb$neuron[i])
#   # plot(bb$bic[[i]],scale=c('adjr2'),main=bb$neuron[i])
# }
# for (i in 1:nrow(bb)){
# #  b<-booteval.relimp(bb$b[[i]])
#   # b<-bb$b[[i]]
#   # plot(b, main=bb$neuron[i])
#   # plot(bb$bic[[i]],main=bb$neuron[i])
#   plot(bb$bic[[i]],scale=c('adjr2'),main=bb$neuron[i])
# }
```


```{r modeling.max.verg.trans,echo=F}
p %>%
  group_by(neuron) %>%
  do(b=calc.relimp(lm(maxfr~verg.angle+max.verg.trans,data=.)),
     bic=regsubsets(maxfr~verg.angle+max.verg.trans,.)) ->
  bb
r <- data.frame()
for (i in 1:nrow(bb)){
  b<- bb$b[[i]]$lmg
  r<-rbind(r,b)
}

r$neuron<-bb$neuron
names(r)<- c(names(bb$b[[1]]$lmg),'neuron')


ggplot(aes(verg.angle,max.verg.trans),data=r)+
  geom_point(size=4,aes(color=verg.angle>max.verg.trans))+
  geom_text(aes(label=neuron),check_overlap=TRUE,hjust="inward")+
  # coord_cartesian(xlim=c(-0.5,1),ylim=c(-0.5,1))+
  ggtitle('Relative Importance using MAX ONLY')


```

```{r minpeak.verg.velocity,fig.height=10}
# qplot(peak.verg.velocity,maxfr,data=p,color=verg.amp)+facet_wrap(~neuron,ncol=2)+geom_point(size=3,alpha=1/20)
# qplot(min.verg.trans,verg.amp,data=p,color=maxfr)+facet_wrap(~neuron,ncol=2)+geom_point(size=3,alpha=1/20)
```

```{r vect.amp.OR.verg.vel,fig.height=10}
# qplot(peak.verg.velocity,maxfr,data=p,color=verg.amp)+facet_wrap(~neuron,ncol=2)+geom_point(size=3,alpha=1/20)
# qplot(peak.verg.velocity,verg.amp,data=p,color=maxfr)+facet_wrap(~neuron,ncol=2)+geom_point(size=3,alpha=1/20)
```


```{r peakvelRight,fig.height=12,fig.width=8}
# ggplot(filter(p,abs(peak.R.H)>50),aes(peak.R.H,maxfr))+geom_point(aes(color=saccade.type),size=4)+facet_wrap(~neuron,ncol=2)
```

```{r peakvelLeft,fig.height=12,fig.width=8}
# ggplot(filter(p,abs(peak.L.H)>50),aes(peak.L.H,maxfr))+geom_point(aes(color=saccade.type),size=4)+facet_wrap(~neuron,ncol=2)
```


```{r,fig.height=12}
# g<- ggplot(aes(counter-buffer,sdf),data=filter(p,dur<(80+buffer*2),peak.R.H>0))
# g+stat_smooth(method='auto',size=2,aes(color=saccade.type))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('RIGHTWARD Average Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('RIGHTWARD Time from Saccade Onset (ms)')
```

```{r,fig.height=12}
#  g<- ggplot(aes(counter-100,sdf),data=filter(p,dur<(80+buffer*2),peak.R.H<0))
# g+stat_smooth(method='auto',size=2,aes(color=saccade.type))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('LEFTWARD Average Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('LEFTWARD Time from Saccade Onset (ms)')
```

```{r,fig.height=12}
# g<- ggplot(aes(counter-100,sdf),data=filter(p,dur<(80+buffer*2)))
# g+geom_point(method='auto',size=1,aes(color=saccade.type))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('Time from Saccade Onset (ms)')
```

```{r,fig.height=12}
# g<- ggplot(aes(counter-buffer,sdf),data=filter(p,dur>(80+buffer*2)))
# g+geom_point(method='auto',size=1,aes(color=saccade.type))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('SLOW SACCADES Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('Time from Saccade Onset (ms)')
```

```{r,fig.height=12}
# g<- ggplot(aes(counter-100,sdf),data=filter(p,dur>(80+buffer*2)))
# g+stat_smooth(method='auto',size=2,aes(color=saccade.type))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('SLOW SACCADES Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('Time from Saccade Onset (ms)')
```

```{r,fig.height=12}
# g<- ggplot(aes(verg.amp,peak.R.H),data=filter(p,dur<(80+buffer*2)))
# g+geom_point(method='auto',size=3,aes(color=maxfr))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('Leftward Spike Rate During Saccades')+
#   ylab('Peak Right Eye Horizontal Velocity')+
#   xlab('Change in Vergence Angle')
```


```{r,fig.height=12}
# g<- ggplot(aes(verg.amp,maxfr),data=filter(p,dur<(80+buffer*2)))
# g+geom_point(method='auto',size=3,aes(color=sqrt(R.H.Amp^2+R.V.Amp^2)))+
#   facet_wrap(~neuron,ncol=2)

```

```{r,fig.height=12}
# g<- ggplot(aes(verg.amp,sqrt(R.H.Amp^2+R.V.Amp^2)),data=p)
# g+geom_point(method='auto',size=3,aes(color=maxfr))+
#   facet_wrap(~neuron,ncol=2)

```

```{r,fig.height=12}
# p %>%
#   group_by(neuron) %>%
#   mutate(spiketimes=counter-buffer,
#          spiketimes=replace(spiketimes,rasters<1,NA)) %>%
#   group_by(neuron,saccade.type)%>%
#   mutate(saccade.type.count=n())->
#   pplot
# 
# qplot(spiketimes,data=filter(pplot,dur<(80+buffer*2)))+facet_wrap(~neuron,ncol=2)
```

```{r, fig.height=20,fig.width=10}
# qplot(spiketimes,data=filter(pplot,dur<(200+buffer*2)),fill=saccade.type)+facet_grid(neuron~saccade.type)
# ggplot(filter(pplot,dur<(100+buffer*2)),aes(x=spiketimes,fill=saccade.type))+geom_density(alpha=0.2)+facet_wrap(~neuron,ncol=2)
```

```{r, fig.height=20,fig.width=10}
# bb<- 20
# 
# ggplot(filter(pplot,dur<(100+buffer*2)),aes(spiketimes,saccade.type.count*..count..,color=saccade.type,size=2))+geom_freqpoly(binwidth=bb)+facet_wrap(~neuron,ncol=2)+geom_vline(x=0)
```

```{r saccade.amp, fig.height=12}

# qplot(R.H.Amp,maxfr,data=filter(p,abs(R.H.Amp)>3))+facet_wrap(~neuron,ncol=2)
```

```{r saccade.amp.vert, fig.height=12}

# qplot(R.V.Amp,maxfr,data=filter(p,abs(R.V.Amp)>3))+facet_wrap(~neuron,ncol=2)
```

```{r saccade.amp.3d, fig.height=12}
# p %>%
#   group_by(neuron) %>%
#   mutate(maxfr=maxfr/max(maxfr),
#          scalednspikes=nspikes/max(nspikes)) ->
#   pscaled
# 
# qplot(R.H.Amp,R.V.Amp,color=nspikes,data=filter(pscaled,abs(R.H.Amp)>3 | abs(R.V.Amp>3)))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_point(aes(alpha=0.3,size=4))
```

```{r change.rate.position}
# m %>%
# #  filter(isfixation=T) %>%
#   group_by(neuron,s) %>%
#   summarize(mean.verg=mean.Verg.Angle[1],
#             mean.Spikerate=mean.Spikerate[1],
#             maxfr=maxfr[n()],
#             maxamp=maxamp[n()],
#             dur=n()) %>%
#   filter(maxamp>3) %>%
#   arrange(s) %>%
#   mutate(verg.change=mean.verg-lag(mean.verg),
#          rate.change=mean.Spikerate-lag(mean.Spikerate)) ->
#   mva
```
