---
title: "Bootstrap Fixations"
author: "Adam"
date: "October 28, 2015"
output: html_document
---

The following analysis identifies periods of fixation and calculate the average eye position and firing rate during each fixation. Next, it performs a bootstrap analysis to find the confidence intervals of a linear model.


```{r,message=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
library(broom)
library(grid)

```

```{r,cache=FALSE}
#load all the .csv files in the data folder, then add a column naming the neuron, 
#using the file name as the default name, then put them all together in one long data frame

#path<-"~/GitHub/NPH-Analysis/practicedata/"
path<-"~/GitHub/NPH-Analysis/data/"
#path<-"~/GitHub/NPH-Analysis/testdata/"
files <- list.files(path=path,pattern='*.csv')
# files<-files[grepl('Patos',files)] # just look at patos files
files<-files[grepl('Bee',files)] # just look at bee files
t<-data.frame()
for (i in 1:length(files)) {
  temp <- read.csv(paste(path,files[i],sep=''))
  temp$neuron<-gsub('.csv','',files[i])
  t <-rbind(t,temp)
}
```

```{r meanFixation}

findSaccades<-function(ev){
  
  i<-which(abs(ev)>10) #find all the times when speed > threshold
  sacoff<-which(diff(i)>15) #minimum duration of an accepted saccade
  sacon<-c(1,sacoff+1) #first saccade
  sacoff<-c(sacoff,length(i)) #end of last saccade
  saccade.onset<-i[sacon] #get actual times
  saccade.offset<-i[sacoff] 
  return(data.frame(saccade.onset,saccade.offset))
}

markSaccades<-function(ev){
  #this function finds and marks saccades given a velocity input
  stimes<-findSaccades(ev)
  
  nsaccades=nrow(stimes)
  
  #add 10ms buffer to saccade onset and offset
  #extra code to make sure there is at least that much space in the data
  buffer<- 15
  if(stimes$saccade.onset[1]>buffer+1){
  stimes$saccade.onset=stimes$saccade.onset-10
  }else{
    stimes$saccade.onset[2:nsaccades] = stimes$saccade.onset[2:nsaccades]-10
    stimes$saccade.onset[1]=1
  }
  if (stimes$saccade.offset[nsaccades]+buffer<length(ev)){
    stimes$saccade.offset=stimes$saccade.offset+buffer
  }else{
    stimes$saccade.offset[1:nsaccades-1]=stimes$saccade.offset[1:nsaccades-1]+buffer
    stimes$saccade.offset[nsaccades]=length(ev)
  }
    
  s<-1:length(ev)*0
  
  for (k in 1:nsaccades){
    s[stimes$saccade.onset[k]:stimes$saccade.offset[k]]<-k
    if(k>1){
      s[stimes$saccade.offset[k-1]:stimes$saccade.onset[k]]<-(k*-1)
    }
  }
  s[1:stimes$saccade.onset[1]]<- -1
  s[stimes$saccade.offset[nrow(stimes)]:length(s)]<- (nrow(stimes)*-1)
  return(s)
}
```

```{r plotfixations,fig.height=46,fig.width=6}
#use the created functions to mark the saccades
t %>%
  mutate(s=markSaccades((sqrt(rev^2)+sqrt(revV^2))/2)) %>%
  filter(s<0) %>% #just look at periods of fixation
  group_by(s,neuron) %>%
  summarize(R.Horizontal=mean(rep),L.Horizontal=mean(lep),R.Vertical=mean(repV),L.Vertical=mean(lepV),fr=mean(sdf)) %>%
  group_by(neuron)%>%
  mutate(maxFR=max(fr),scaledfr=fr/maxFR) ->
  tt
qplot(R.Horizontal,R.Vertical,color=scaledfr,size=8,data=tt)+facet_grid(neuron~.)
```

```{r plotregressions,fig.height=46,fig.width=10}

tt %>%
  gather(temp,P,3:6) %>%
  separate(temp,c("Eye","HV")) ->
  tc
  qplot(P,scaledfr,data=tc,color=Eye,alpha=0.2)+facet_grid(neuron~HV)+
    xlab('Eye Position (degrees)')+
    ggtitle("Mean FR (scaled) during Fixation")+
    scale_color_manual(values=c('blue','red'))
  
  qplot(P,fr,data=tc,color=Eye,alpha=0.2)+facet_grid(neuron~HV)+
    xlab('Eye Position (degrees)')+
    ggtitle("Mean FR during Fixation")+
    scale_color_manual(values=c('blue','red'))
```

Now the boostrap analysis will begin here. We will probably have to use a loop because I haven't figured out how to get the boostrap.R. function to work for grouped data without losing the groups.

```{r BoostrapTime}
  bootci <- function(t,n=100,alpha=0.05,formula='sdf~rep+lep'){
  t %>%
    bootstrap(n) %>%
    do(tidy(lm(formula,.))) %>%
    group_by(term) %>%
    summarize(low=quantile(estimate, alpha / 2),
            high=quantile(estimate, 1 - alpha / 2)) ->
    ci
  return(ci)
}
  tt<- ungroup(tt)
  n<- unique(tt$neuron)
  ci <- data.frame()
  for (i in 1:length(n)){
    tt %>%
      filter(neuron==n[i]) %>%
      # bootci(n=1999,alpha=0.05,formula='fr~R.Horizontal+L.Horizontal+R.Vertical+L.Vertical') ->
      bootci(n=1999,alpha=0.05,formula='fr~R.Horizontal+R.Vertical') ->
      #bootci(n=1999,alpha=0.05,formula='fr~L.Horizontal+L.Vertical') ->
      #bootci(n=1999,alpha=0.05,formula='fr~L.Horizontal+R.Horizontal') ->
      temp
      temp$neuron<-n[i]
      ci<-rbind(ci,temp)
      
  }
  
```

```{r paramstable}
#ci %>% 
#  select(c(1,2,4)) %>% 
#  spread(term,low) -> 
#  c
#ci %>% 
#  select(c(1,3,4)) %>% 
#  spread(term,high) -> 
#  ch
#full_join(c,ch) %>%
#  arrange(neuron) %>%
#  mutate(angle=atan2(L.Vertical,L.Horizontal)*180/pi)->
#  cij
#kable(cij)

```

```{r plotci, fig.width=8,fig.height=30}
ci %>%
  mutate(m=(low+high)/2) %>%
  filter(term != '(Intercept)') %>%
  ggplot(aes(factor(term),m)) ->
  g
g+geom_linerange(aes(ymin=low,ymax=high,color=neuron),size=2)+
  facet_grid(neuron~.)+
  geom_hline(x=0)+
  coord_flip()

```

```{r directionPlot}
ci %>%
  mutate(m=(low+high)/2) %>%
  select(term,neuron,m) %>%
  spread(term,m) ->
  sci
#   ggplot(sci) +
#   geom_segment(aes(x=0,xend=L.Horizontal,y=0,yend=L.Vertical),size=1.0,arrow=arrow(20))+
#     ylab('Left Eye Vertical') +xlab('Left Eye Horizontal')
  ggplot(sci) +
  geom_segment(aes(x=0,xend=R.Horizontal,y=0,yend=R.Vertical),size=1.0,arrow=arrow(20))+
    ylab('Right Eye Vertical') +xlab('Right Eye Horizontal')
  
```

Now replace params that have zero in the CI with zero

```{r directionGood}
  ci <- mutate(ci,m=(low+high)/2,bad=((low*high)<0))
  ci$m[ci$bad]=0
  ci %>%
    select(term,neuron,m) %>%
    spread(term,m) ->
    scigood
#    ggplot(scigood) +
#     geom_segment(aes(x=0,xend=L.Horizontal,y=0,yend=L.Vertical),size=1.0,arrow=arrow(20))+
#     ylab('Left Eye Vertical') +xlab('Left Eye Horizontal')+ggtitle('Significant Parameters')
  ggplot(scigood) +
  geom_segment(aes(x=0,xend=R.Horizontal,y=0,yend=R.Vertical),size=1.0,arrow=arrow(20))+
    ylab('Right Eye Vertical') +xlab('Right Eye Horizontal')+ggtitle('Significant Paramters')
```

Next, we will identify cells with and without overlap in the CI between the parameters for each eye. 
(in progress)
Next, we will plot the strabismus angle versus firing rate

```{r strabismusangle,fig.width=8,fig.height=40}
#   tt %>%
#     mutate(strab=R.Horizontal-L.Horizontal,dvd=R.Vertical-L.Vertical) ->
#     tt
#   strabangle<-ggplot(tt,aes(strab,fr))
#   strabangle+geom_point()+facet_grid(neuron~.)+stat_smooth(method='lm')+
#     xlab('Strabismus Angle')+ggtitle('Strabismus Angle')
#   
```
```{r dvdplot,fig.width=8,fig.height=40}

#   dvdplot<-ggplot(tt,aes(dvd,fr))
#   dvdplot+geom_point()+facet_grid(neuron~.)+stat_smooth(method='lm')+
#     xlab('DVD: Right minus Left')+ggtitle('DVD')
#   
```

```{r cyclopeanplot, fig.width=8,fig.height=40}
#   tt %>%
#     mutate(C.Horizontal=(L.Horizontal+R.Horizontal)/2,C.Vertical=(L.Vertical+R.Vertical)/2) %>%
#     gather(HV,position,12:13) ->
#     tc
#   cycplot<- ggplot(tc,aes(position,fr))
#   cycplot+geom_point()+facet_grid(neuron~HV)
```