---
title: "BootstrapSaccades"
author: "Adam"
output: html_document
---
#Introduction
This is an analysis of cells believed to be recorded in the NPH of a normal monkey (Bee) and a monkey with exotropia (Patos). The NPH is thought to provide the horizontal integrator for the control of eye movements. Individual neurons in NPH are typically described as either burst-tonic or tonic cells, with activity related to either the position or position and velocity of the eyes. 

#Analysis
*Calclate the lead time for each neuron.
+shift data from cell and eye coils to align based on lead time
*Identify saccades.
+for this analysis, we remove periods of fixation
*fit and evaluate a linear model: Firing Rate ~ eye position/velocity, horizontal/vertical, left/right (8 terms)
+Evaluate using Relative Importance
+Evaluate using BIC and adjusted R^2, using exhaustive search that finds the best model using 1-8 terms
*Optionally, we can restrict our analysis to just disjunctive saccades. This can help to identify monocular cells, since the parameters during conjugate saccades are typically well correlated.


```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE)
```

```{r,message=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
library(broom)
library(grid)
library(relaimpo)
library(leaps)
library(data.table)

```

```{r loadfiles,cache=FALSE}
#load all the .csv files in the data folder, then add a column naming the neuron, 
#using the file name as the default name, then put them all together in one long data frame

#path<-"~/GitHub/NPH-Analysis/practicedata/"
#path<-"~/GitHub/NPH-Analysis/data/"
path<-"~/GitHub/NPH-Analysis/testdata/"
files <- list.files(path=path,pattern='*.csv')
# files<-files[grepl('Patos',files)] # just look at patos files
# files<-files[grepl('Bee',files)] # just look at bee files
t<-data.frame()
for (i in 1:length(files)) {
  temp <- read.csv(paste(path,files[i],sep=''))
  temp$neuron<-gsub('.csv','',files[i])
  t <-rbind(t,temp)
}
```

```{r leadtime}
dynamiclead<-function(p,lags=seq(10,300,by=10)) {

rsq<-NULL
for (i in 1:length(lags)) {
  if (lags[i] > 0){
  p$sdflag<-dplyr::lag(p$sdf,lags[i])
  }
  else{
    p$sdflag<-dplyr::lead(p$sdf,lags[i]*-1)
  }
    
  rsq[i]<- summary(lm(sdflag~rep+lep+repV+lepV,data=p))$r.squared
}
#return(rsq)
return(lags[rsq==max(rsq)])
}

t %>%
  group_by(neuron) %>%
  do(leadtime=dynamiclead(.)) %>%
  mutate(leadtime=as.numeric(leadtime)) ->
  dl
  
dl%>%
  separate(neuron,c("Monkey","cellnum"),remove =FALSE) %>%
  mutate(cellnum=as.numeric(cellnum))->
  dlplot

qplot(cellnum,leadtime/5,data=dlplot,binwidth=10)+facet_grid(Monkey~.)+ylab("Lead Time (ms)")

#At this point I have to switch over to using data.table because dplyr can't handle shifting each group by a different amount. Hopefully this doesn't mess everything else up.
dl<-setDT(dl)
t<-setDT(t)
t<-left_join(t,dl,by="neuron")

#the := operator is actually adding the column shiftsdf to the data table
t<-t[,sdflag:=shift(sdf,leadtime[1]),by=neuron]
t<-as.data.frame(t)

```

```{r markSaccades}

findSaccades<-function(ev){
  
  i<-which(abs(ev)>10) #find all the times when speed > threshold
  sacoff<-which(diff(i)>15) #minimum duration of an accepted saccade
  sacon<-c(1,sacoff+1) #first saccade
  sacoff<-c(sacoff,length(i)) #end of last saccade
  saccade.onset<-i[sacon] #get actual times
  saccade.offset<-i[sacoff] 
  return(data.frame(saccade.onset,saccade.offset))
}

markSaccades<-function(ev){
  #this function finds and marks saccades given a velocity input
  stimes<-findSaccades(ev)
  
  nsaccades=nrow(stimes)
  
  #add 10ms buffer to saccade onset and offset
  #extra code to make sure there is at least that much space in the data
  buffer<- 15
  if(stimes$saccade.onset[1]>buffer+1){
  stimes$saccade.onset=stimes$saccade.onset-10
  }else{
    stimes$saccade.onset[2:nsaccades] = stimes$saccade.onset[2:nsaccades]-10
    stimes$saccade.onset[1]=1
  }
  if (stimes$saccade.offset[nsaccades]+buffer<length(ev)){
    stimes$saccade.offset=stimes$saccade.offset+buffer
  }else{
    stimes$saccade.offset[1:nsaccades-1]=stimes$saccade.offset[1:nsaccades-1]+buffer
    stimes$saccade.offset[nsaccades]=length(ev)
  }
    
  s<-1:length(ev)*0
  
  for (k in 1:nsaccades){
    s[stimes$saccade.onset[k]:stimes$saccade.offset[k]]<-k
    if(k>1){
      s[stimes$saccade.offset[k-1]:stimes$saccade.onset[k]]<-(k*-1)
    }
  }
  s[1:stimes$saccade.onset[1]]<- -1
  s[stimes$saccade.offset[nrow(stimes)]:length(s)]<- (nrow(stimes)*-1)
  return(s)
}
```

```{r isolateSaccades,fig.height=46,fig.width=6}
#use the created functions to mark the saccades
t %>%
  mutate(s=markSaccades((sqrt(rev^2)+sqrt(revV^2))/2),time=row_number()) %>%
  filter(s>0)-> #mark saccades gives saccades positive numbers and everything else negative
  tt
```


```{r relativeImportance, message=FALSE}
# library(relaimpo)
# 
# tt %>%
#   group_by(neuron) %>%
#   do(b=calc.relimp(lm("sdflag~rep+rev+repV+revV+lep+lev+lepV+levV",.))) ->
#   bb
# for (i in 1:nrow(bb)){
#   plot(bb$b[[i]],main=bb$neuron[i])
# }
```

```{r disjunctiveOnly, cached=TRUE}

tt %>% 
  group_by(neuron,s) %>% 
  summarize(R.H.Amp=rep[1]-rep[length(rep)],
            L.H.Amp=lep[1]-lep[length(lep)],
            R.V.Amp=repV[1]-repV[length(repV)],
            L.V.Amp=lepV[1]-lepV[length(lepV)],
            maxamp=max(abs(R.H.Amp),abs(R.V.Amp),abs(L.H.Amp),abs(L.V.Amp))) %>%
  mutate(disjH=sign(R.H.Amp*L.H.Amp)<0,disjV=sign(R.V.Amp*L.V.Amp)<0,disjEither=disjH | disjV) ->
  amp
tt <-left_join(tt,amp,by=c('s','neuron'))

minAmp<-5
nDisjunctive<-nrow(filter(amp,maxamp>minAmp & disjEither))
nTotal<- nrow(filter(amp,maxamp>minAmp))
```


```{r BICcalc}
#This function can either just calculate the relative importance or use bootstrapping to find a confidence interval for the relative importance. Bootstrapping obviously takes a long time. Also, it can either fit the model to all of the saccades, or just the disjunctive ones. 
tt %>%
  filter(maxamp>minAmp,sdflag>10) %>%
  #filter(maxamp>minAmp & disjEither,sdflag>10) %>%
  group_by(neuron) %>%
#    do(b=boot.relimp(lm("sdflag~rep+rev+repV+revV+lep+lev+lepV+levV",.),b=1999),
    do(b=calc.relimp(lm("sdflag~rep+rev+repV+revV+lep+lev+lepV+levV",.)),
    bic=regsubsets(sdflag~rep+rev+repV+revV+lep+lev+lepV+levV,.)) ->
  bb

for (i in 1:nrow(bb)){
#  b<-booteval.relimp(bb$b[[i]])
  b<-bb$b[[i]]
  plot(b, main=bb$neuron[i])
  plot(bb$bic[[i]],main=bb$neuron[i])
  plot(bb$bic[[i]],scale=c('adjr2'),main=bb$neuron[i])
}
```

There were a total of `r nDisjunctive` disjunctive Saccades, out of `r nTotal` total saccades.

```{r bootstrapModel}
#   bootci <- function(t,n=100,alpha=0.05,formula='sdf~rep+lep'){
#   t %>%
#     bootstrap(n) %>%
#     do(tidy(lm(formula,.))) %>%
#     group_by(term) %>%
#     summarize(low=quantile(estimate, alpha / 2),
#             high=quantile(estimate, 1 - alpha / 2)) ->
#     ci
#   return(ci)
#   }
# 
#   tt<- ungroup(tt)
#   n<- unique(tt$neuron)
#   ci <- data.frame()
#   f<- "FRtd~R.P.Horizontal+L.P.Horizontal+R.V.Horizontal+L.V.Horizontal+R.P.Vertical+L.P.Vertical+R.V.Vertical+L.V.Vertical"
#   tt %>%
#     filter(sdflag>10,maxamp>2, disjEither) %>%
#     rename(R.P.Horizontal=rep,L.P.Horizontal=lep,
#              R.V.Horizontal=rev,L.V.Horizontal=lev,
#              R.P.Vertical=repV,L.P.Vertical=lepV,
#              R.V.Vertical=revV,L.V.Vertical=levV,
#              FRtd=sdflag) ->
#     tmodel
#   for (i in 1:length(n)){
#     tmodel %>%
#       filter(neuron==n[i]) %>%
#       bootci(n=1999,alpha=0.01,formula=f) ->
#       temp
#       temp$neuron<-n[i]
#       ci<-rbind(ci,temp)
#  }
```
 
```{r plotci, fig.width=7,fig.height=30}
# ci %>%
#   mutate(m=(low+high)/2) %>%
#   filter(term != '(Intercept)') ->
#     pci
# #   g<-ggplot(pci,aes(factor(term),m)) 
# #   
# # g+geom_linerange(aes(ymin=low,ymax=high,color=neuron),size=2)+
# #   facet_grid(neuron~.)+
# #   geom_hline(x=0)+
# #   coord_flip()
# 
# 
# pci %>%
#   separate(term,c('Direction','PV','HV'),remove=FALSE) %>%
#   mutate(scale=9*as.numeric(PV=='V')+1,
#          low=low*scale, high=high*scale,m=m*scale) ->
#   ppci
# 
#   g<-ggplot(ppci,aes(factor(term),m)) 
#   
# g+geom_linerange(aes(ymin=low,ymax=high,color=neuron),size=2)+
#   facet_grid(neuron~.)+
#   geom_hline(x=0)+
#   coord_flip()+
  # ylab('Coefficient: Velocity scaled by 10')
```

