---
title: "NRTP Vergence"
author: "Adam"
date: "February 8, 2016"
output: html_document
---
#Introduction
This is an analysis of the activity of individual neurons in the NRTP of monkeys while they make combined saccade vergence movements. 

#Data Processing
* Load .csv files from the appropriate directory. These .csv files were creating using matlab.
* Calclate the lead time for each neuron.
+ shift data from cell and eye coils to align based on lead time
* Identify saccades.

```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE)
```

```{r,message=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
# library(broom)
# library(grid)
# library(relaimpo)
# library(leaps)
#library(data.table)
library(stringr)
```

```{r helperfunctions}

spikedensity<-function (rasters,sd=100) {
  gsize<- sd*10
  g<-dnorm(-gsize:gsize,mean=0,sd=sd)
  sdf<-convolve(rasters,g,type="open")
  sdf<-sdf[gsize:(length(sdf)-(gsize+1))]*1000
  sdf
}

dynamiclead<-function(p,lags=seq(10,300,by=10)) {
  
  rsq<-NULL
  for (i in 1:length(lags)) {
    if (lags[i] > 0){
      p$sdflag<-dplyr::lag(p$sdf,lags[i])
    }
    else{
      p$sdflag<-dplyr::lead(p$sdf,lags[i]*-1)
    }
    
    rsq[i]<- summary(lm(sdflag~rep+lep+repV+lepV,data=p))$r.squared
  }
  #return(rsq)
  return(lags[rsq==max(rsq)])
}

findSaccades<-function(ev){
  
  i<-which(abs(ev)>10) #find all the times when speed > threshold
  sacoff<-which(diff(i)>15) #minimum duration of an accepted saccade
  sacon<-c(1,sacoff+1) #first saccade
  sacoff<-c(sacoff,length(i)) #end of last saccade
  saccade.onset<-i[sacon] #get actual times
  saccade.offset<-i[sacoff] 
  return(data.frame(saccade.onset,saccade.offset))
}

markSaccades<-function(ev){
  #this function finds and marks saccades given a velocity input
  stimes<-findSaccades(ev)
  
  nsaccades=nrow(stimes)
  
  #add 10ms buffer to saccade onset and offset
  #extra code to make sure there is at least that much space in the data
  buffer<- 15
  if(stimes$saccade.onset[1]>buffer+1){
  stimes$saccade.onset=stimes$saccade.onset-buffer
  }else{
    stimes$saccade.onset[2:nsaccades] = stimes$saccade.onset[2:nsaccades]-buffer
    stimes$saccade.onset[1]=1
  }
  if (stimes$saccade.offset[nsaccades]+buffer<length(ev)){
    stimes$saccade.offset=stimes$saccade.offset+buffer
  }else{
    stimes$saccade.offset[1:nsaccades-1]=stimes$saccade.offset[1:nsaccades-1]+buffer
    stimes$saccade.offset[nsaccades]=length(ev)
  }
    
  s<-1:length(ev)*0
  
  for (k in 1:nsaccades){
    s[stimes$saccade.onset[k]:stimes$saccade.offset[k]]<-k
    if(k>1){
      s[stimes$saccade.offset[k-1]:stimes$saccade.onset[k]]<-(k*-1)
    }
  }
  s[1:stimes$saccade.onset[1]]<- -1
  s[stimes$saccade.offset[nrow(stimes)]:length(s)]<- (nrow(stimes)*-1)-1
  return(s)
}

parabolicdiff <- function(pos,n=7){
  q <- sum(2*((1:n)^2))
  convoutput<- convolve(pos,c(-n:-1, 1:n),type="open")
  convoutput<- convoutput[(n*2):(length(pos)-((n*2)+1))]
  vels<- c(array(convoutput[1],dim=n*2),convoutput,array(convoutput[length(convoutput)],dim=n*2))
  vels <- vels/q*1000
}

```

```{r loadfiles,cache=FALSE}
#load all the .csv files in the data folder, then add a column naming the neuron, 
#using the file name as the default name, then put them all together in one long data frame

path<-"C:/Users/setup/Desktop/NRTP Vergence/"

files <- list.files(path=path,pattern='*.csv')
# files<-files[grepl('Patos',files)] # just look at patos files
# files<-files[grepl('Bee',files)] # just look at bee files
t<-data.frame()
nfiles<-length(files)
# nfiles=1
for (i in 1:nfiles) {
  f<-files[i]
  temp <- read.csv(paste(path,f,sep=''))
  names<-str_match(f,"(^[a-zA-Z]+)-([0-9]+)")
  temp$neuron<-names[1]
  temp$monkey<-names[2]
  temp$cellnum<-names[3]
  temp$sdf<-spikedensity(temp$rasters,sd=100)
  leadtime<-dynamiclead(temp)
  temp<-mutate(temp,
               sdflag=lag(sdf,leadtime),
               s=markSaccades((sqrt(rev^2)+sqrt(revV^2))/2),
               time=row_number(),
               verg.angle=rep-lep,
               verg.velocity=parabolicdiff(verg.angle,7),
               isfixation=s<0,
               s=abs(s))
  
  t <-rbind(t,temp)

  }
```

```{r measureMovements}

t %>%
  group_by(neuron,s,isfixation) %>%
  mutate(meanfr=mean(sdflag),
         maxfr=max(sdflag),
         R.Hor=mean(rep),
         R.Ver=mean(repV),
         L.Hor=mean(lep),
         L.Ver=mean(lepV),
         mean.Verg.Angle=mean(verg.angle),
         max.Verg.Vel = max(verg.velocity),
         max.Verg.Ang = max(verg.angle),
         nspikes=sum(rasters),
         dur=n(),
         mean.Spikerate=sum(rasters)/dur*1000,
         R.H.Amp=rep[1]-rep[length(rep)],
         L.H.Amp=lep[1]-lep[length(lep)],
         R.V.Amp=repV[1]-repV[length(repV)],
         L.V.Amp=lepV[1]-lepV[length(lepV)],
         maxamp=max(abs(R.H.Amp),abs(R.V.Amp),abs(L.H.Amp),abs(L.V.Amp)))->
  m

#write.csv(m,"NPHFullData.csv")



t %>%
  group_by(neuron,s) %>%
  summarize(meanfr=mean(sdflag),
            R.Hor=mean(rep),
            R.Ver=mean(repV),
            L.Hor=mean(lep),
            L.Ver=mean(lepV),
            nspikes=sum(rasters),
            
            dur=n(),
            nspk=sum(rasters)/dur*1000)->
  summaryforplot


m %>%
  filter(isfixation=F,dur>150) %>%
  group_by(neuron,s) %>%
  mutate(counter=time-time[1]) ->
mm

```

```{r verg.fixations}
m %>%
  filter(isfixation=T,dur>200) %>%
  summarize(mean.Spikerate=mean.Spikerate[1],
            mean.Verg.Angle=mean.Verg.Angle[1],
            dur=dur[1]) ->
summaryforplot


qplot(mean.Verg.Angle,mean.Spikerate,data=summaryforplot,color=dur)+
  geom_point(size=4)+
  stat_smooth(method='lm')+
  facet_wrap(~neuron)+
  ggtitle('Firing Rate as a function of Vergence Angle during Fixations')
  

static.model<-lm(mean.Spikerate~mean.Verg.Angle,data=summaryforplot)

quick.predict <- function(static.model,value) {
  return(static.model$coefficients[1]+static.model$coefficients[2]*value)
}
```

```{r change.rate.position}
m %>%
#  filter(isfixation=T) %>%
  group_by(neuron,s) %>%
  summarize(mean.verg=mean.Verg.Angle[1],
            mean.Spikerate=mean.Spikerate[1],
            maxfr=maxfr[n()],
            maxamp=maxamp[n()],
            dur=n()) %>%
  filter(maxamp>3) %>%
  arrange(s) %>%
  mutate(verg.change=mean.verg-lag(mean.verg),
         rate.change=mean.Spikerate-lag(mean.Spikerate)) ->
  mva

qplot(verg.change,rate.change,data=mva)+facet_wrap(~neuron)
```

```{r peakfr}
qplot(verg.change,maxfr,data=mva)+facet_wrap(~neuron)
```


```{r verg.velocity}
m %>%
  filter(isfixation==F,dur>40,max.Verg.Vel<40) %>%
  summarize(max.Verg.Vel=max.Verg.Vel[1],
            maxfr=maxfr[1]) ->
summaryforplot


qplot(max.Verg.Vel,maxfr,data=summaryforplot)+
  geom_point(size=4)+
  stat_smooth(method='lm')+
  facet_wrap(~neuron)+
  ggtitle('Max Firing Rate as a function of Max Vergence Velocity during Saccades')
```


```{r saccade.dynamics}


nsac<-20 #number of saccades to show
sacsamples<-unique(m$s[m$s>0])
sacsamples<-sample(sacsamples,nsac)

m %>%
  filter(isfixation==F,s %in% sacsamples) %>%
  group_by(neuron,s) %>%
  mutate(counter=time-time[1]) ->
summaryforplot


qplot(verg.velocity,sdflag,data=summaryforplot,color=as.factor(s))+
  facet_wrap(~neuron)+
  ggtitle('Firing Rate during Saccades')
```

```{r saccade.dynamics.adjusted}


m %>%
  filter(isfixation==F,s %in% sacsamples) %>%
  group_by(neuron,s) %>%
  mutate(counter=time-time[1],
         predicted.fr = quick.predict(static.model,verg.angle),
         velocity.cor = cor(sdflag,verg.velocity)) ->
summaryforplot


qplot(verg.velocity,sdflag-predicted.fr,data=summaryforplot,color=as.factor(s))+
  facet_wrap(~neuron)+
  ggtitle('Firing Rate during Saccades')
```

```{r saccades.cor.test}


m %>%
  filter(isfixation==F) %>%
  group_by(neuron,s) %>%
  mutate(counter=time-time[1],
         predicted.fr = quick.predict(static.model,verg.angle),
         velocity.cor = cor(sdflag,verg.velocity)) ->
summaryforplot

qplot(velocity.cor,data=summaryforplot)+facet_wrap(~neuron)
#qplot(verg.velocity,sdflag-predicted.fr,data=filter(summaryforplot,velocity.cor< -0.9),color=as.factor(s))+
#  ggtitle('Firing Rate during Saccades')

#qplot(counter,sdflag-predicted.fr)

```

```{r Firing.Rate.adjusted}


m %>%
  filter(isfixation==F,s %in% sacsamples) %>%
  group_by(neuron,s) %>%
  mutate(counter=time-time[1],
         predicted.fr = quick.predict(static.model,verg.angle),
         velocity.cor = cor(sdflag,verg.velocity)) ->
summaryforplot


qplot(counter,sdflag-predicted.fr,data=summaryforplot,color=as.factor(s))+
  facet_wrap(~neuron)+
  ggtitle('Firing Rate during Saccades')
```



```{r testfig}
ggplot(aes(time),data=filter(t,time<50000,neuron=='Bee-01'))+geom_line(aes(time,rep),color='red')+geom_line(aes(time,lep),color='blue')+geom_line(aes(time,verg.angle),col='green')+geom_line(aes(time,sdf/10))
```
