---
title: "NRTP Vergence"
author: "Adam"
date: "February 16, 2016"
output: html_document
---
#Introduction
This is an analysis of the activity of individual neurons in the NRTP of monkeys while they make combined saccade vergence movements. 

#Data Processing
* Load .csv files from the appropriate directory. These .csv files were creating using matlab.
* Calclate the lead time for each neuron.
+ shift data from cell and eye coils to align based on lead time
* Identify saccades.

```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE)
```

```{r,message=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
# library(broom)
# library(grid)
# library(relaimpo)
# library(leaps)
#library(data.table)
library(stringr)
```

```{r helperfunctions}

spikedensity<-function (rasters,sd=100) {
  gsize<- sd*10
  g<-dnorm(-gsize:gsize,mean=0,sd=sd)
  sdf<-convolve(rasters,g,type="open")
  sdf<-sdf[gsize:(length(sdf)-(gsize+1))]*1000
  sdf
}

dynamiclead<-function(p,lags=seq(10,300,by=10)) {
  
  rsq<-NULL
  for (i in 1:length(lags)) {
    if (lags[i] > 0){
      p$sdflag<-dplyr::lag(p$sdf,lags[i])
    }
    else{
      p$sdflag<-dplyr::lead(p$sdf,lags[i]*-1)
    }
    
    rsq[i]<- summary(lm(sdflag~rep+lep+repV+lepV,data=p))$r.squared
  }
  #return(rsq)
  return(lags[rsq==max(rsq)])
}

findSaccades<-function(ev,threshold=40){
  
  i<-which(abs(ev)>threshold) #find all the times when speed > threshold
  sacoff<-which(diff(i)>15) #minimum duration of an accepted saccade
  sacon<-c(1,sacoff+1) #first saccade
  sacoff<-c(sacoff,length(i)) #end of last saccade
  saccade.onset<-i[sacon] #get actual times
  saccade.offset<-i[sacoff] 
  return(data.frame(saccade.onset,saccade.offset))
}

markSaccades<-function(ev,buffer=15,threshold=40){
  #this function finds and marks saccades given a velocity input
  stimes<-findSaccades(ev,threshold)
  
  nsaccades=nrow(stimes)
  
  #add 10ms buffer to saccade onset and offset
  #extra code to make sure there is at least that much space in the data

  if(stimes$saccade.onset[1]>buffer+1){
  stimes$saccade.onset=stimes$saccade.onset-buffer
  }else{
    stimes$saccade.onset[2:nsaccades] = stimes$saccade.onset[2:nsaccades]-buffer
    stimes$saccade.onset[1]=1
  }
  if (stimes$saccade.offset[nsaccades]+buffer<length(ev)){
    stimes$saccade.offset=stimes$saccade.offset+buffer
  }else{
    stimes$saccade.offset[1:nsaccades-1]=stimes$saccade.offset[1:nsaccades-1]+buffer
    stimes$saccade.offset[nsaccades]=length(ev)
  }
    
  s<-1:length(ev)*0
  
  for (k in 1:nsaccades){
    s[stimes$saccade.onset[k]:stimes$saccade.offset[k]]<- k
    if(k>1){
      s[stimes$saccade.offset[k-1]:stimes$saccade.onset[k]]<-(k*-1)
    }
  }
  s[1:stimes$saccade.onset[1]]<- -1
  s[stimes$saccade.offset[nrow(stimes)]:length(s)]<- (nrow(stimes)*-1)-1
  return(s)
}

parabolicdiff <- function(pos,n=7){
  q <- sum(2*((1:n)^2))
  convoutput<- convolve(pos,c(-n:-1, 1:n),type="open")
  convoutput<- convoutput[(n*2):(length(pos)-((n*2)+1))]
  vels<- c(array(convoutput[1],dim=n*2),convoutput,array(convoutput[length(convoutput)],dim=n*2))
  vels <- vels/q*1000
}

```

```{r loadfiles,cache=TRUE}
#load all the .csv files in the data folder, then add a column naming the neuron, 
#using the file name as the default name, then put them all together in one long data frame

path<-"C:/Users/User/Desktop/NRTP/"

files <- list.files(path=path,pattern='*.csv')
# files<-files[grepl('Patos',files)] # just look at patos files
# files<-files[grepl('Bee',files)] # just look at bee files

nfiles<-length(files)
 # nfiles=1
 
 loadedfiles <- list()
 for (i in 1:nfiles){
   f<- files[i]
   loadedfiles[[i]]<- read.csv(paste(path,f,sep=''))
 }
 
 
```

```{r mergefiles,cache=TRUE}
 #this function puts all the files loaded together into one data.frame

t<-data.frame()
buffer<- 200  
for (i in 1:nfiles) {
  f<- files[i]
  temp=loadedfiles[[i]]
  
  names<-str_match(f,"(^[a-zA-Z]+)-([0-9]+)")
  temp$neuron<-names[1]
  temp$monkey<-names[2]
  temp$cellnum<-names[3]
  temp$sdf<-spikedensity(temp$rasters,sd=10)
  leadtime<-dynamiclead(temp)
  temp<-mutate(temp,
               sdflag=lag(sdf,leadtime),
               s=markSaccades((sqrt(rev^2)+sqrt(revV^2))/2,buffer=buffer,threshold=10),
               time=row_number(),
               verg.angle=rep-lep,
               verg.velocity=parabolicdiff(verg.angle,7),
               isfixation=s<0,
               s=abs(s))
  
  t <-rbind(t,temp)

  }
```

```{r measureMovements}

t %>%
  group_by(neuron,s,isfixation) %>%
  mutate(meanfr=mean(sdflag),
         maxfr=max(sdflag),
         R.Hor=mean(rep),
         R.Ver=mean(repV),
         L.Hor=mean(lep),
         L.Ver=mean(lepV),
         mean.Verg.Angle=mean(verg.angle),
         max.Verg.Vel = max(verg.velocity),
         max.Verg.Ang = max(verg.angle),
         nspikes=sum(rasters),
         dur=n(),
         mean.Spikerate=sum(rasters)/dur*1000,
         R.H.Amp=rep[1]-rep[length(rep)],
         L.H.Amp=lep[1]-lep[length(lep)],
         R.V.Amp=repV[1]-repV[length(repV)],
         L.V.Amp=lepV[1]-lepV[length(lepV)],
         maxamp=max(abs(R.H.Amp),abs(R.V.Amp),abs(L.H.Amp),abs(L.V.Amp)))->
  m

#write.csv(m,"NPHFullData.csv")

# 
# 
# t %>%
#   group_by(neuron,s) %>%
#   summarize(meanfr=mean(sdflag),
#             R.Hor=mean(rep),
#             R.Ver=mean(repV),
#             L.Hor=mean(lep),
#             L.Ver=mean(lepV),
#             nspikes=sum(rasters),
#             
#             dur=n(),
#             nspk=sum(rasters)/dur*1000)->
#   summaryforplot
# 
# 
# m %>%
#   filter(isfixation=F,dur>150) %>%
#   group_by(neuron,s) %>%
#   mutate(counter=time-time[1]) ->
# mm

```

```{r verg.fixations}
m %>%
  filter(isfixation=T,dur>200) %>%
  summarize(mean.Spikerate=mean.Spikerate[1],
            mean.Verg.Angle=mean.Verg.Angle[1],
            dur=dur[1]) ->
summaryforplot


qplot(mean.Verg.Angle,mean.Spikerate,data=summaryforplot,color=dur)+
  geom_point(size=4)+
  stat_smooth(method='lm')+
  facet_wrap(~neuron)+
  ggtitle('Firing Rate as a function of Vergence Angle during Fixations')

```

We plot the firing rate of each cell during saccades, including 100ms before and after the movement. Convergent saccades have an amplitude change of +3, divergent, -3 and version saccades are the rest. 

```{r is.there.a.burst, fig.height=10,warning=FALSE,message=FALSE}

maxabs<- function(x){
  m1<-max(x,na.rm=T)
  m2<-min(x,na.rm=T)
  if (abs(m1)>abs(m2)) {
    return(m1)
  } else{
    return(m2)
  }
  
}
t%>%
  group_by(neuron) %>%
  #   mutate(s=markSaccades((sqrt(rev^2)+sqrt(revV^2))/2,100),
  #          isfixation=s<0,
  #          s=abs(s),
  #          sdf=spikedensity(temp$rasters,sd=20)) %>%
  filter(isfixation == F) %>%
  group_by(neuron,s) %>%
  mutate(dur=n(),
         peak.R.H= maxabs(rev),
         peak.R.V= maxabs(revV),
         peak.L.H= maxabs(lev),
         peak.L.V= maxabs(levV),
         R.H.Amp=rep[n()]-rep[1],
         L.H.Amp=lep[n()]-lep[1],
         R.V.Amp=repV[n()]-repV[1],
         L.V.Amp=lepV[n()]-lepV[1],
         nspikes=sum(rasters),
         maxamp=max(abs(R.H.Amp),abs(R.V.Amp),abs(L.H.Amp),abs(L.V.Amp)),
         verg.amp=verg.angle[n()]-verg.angle[1],
         maxfr=max(sdf),
         counter=time-time[1])%>%
  group_by(neuron) %>%
  mutate(saccade.type='version',
         saccade.type=replace(saccade.type,verg.amp > 2,'convergence'),
         saccade.type=replace(saccade.type,verg.amp < -2, 'divergence'))->
  p


g<- ggplot(aes(counter-buffer,sdf),data=filter(p,dur<(80+buffer*2)))
g+stat_smooth(method='auto',size=2,aes(color=saccade.type))+
  facet_wrap(~neuron,ncol=2)+
  geom_vline(x=0)+
  ggtitle('Average Spike Rate During Saccades')+
  ylab('Spike Density Function')+
  xlab('Time from Saccade Onset (ms)')



```

```{r peakvelRight,fig.height=12,fig.width=8}
# ggplot(filter(p,abs(peak.R.H)>50),aes(peak.R.H,maxfr))+geom_point(aes(color=saccade.type),size=4)+facet_wrap(~neuron,ncol=2)
```

```{r peakvelLeft,fig.height=12,fig.width=8}
# ggplot(filter(p,abs(peak.L.H)>50),aes(peak.L.H,maxfr))+geom_point(aes(color=saccade.type),size=4)+facet_wrap(~neuron,ncol=2)
```


```{r,fig.height=12}
# g<- ggplot(aes(counter-buffer,sdf),data=filter(p,dur<(80+buffer*2),peak.R.H>0))
# g+stat_smooth(method='auto',size=2,aes(color=saccade.type))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('RIGHTWARD Average Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('RIGHTWARD Time from Saccade Onset (ms)')
```

```{r,fig.height=12}
#  g<- ggplot(aes(counter-100,sdf),data=filter(p,dur<(80+buffer*2),peak.R.H<0))
# g+stat_smooth(method='auto',size=2,aes(color=saccade.type))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('LEFTWARD Average Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('LEFTWARD Time from Saccade Onset (ms)')
```

```{r,fig.height=12}
# g<- ggplot(aes(counter-100,sdf),data=filter(p,dur<(80+buffer*2)))
# g+geom_point(method='auto',size=1,aes(color=saccade.type))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('Time from Saccade Onset (ms)')
```

```{r,fig.height=12}
# g<- ggplot(aes(counter-buffer,sdf),data=filter(p,dur>(80+buffer*2)))
# g+geom_point(method='auto',size=1,aes(color=saccade.type))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('SLOW SACCADES Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('Time from Saccade Onset (ms)')
```

```{r,fig.height=12}
# g<- ggplot(aes(counter-100,sdf),data=filter(p,dur>(80+buffer*2)))
# g+stat_smooth(method='auto',size=2,aes(color=saccade.type))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('SLOW SACCADES Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('Time from Saccade Onset (ms)')
```

```{r,fig.height=12}
# g<- ggplot(aes(verg.amp,peak.R.H),data=filter(p,dur<(80+buffer*2)))
# g+geom_point(method='auto',size=3,aes(color=maxfr))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('Leftward Spike Rate During Saccades')+
#   ylab('Peak Right Eye Horizontal Velocity')+
#   xlab('Change in Vergence Angle')
```


```{r,fig.height=12}
# g<- ggplot(aes(verg.amp,maxfr),data=filter(p,dur<(80+buffer*2)))
# g+geom_point(method='auto',size=3,aes(color=sqrt(R.H.Amp^2+R.V.Amp^2)))+
#   facet_wrap(~neuron,ncol=2)

```

```{r,fig.height=12}
# g<- ggplot(aes(verg.amp,sqrt(R.H.Amp^2+R.V.Amp^2)),data=p)
# g+geom_point(method='auto',size=3,aes(color=maxfr))+
#   facet_wrap(~neuron,ncol=2)

```

```{r,fig.height=12}
p %>%
  group_by(neuron) %>%
  mutate(spiketimes=counter-buffer,
         spiketimes=replace(spiketimes,rasters<1,NA)) %>%
  group_by(neuron,saccade.type)%>%
  mutate(saccade.type.count=n())->
  pplot

qplot(spiketimes,data=filter(pplot,dur<(80+buffer*2)))+facet_wrap(~neuron,ncol=2)
```

```{r, fig.height=20,fig.width=10}
# qplot(spiketimes,data=filter(pplot,dur<(200+buffer*2)),fill=saccade.type)+facet_grid(neuron~saccade.type)
# ggplot(filter(pplot,dur<(100+buffer*2)),aes(x=spiketimes,fill=saccade.type))+geom_density(alpha=0.2)+facet_wrap(~neuron,ncol=2)
```

```{r, fig.height=20,fig.width=10}
bb<- 20

ggplot(filter(pplot,dur<(100+buffer*2)),aes(spiketimes,10000*..density..,color=saccade.type))+geom_freqpoly(binwidth=bb)+facet_wrap(~neuron,ncol=2)
```

```{r saccade.amp, fig.height=12}

# qplot(R.H.Amp,maxfr,data=filter(p,abs(R.H.Amp)>3))+facet_wrap(~neuron,ncol=2)
```

```{r saccade.amp.vert, fig.height=12}

# qplot(R.V.Amp,maxfr,data=filter(p,abs(R.V.Amp)>3))+facet_wrap(~neuron,ncol=2)
```

```{r saccade.amp.3d, fig.height=12}
# p %>%
#   group_by(neuron) %>%
#   mutate(maxfr=maxfr/max(maxfr),
#          scalednspikes=nspikes/max(nspikes)) ->
#   pscaled
# 
# qplot(R.H.Amp,R.V.Amp,color=nspikes,data=filter(pscaled,abs(R.H.Amp)>3 | abs(R.V.Amp>3)))+
#   facet_wrap(~neuron,ncol=2)+
#   geom_point(aes(alpha=0.3,size=4))
```

```{r change.rate.position}
# m %>%
# #  filter(isfixation=T) %>%
#   group_by(neuron,s) %>%
#   summarize(mean.verg=mean.Verg.Angle[1],
#             mean.Spikerate=mean.Spikerate[1],
#             maxfr=maxfr[n()],
#             maxamp=maxamp[n()],
#             dur=n()) %>%
#   filter(maxamp>3) %>%
#   arrange(s) %>%
#   mutate(verg.change=mean.verg-lag(mean.verg),
#          rate.change=mean.Spikerate-lag(mean.Spikerate)) ->
#   mva
```
