---
title: "NRTP vs SOA"
author: "Adam"
date: "March 14, 2016"
output: html_document
---
#Introduction
This document compares the activity of neurons in the SOA with those in the NRTP. Analysis surrounds the sensitivity to vergence angle during fixation, and an analysis of any increase in firing rate during saccades with vergence.  


```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE,cache=FALSE)
```

```{r,message=FALSE}

library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
# library(broom)
# library(grid)
library(relaimpo)
library(leaps)
#library(data.table)
library(stringr)

```

```{r helperfunctions}

spikedensity<-function (rasters,sd=100) {
  gsize<- sd*10
  g<-dnorm(-gsize:gsize,mean=0,sd=sd)
  sdf<-convolve(rasters,g,type="open")
  sdf<-sdf[gsize:(length(sdf)-(gsize+1))]*1000
  sdf
}

dynamiclead<-function(p,lags=seq(10,300,by=10)) {
  
  rsq<-NULL
  for (i in 1:length(lags)) {
    if (lags[i] > 0){
      p$sdflag<-dplyr::lag(p$sdf,lags[i])
    }
    else{
      p$sdflag<-dplyr::lead(p$sdf,lags[i]*-1)
    }
    
    rsq[i]<- summary(lm(sdflag~rep+lep+repV+lepV,data=p))$r.squared
  }
  #return(rsq)
  return(lags[rsq==max(rsq)])
}

findSaccades<-function(ev,threshold=40){
  
  i<-which(abs(ev)>threshold) #find all the times when speed > threshold
  sacoff<-which(diff(i)>15) #minimum duration of an accepted saccade
  sacon<-c(1,sacoff+1) #first saccade
  sacoff<-c(sacoff,length(i)) #end of last saccade
  saccade.onset<-i[sacon] #get actual times
  saccade.offset<-i[sacoff] 
  return(data.frame(saccade.onset,saccade.offset))
}

markSaccades<-function(ev,buffer=15,threshold=40){
  #this function finds and marks saccades given a velocity input
  stimes<-findSaccades(ev,threshold)
  
  #remove saccades without enough data at the end of the file, based on buffer size
  toolong<- stimes$saccade.offset> length(ev)-buffer
  tooshort<- stimes$saccade.onset<buffer+1
  stimes<- filter(stimes, !tooshort, !toolong)
  
  nsaccades=nrow(stimes)

  stimes$saccade.onset=stimes$saccade.onset-buffer
  stimes$saccade.offset=stimes$saccade.offset+buffer
  
  s<-1:length(ev)*0
  
  for (k in 1:nsaccades){
    s[stimes$saccade.onset[k]:stimes$saccade.offset[k]]<- k
    if(k>1){
      s[stimes$saccade.offset[k-1]:stimes$saccade.onset[k]]<-(k*-1)
    }
  }
  s[1:stimes$saccade.onset[1]]<- -1
  s[stimes$saccade.offset[nrow(stimes)]:length(s)]<- (nrow(stimes)*-1)-1
  return(s)
}

parabolicdiff <- function(pos,n=7){
  q <- sum(2*((1:n)^2))
  convoutput<- convolve(pos,c(-n:-1, 1:n),type="open")
  convoutput<- convoutput[(n*2):(length(pos)-((n*2)+1))]
  vels<- c(array(convoutput[1],dim=n*2),convoutput,array(convoutput[length(convoutput)],dim=n*2))
  vels <- vels/q*1000
}

```

```{r loadfiles}
#load all the .csv files in the data folder, then add a column naming the neuron, 
#using the file name as the default name, then put them all together in one long data frame

path<- "C:/Users/setup/Desktop/NRTP Vergence/"

#get names of all files in path
files <- list.files(path=path,pattern='*.csv')
#extract neuron name eg. Bee-01
names<-sapply(files, str_match,"^[a-zA-Z]+-[0-9]+",USE.NAMES=FALSE)
#check for new cells
r<-readRDS('NRTPr.RDS') #saved data
files<-files[!names %in% r$neuron] #comparison

nfiles<-length(files)
 # nfiles=1
if (nfiles>0){
  message(paste('Loading: ',files))
  loadedfiles <- lapply(paste(path,files,sep=''),read.csv)
}else{
  stop('********NO NEW CELLS********')
}

 t<-data.frame()
 buffer<- 200
 for (i in 1:nfiles) {
   f<- files[i]
   temp=loadedfiles[[i]]

   names<-str_match(f,"(^[a-zA-Z]+)-([0-9]+)")
   temp$neuron<-names[1]
   temp$monkey<-names[2]
   temp$cellnum<-names[3]
   temp$sdf<-spikedensity(temp$rasters,sd=10)
   # leadtime<-dynamiclead(temp)
   temp<-mutate(temp,
                # sdflag=lag(sdf,leadtime),
                s=markSaccades((sqrt(rev^2)+sqrt(revV^2))/2,buffer=buffer,threshold=10),
                time=row_number(),
                verg.angle=rep-lep,
              verg.velocity=parabolicdiff(verg.angle,7),
                isfixation=s<0,
                s=abs(s))

   t <-rbind(t,temp)

 }

```

```{r measureMovements}
t %>%
  group_by(neuron,s,isfixation) %>%
  mutate(meanfr=mean(sdf),
         maxfr=max(sdf),
         R.Hor=mean(rep),
         R.Ver=mean(repV),
         L.Hor=mean(lep),
         L.Ver=mean(lepV),
         mean.Verg.Angle=mean(verg.angle),
         mean.Verg.Angle=replace(mean.Verg.Angle, mean.Verg.Angle<0, NA),
         max.Verg.Vel = max(verg.velocity),
         max.Verg.Ang = max(verg.angle),
         nspikes=sum(rasters),
         dur=n(),
         mean.Spikerate=sum(rasters)/dur*1000,
         R.H.Amp=rep[1]-rep[length(rep)],
         L.H.Amp=lep[1]-lep[length(lep)],
         R.V.Amp=repV[1]-repV[length(repV)],
         L.V.Amp=lepV[1]-lepV[length(lepV)],
         maxamp=max(abs(R.H.Amp),abs(R.V.Amp),abs(L.H.Amp),abs(L.V.Amp)))->
  m


```

```{r verg.fixations,fig.height=10}
m %>%
  filter(isfixation=T,dur>200) %>%
  summarize(mean.Spikerate=mean.Spikerate[1],
            mean.Verg.Angle=mean.Verg.Angle[1],
            dur=dur[1]) ->
summaryforplot

s.old<-readRDS('NRTPsummaryforplot.RDS')

summaryforplot<-rbind(s.old,summaryforplot)

saveRDS(summaryforplot,'NRTPsummaryforplot-new.RDS')

ggplot(aes(mean.Verg.Angle,mean.Spikerate),data=summaryforplot)+
  geom_point(size=2,alpha=1/5)+
  facet_wrap(~neuron)+
  stat_smooth(method='lm')+
  ggtitle('Firing Rate as a function of Vergence Angle during Fixations')

# qplot(mean.Verg.Angle,mean.Spikerate,data=summaryforplot)+
#   geom_point()+
#   stat_smooth(method='lm')+
#   facet_wrap(~neuron)+
#   ggtitle('Firing Rate as a function of Vergence Angle during Fixations')

```

We plot the firing rate of each cell during saccades, including 100ms before and after the movement. Convergent saccades have an amplitude change of +3, divergent, -3 and version saccades are the rest. 

```{r is.there.a.burst, fig.height=28,fig.width=13}
maxabs<- function(x){
  m1<-max(x,na.rm=T)
  m2<-min(x,na.rm=T)
  if (abs(m1)>abs(m2)) {
    return(m1)
  } else{
    return(m2)
  }

}
t%>%
  group_by(neuron) %>%
  #   mutate(s=markSaccades((sqrt(rev^2)+sqrt(revV^2))/2,100),
  #          isfixation=s<0,
  #          s=abs(s),
  #          sdf=spikedensity(temp$rasters,sd=20)) %>%
  filter(isfixation == F) %>%
  group_by(neuron,s) %>%
  mutate(dur=n(),
         peak.R.H= maxabs(rev),
         peak.R.V= maxabs(revV),
         peak.L.H= maxabs(lev),
         peak.L.V= maxabs(levV),
         R.H.Amp=rep[n()]-rep[1],
         L.H.Amp=lep[n()]-lep[1],
         R.V.Amp=repV[n()]-repV[1],
         L.V.Amp=lepV[n()]-lepV[1],
         r.angle=atan2(R.V.Amp,R.H.Amp)*180/pi,
         r.amp=sqrt(R.H.Amp^2+R.V.Amp^2),
         nspikes=sum(rasters),
         vect.amp= (sqrt(R.H.Amp^2+R.V.Amp^2)+sqrt(L.H.Amp^2+L.V.Amp^2))/2,
         maxamp=max(abs(R.H.Amp),abs(R.V.Amp),abs(L.H.Amp),abs(L.V.Amp)),
         verg.amp=verg.angle[n()]-verg.angle[1],
         peak.verg.velocity= maxabs(verg.velocity),
         min.verg.trans = min(verg.velocity),
         max.verg.trans = max(verg.velocity),
         maxfr=max(sdf),
         counter=time-time[1])%>%
  group_by(neuron) %>%
  mutate(saccade.type='version',
         saccade.type=replace(saccade.type, verg.amp > 2,'convergence'),
         saccade.type=replace(saccade.type, verg.amp < -2, 'divergence'))->
  p

  p.old<- readRDS('NRTPp.RDS')
  
  p<- rbind(p.old,p)
  
  saveRDS(p,'NRTPp-new.RDS')


g<- ggplot(aes(counter-buffer,sdf),data=filter(p,dur<(80+buffer*2)))
# g+stat_smooth(method='auto',size=2)+
#   facet_wrap(~neuron,ncol=2)+
#   geom_vline(x=0)+
#   ggtitle('Average Spike Rate During Saccades')+
#   ylab('Spike Density Function')+
#   xlab('Time from Saccade Onset (ms)')
```


```{r verg.change,fig.height=28,fig.width=13}
g+
  # geom_point(alpha=1/30,aes(color=saccade.type))+
  stat_smooth(method='auto',size=2,aes(color=saccade.type))+
  facet_wrap(~neuron,ncol=2)+
  geom_vline(xintercept=0)+
  ggtitle('Average Spike Rate During Saccades')+
  ylab('Spike Density Function')+
  xlab('Time from Saccade Onset (ms)')+
  theme(legend.position="top")
```

```{r peak.verg.velocity,fig.height=28,fig.width=13,echo=F}
# qplot(peak.verg.velocity,maxfr,data=p,color=saccade.type)+
#   facet_wrap(~neuron,ncol=2)+geom_point(size=3,alpha=1/20)+
#   theme(legend.position="top")
# # qplot(max.verg.trans,maxfr,data=p,color=verg.amp)+facet_wrap(~neuron,ncol=2)+geom_point(size=3,alpha=1/20)
```

##Model Fitting: Peak transient velocity or amplitude of vergence angle change?
In this next section we attempt to distinguish between two factors that are correlated with the peak firing rates of the vergence-burster cells: the amplitude of the vergence angle change and the peak velocity of the vergence transient. It may be possible to distinguish these because there are vergence transients even during saccades without a significant change in vergence angle. The above plot demonstrates this. In some cells, the blue points are below the red points, and above the green ones. This means that for a given peak transient velocity, the cell will fire more if the vergence angle changes more. 

### Model based on the positive transient
```{r positive.trans only,echo=F}
p %>%
  # filter(peak.verg.velocity>0) %>%
  group_by(neuron,cellnum) %>%
  # do(b=calc.relimp(lm(maxfr~verg.angle+peak.verg.velocity,data=.)),
     # bic=regsubsets(maxfr~verg.angle+peak.verg.velocity,.)) ->
    do(b=calc.relimp(lm(maxfr~verg.angle+max.verg.trans,data=.)),
     bic=regsubsets(maxfr~verg.angle+max.verg.trans,.)) ->
  bb
r <- data.frame()
r2 <- NULL
for (i in 1:nrow(bb)){
  b<- bb$b[[i]]$lmg
  r<-rbind(r,b)
  
  r2<- c(r2,bb$b[[i]]$R2)
  
}

r$neuron<-bb$neuron
r$cellnum<- bb$cellnum
r$R2<- r2

names(r)<- c(names(bb$b[[1]]$lmg),'neuron','cellnum','R2')

r<- mutate(r, SOA=as.numeric(cellnum)>100)
r.old<-readRDS('NRTPr.RDS')
r<- rbind(r.old,r)
saveRDS(r,'NRTPr-new.RDS')

# write.csv(r,"allfiles-r.csv")
# rmark<-read.csv('marksoacells.csv')
# r<- rbind(r,rmark[,-1])
```

```{r plot.positive.trans.fit,fig.height=10,fig.width=10}

ggplot(aes(verg.angle,max.verg.trans),data=r)+
  # geom_point(size=4,aes(color=R2,shape=verg.angle>max.verg.trans))+
  geom_point(size=4,aes(color=R2,shape=SOA))+
  # geom_point(size=4,aes(color=R2))+
  scale_color_gradient(low='blue',high='red')+
  # geom_point(size=4,aes(color=verg.angle>max.verg.trans))+
  geom_text(aes(label=neuron),check_overlap=FALSE,size=3,vjust=-1)+
  geom_abline(intercept=0,slope=1)+
  # coord_cartesian(xlim=c(-0.5,1),ylim=c(-0.5,1))+
  theme(legend.position="top")+
  ggtitle('Relative Importance')


# qplot(verg.angle,peak.verg.velocity,data=r, color=neuron,size=4)
# for (i in 1:nrow(bb)){
# #  b<-booteval.relimp(bb$b[[i]])
#   b<-bb$b[[i]]
#   plot(b, main=bb$neuron[i])
#   # plot(bb$bic[[i]],main=bb$neuron[i])
#   # plot(bb$bic[[i]],scale=c('adjr2'),main=bb$neuron[i])
# }
# for (i in 1:nrow(bb)){
# #  b<-booteval.relimp(bb$b[[i]])
#   # b<-bb$b[[i]]
#   # plot(b, main=bb$neuron[i])
#   # plot(bb$bic[[i]],main=bb$neuron[i])
#   plot(bb$bic[[i]],scale=c('adjr2'),main=bb$neuron[i])
# }
```
