---
title: "NPH static analysis"
author: "Adam"
date: "September 23, 2015"
output: word_document
---
This is my first effort at analysis of the activity of the purported NPH cells. 

In Matlab, I did spike sorting and created a spike density function by convolving the spiketimes with a Gaussian with a standard deviation of 20ms. I then saved that as a table containing the right and left eye position and velocity (calculated using a 7 point parabolic differentiation function) and the spike density function, scaled to approximate firing rate.

```{r,message=FALSE}
t1 <- read.csv("~/GitHub/NPHanalysis/Patos_2014_03_27_1435_Radial.csv")
t2 <- read.csv("~/GitHub/NPHanalysis/Bee_Mark_2015_09_17_1440_Radial.csv")

library(ggplot2)
library(dplyr)
library(knitr)
```

First I will plot the average firing rate of the neuron while the eyes are in various positions. I've restricted my analysis to periods when the eyes are not in motion using a simple eye velocity threshold. I require both the vertical and horizontal eye position to be less than one. This allows for pre-movement burst activity to potentially interfere with the static analysis. 

```{r}
meanfr <- function(t){
  thresh=1.5
  t %>%
    filter(abs(rev)<thresh,abs(revV)<thresh,abs(lev)<thresh,abs(levV)<thresh) %>%
    mutate(RHep=round(rep),RVep=round(repV), LHep=round(lep),LVep=round(lepV)) %>%
    group_by(RHep,RVep,LHep,LVep) %>%
    summarize(fr=mean(sdf)) %>%
    ungroup(.) ->
    s
  return(s)
}
s1<-meanfr(t1)
s2<-meanfr(t2)

plottile<-function(s){
  m<-ggplot(s,aes(RHep,RVep,fill=fr,z=fr))
  m1<-m+geom_tile()+scale_fill_gradient(low='black',high='orange')+
    xlab('Horizontal Eye Position')+ylab('Vertical Eye Position')+
    ggtitle('Right Eye')
  m<-ggplot(s,aes(LHep,LVep,fill=fr,z=fr))
  m2<-m+geom_tile()+scale_fill_gradient(low='black',high='orange')+
    xlab('Horizontal Eye Position')+ylab('Vertical Eye Position')+
    ggtitle('Left Eye')
  return(list(m1, m2))
}

m1<-plottile(s1)
m2<-plottile(s2)

m1[1]
m2[1]
m1[2]
m2[2]
```

Next, I calculate the sensitivity of the neuron to horizontal and vertical eye position:

```{r}
compareslope <- function(s) {
  Left.Horizontal.Slope <- summary(lm(fr~LHep,data=s))$coefficients[2]
  Left.Vertical.Slope <- summary(lm(fr~LVep,data=s))$coefficients[2]
  Left.Preferred.Direction <- atan2(Left.Vertical.Slope,Left.Horizontal.Slope)*180/pi
  
  Right.Horizontal.Slope<-summary(lm(fr~RHep,data=s))$coefficients[2]
  Right.Vertical.Slope<-summary(lm(fr~RVep,data=s))$coefficients[2]
  Right.Preferred.Direction<-atan2(Right.Vertical.Slope,Right.Horizontal.Slope)*180/pi
  return(data.frame(Left.Horizontal.Slope,Left.Vertical.Slope,Left.Preferred.Direction,
                    Right.Horizontal.Slope,Right.Vertical.Slope,Right.Preferred.Direction))
}

x1<-compareslope(s1)
x2<-compareslope(s2)

x<-rbind(x1,x2)
kable(x,digits=2)
```


