---
title: "NPH Interactive"
author: "Adam"
date: "November 30, 2015"
output:
  html_document:
    self_contained: no
runtime: shiny
---

#Introduction
This is an analysis of cells believed to be recorded in the NPH of a normal monkey (Bee) and a monkey with exotropia (Patos). The NPH is thought to provide the horizontal integrator for the control of eye movements. Individual neurons in NPH are typically described as either burst-tonic or tonic cells, with activity related to either the position or position and velocity of the eyes. 

#Analysis
* Calclate the lead time for each neuron.
+ shift data from cell and eye coils to align based on lead time
* Identify saccades.
* Plot the firing rate during fixations
* fit and evaluate a linear model: Firing Rate ~ eye position/velocity, horizontal/vertical, left/right (8 terms)
+ Evaluate using Relative Importance
+ Evaluate using BIC and adjusted R^2, using exhaustive search that finds the best model using 1-8 terms
* Optionally, we can restrict our analysis to just disjunctive saccades. This can help to identify monocular cells, since the parameters during conjugate saccades are typically well correlated.


```{r echo=FALSE} 
library(knitr)
opts_chunk$set(echo=FALSE)
```

```{r,message=FALSE}

library(ggplot2)
library(dplyr)
#library(knitr)
#library(tidyr)
#library(broom)
#library(grid)
library(relaimpo)
library(leaps)
#library(data.table)

```


```{R SHINYTRY}
#In order to make the shiny app load fast, I'm just saving the output. See BoostrapSaccades.Rmd for the actual analysis.
bb<-readRDS(file="NPHFULLBIC.Rda")
summaryforplot<-read.csv("NPHFULLplotsummary.csv")

neurons<-as.character(unique(bb$neuron))

inputPanel(
  selectizeInput("neuronchoice", label = "Select a Neuron:",
              choices = neurons)
)
renderPlot({
  nc<-input$neuronchoice
  x<-filter(summaryforplot,neuron==nc)
  qplot(R.Hor,R.Ver,color=meanfr,data=filter(x,s<0,dur>200))+geom_point(size=4)+ggtitle("Mean Firing Rate During Fixation")
})

renderPlot({
  nc<-input$neuronchoice
  x<-filter(bb,neuron==nc)
  plot(x$b[[1]],main=nc)
  #plot(x$bic[[1]],main=nc)
})

renderPlot({
  nc<-input$neuronchoice
  x<-filter(bb,neuron==nc)
  #plot(x$b[[1]],main=nc)
  plot(x$bic[[1]],main=nc)
})

```

